---
title: "Land Analysis Dashboard"
format:
  dashboard:
    embed-resources: true
    theme:
      - default
editor: source
date: "2026-04-14"
params:
# =========================================================================
# COMPANY INFORMATION
# =========================================================================
  Company: Red River Group
  CompAddress: PO Box 1180
  CompCity: Niverville
  CompProvince: MB
  CompPC: R0A 1E0

# =========================================================================
# SUBJECT PROPERTY
# =========================================================================
  SubAddress: Shady Shores Dr E
  SubCity: Winnipeg
  SubMunicipality: Winnipeg (City)           # Subject municipality (may differ from city)
  SubProvince: MB
  SubLat: 49.8788846906338
  SubLon: -97.02857151750601
  SubLotAc: 5.18
  SubLotSF: 225583
  SubZoning: "RMF-S"                         # Subject zoning designation
  EffDate: "2026-04-17"                      # Appraisal effective date (YYYY-MM-DD)
  SubNeighborhood: [""]                      # Subject neighborhood(s), blank if n/a
  
# =========================================================================
# REFERENCE/COMPARISON SETTINGS
# =========================================================================
  RefLat: 49.88879225852696 # Reference lat/lon for mapping - e.g. Centre of Winnipeg - Main/Broadway
  RefLon: -97.1349132019094
  SubRef: Ref # Use Sub for Subject location or Ref for Reference location for radius
  RefPoint: "Downtown" # Subject if sub, Winnipeg or whatever reference is if otherwise
  
# =========================================================================
# LOCATION FILTERS
# =========================================================================
  UCFilter: A  # A = do not filter; I = INCLUDE; E = EXCLUDE
  CityList: [""]  # Cities to include in the comparables filter
  UCFilterList: UDC  # WpgMetro, WpgCapital, UC3K, UDC
  LoDistKM: 5      # Lower distance filter (km from Sub/Ref)
  HiDistKM: 20     # Upper distance filter (km from Sub/Ref)
  NeighborhoodExcl: ["Downtown East", "Downtown West"] # Exclude these Neighbourhoods

# =========================================================================
# PROPERTY FILTERS
# =========================================================================
  PropMajorInc: [""] # Property major categories to include
  AcOrSF: "ac"  # Controls filtering AND chart display: "ac" or "sf"
  LoLandSizeAc: 1.25                          
  HiLandSizeAc: 12
  LoLandSizeSF: 40000
  HiLandSizeSF: 400000
  LoSaleDate: "2021-01-01"                   # Earliest sale date to include (YYYY-MM-DD)
  HiSaleDate: "" # If blank, uses EffDate above - else you can define here
  Outliers: [""] # Example w/explanation: 27440|McDonalds Niverville
  ZoningFilter:  [""] # Include only these zoning designations

# =========================================================================
# EXPORT AND CHART CONTROL SETTINGS
# =========================================================================
  ExportCharts: Y  # Set to "Y" to export all charts and maps to ./charts/ directory, "N" to skip
  ShowRadius: N  # Y = zoom map view to show full HiDistKM radius circle + label; N = zoom to data extent only
  ExposureCharts: Y  # Y = Show exposure analysis; N = Hide
  FeatureImportance: N  # Y = Show feature importance tab; N = Hide

# =========================================================================
# EXPOSURE ANALYSIS SETTINGS (conditional on ExposureCharts = Y)
# =========================================================================
  ExposurePriceMin: 1000000    # Minimum price for exposure analysis band
  ExposurePriceMax: 5000000    # Maximum price for exposure analysis band

# =========================================================================
# MULTI-FAMILY / LAND UNITS PARAMETERS
# NOTE: Partially implemented - not in dashboard - reserved for future phase
# =========================================================================
  PricePerUnit: N  # Y = Run charts for price per land unit; N = do not run
  LandUnitType: ["Apartment"]  # Allowed: Apartment, Condo, Lot, Other. Use a list e.g. ["Apartment", "Condo"]. Leave as [""] to include ALL records (no type filter - NOT RECOMMENDED).
  SubLandUnits: 92  # Number of land units (e.g., apartment units) on subject property
  # Subject density (Units/Acre) is computed automatically as round(SubLandUnits / SubLotAc) - see setup chunk
  LoLandSizeUnit: 10  # Minimum land units for filtering (only if PricePerUnit = Y)
  HiLandSizeUnit: 400  # Maximum land units for filtering (only if PricePerUnit = Y)
  MultiFamilyYN: N  # Y = Run charts for Price by Zoning (multi-family); N = do not run-NOT FULLY IMPLEMENTED
---

# {.sidebar}

```{r sidebar_filters_parameters}
#| title: "Filters & Parameters"
```

---

**Data Provided By:** `r params$Company`

---

**Subject Property**

**Address:** `r params$SubAddress`, `r params$SubCity`, `r params$SubProvince`<br>
**Lot Size:** `r if(params$AcOrSF == "ac") paste0(params$SubLotAc, " acres") else paste0(format(params$SubLotSF, big.mark=","), " sf")`<br>
**Zoning:** `r params$SubZoning`<br>
**Effective Date:** `r params$EffDate`

---

**Parameters for Competitive Market Segment (CMS)**

**Sale Date Range:** `r format(as.Date(params$LoSaleDate), "%b %Y")` to `r format(as.Date(if (params$HiSaleDate == "") params$EffDate else params$HiSaleDate), "%b %Y")`<br>
**Size Range:** `r if(params$AcOrSF == "ac") paste0(params$LoLandSizeAc, "-", params$HiLandSizeAc, " acres") else paste0(format(params$LoLandSizeSF, big.mark=","), "-", format(params$HiLandSizeSF, big.mark=","), " sf")`<br>
**Distance:** `r params$LoDistKM` to `r params$HiDistKM` km from `r params$RefPoint`<br>
**Property Type:** `r if(length(params$PropMajorInc) > 0 && any(params$PropMajorInc != "")) paste(params$PropMajorInc, collapse=", ") else "All"`<br>
**Size Unit:** `r toupper(params$AcOrSF)`\
**Neighbourhoods Excluded:** `r if(length(params$NeighborhoodExcl) > 0 && any(params$NeighborhoodExcl != "")) paste(params$NeighborhoodExcl, collapse = ", ") else "None"`

---

```{r setup, include=FALSE}
# Load required packages and resolve HiSaleDate default from params.
options(scipen = 999)

# Load packages
pacman::p_load(tidyverse, dplyr, readr, ggtext, geosphere, mapgl, scales,
               plotly, patchwork, mapview, chromote, openxlsx, stringr,
               lubridate, glue, ggpubr, sf, magrittr, explore)

# ==============================================================================
# PARAMETER DEFAULTS: Fall back to EffDate if HiSaleDate is blank
# ==============================================================================
HiSaleDate <- if (is.null(params$HiSaleDate) || params$HiSaleDate == "") {
  params$EffDate
} else {
  params$HiSaleDate
}

# ==============================================================================
# SUBJECT DENSITY: Computed as round(SubLandUnits / SubLotAc).
# Used by the CMSLU density charts (vline + intersection caption).
# ==============================================================================
SubLandUnitDensity1 <- if (!is.null(params$SubLandUnits) &&
                           !is.null(params$SubLotAc) &&
                           is.numeric(params$SubLandUnits) &&
                           is.numeric(params$SubLotAc) &&
                           params$SubLotAc > 0) {
  round(params$SubLandUnits / params$SubLotAc)
} else {
  NA_real_
}
```

```{r sidebar_multifamily_section, echo=FALSE, results='asis'}
# Conditionally render a Multi-Family Density block in the sidebar when
# PricePerUnit == "Y". Runs after the setup chunk so SubLandUnitDensity1 is
# already computed.
if (isTRUE(params$PricePerUnit == "Y")) {
  lut_label <- if (!is.null(params$LandUnitType) &&
                   length(params$LandUnitType) > 0 &&
                   any(params$LandUnitType != "")) {
    paste(params$LandUnitType, collapse = ", ")
  } else {
    "All"
  }

  density_label <- if (is.na(SubLandUnitDensity1)) {
    "n/a"
  } else {
    paste0(SubLandUnitDensity1, " units/acre")
  }

  cat("**Multi-Family Density**\n\n")
  cat("**Land Unit Type:** ", lut_label, "<br>\n", sep = "")
  cat("**Subject Units:** ", format(params$SubLandUnits, big.mark = ","), "<br>\n", sep = "")
  cat("**Subject Density:** ", density_label,
      " *(", params$SubLandUnits, " \u00f7 ", params$SubLotAc, " ac)*<br>\n", sep = "")
  cat("**Unit Count Range:** ", params$LoLandSizeUnit, "\u2013", params$HiLandSizeUnit, " units\n\n", sep = "")
  cat("---\n\n")
}
```

```{r helper_functions, include=FALSE}
# ==============================================================================
# HELPER FUNCTIONS
# ==============================================================================

theme_point_colour <- function() {
  list(
    geom_point(
      shape = 21,
      size = 3,
      fill = "steelblue1",
      alpha = 0.6,
      color = "steelblue4",
      stroke = 0.5
    )
  )
}

theme_custom <- function(
  base_size = 12,
  title_color = "red4",
  accent_color = "steelblue3",
  grid_color = "lightgray",
  background_color = "white",
  title_size = 16,
  subtitle_size = 12,
  caption_size = 10,
  axis_text_size = 10,
  use_markdown = FALSE
) {
  if (use_markdown && requireNamespace("ggtext", quietly = TRUE)) {
    subtitle_element <- ggtext::element_markdown(size = subtitle_size)
  } else {
    subtitle_element <- element_text(size = subtitle_size)
  }

  theme_minimal(base_size = base_size) +
    theme(
      text = element_text(size = base_size),
      plot.title = element_text(color = title_color, size = title_size,
                                 face = "bold", margin = margin(b = 5)),
      plot.subtitle = subtitle_element,
      plot.caption = element_text(color = title_color, size = caption_size,
                                   face = "bold", hjust = 1),
      panel.grid.major.y = element_line(color = grid_color, linetype = "solid",
                                         linewidth = 0.25),
      panel.grid.minor.y = element_line(color = grid_color, linetype = "dashed",
                                         linewidth = 0.25),
      panel.grid.major.x = element_line(color = grid_color, linetype = "solid",
                                         linewidth = 0.25),
      panel.grid.minor.x = element_line(color = grid_color, linetype = "dashed",
                                         linewidth = 0.25),
      panel.background = element_rect(fill = background_color),
      plot.background = element_rect(fill = background_color, color = NA),
      line = element_line(color = accent_color),
      axis.text.x = element_text(size = axis_text_size, margin = margin(t = 5),
                                  vjust = 0.5),
      axis.text.y = element_text(size = axis_text_size, margin = margin(r = 5),
                                  hjust = 1),
      axis.title = element_text(size = axis_text_size, face = "bold",
                                 margin = margin(t = 10, b = 10)),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)),
      axis.ticks = element_line(color = grid_color, linewidth = 0.5),
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      legend.text = element_text(size = axis_text_size),
      legend.key = element_rect(fill = NA),
      plot.margin = margin(t = 10, r = 22, b = 5, l = 5, unit = "pt")
    )
}

# Helper to create circle geometry for distance rings
create_circle_sf <- function(lon, lat, radius_km, n_points = 64) {
  angles <- seq(0, 2 * pi, length.out = n_points)
  lat_rad <- lat * pi / 180
  lon_offset <- (radius_km / 111) / cos(lat_rad)
  lat_offset <- radius_km / 111

  coords <- cbind(
    lon + lon_offset * cos(angles),
    lat + lat_offset * sin(angles)
  )
  coords <- rbind(coords, coords[1,])

  st_sf(
    geometry = st_sfc(st_polygon(list(coords)), crs = 4326),
    radius_km = radius_km
  )
}

add_distance_rings <- function(map, lon, lat, inner_km, outer_km, show = TRUE) {
  if (!show) return(map)
  # Label offset scales with radius: 15% of radius + small minimum
  # This adapts for both small (3 km) and large (70 km) radii
  outer_label_offset <- (outer_km / 111) * 0.1 + 0.005

  # Create outer ring
  outer_ring <- create_circle_sf(lon, lat, outer_km)
  outer_label <- st_sf(
    label = paste0(outer_km, " km"),
    geometry = st_sfc(st_point(c(lon, lat + outer_km / 111 + outer_label_offset)), crs = 4326)
  )

  map <- map |>
    add_line_layer(
      id = "outer-ring",
      source = outer_ring,
      line_color = "blue",
      line_width = 1.5
    ) |>
    add_symbol_layer(
      id = "outer-ring-label",
      source = outer_label,
      text_field = get_column("label"),
      text_size = 14,
      text_color = "blue",
      text_font = c("Open Sans Bold", "Arial Unicode MS Bold")
    )

  if (inner_km > 0) {
    inner_ring <- create_circle_sf(lon, lat, inner_km)
    inner_label_offset <- (inner_km / 111) * 0.1 + 0.005
    inner_label <- st_sf(
      label = paste0(inner_km, " km"),
      geometry = st_sfc(st_point(c(lon, lat + inner_km / 111 + inner_label_offset)), crs = 4326)
    )

    map <- map |>
      add_line_layer(
        id = "inner-ring",
        source = inner_ring,
        line_color = "black",
        line_width = 2
      ) |>
      add_symbol_layer(
        id = "inner-ring-label",
        source = inner_label,
        text_field = get_column("label"),
        text_size = 14,
        text_color = "black",
        text_font = c("Open Sans Bold", "Arial Unicode MS Bold")
      )
  }

  map
}


apply_uc_filter <- function(df, uc_filter, uc_filter_list) {
  if (!uc_filter %in% c("I", "E")) return(df)

  lookup_list <- get(uc_filter_list, inherits = TRUE)
  col_name <- if (grepl("Wpg", uc_filter_list)) "Municipality" else "City"
  lookup_values <- lookup_list[[col_name]]

  if (uc_filter == "I") {
    filter(df, .data[[col_name]] %in% lookup_values)
  } else {
    filter(df, !.data[[col_name]] %in% lookup_values)
  }
}

# Distance filter helper — consolidates the SubRef branching
apply_dist_filter <- function(df, params, lo_km, hi_km) {
  col <- if (params$SubRef == "Ref") "RefDist" else "SubDist"
  filter(df, between(.data[[col]], lo_km, hi_km))
}

# Tooltip builder — standardizes the tooltip text for land maps.
make_tooltip <- function(df, unit_label, ac_or_sf = "ac") {
  paste0(
    df$Address, ", ", df$City,
    "<br>Date: ", format(df$DateSold, "%Y-%m-%d"),
    "<br>Price: ", scales::dollar(df$PriceSold, accuracy = 1),
    "<br>", if(ac_or_sf == "sf") paste0("Land SF: ", scales::comma(df$LandSF, accuracy = 1)) else paste0("Acres: ", round(df$Acres, 2)),
    "<br>$/", unit_label, ": ", if(ac_or_sf == "sf") scales::dollar(df$PriceLandSF, accuracy = 0.01) else scales::dollar(df$PriceAcre, accuracy = 1),
    "<br>Zoning: ", df$Zoning
  )
}

# Build a base map with optional boundary layers, distance rings, and satellite toggle.
build_base_map <- function(bounds, muni_bnd = NULL, wpg_nb_bnd = NULL,
                           muni_color_map = NULL, id_prefix = "map",
                           circle_lon = NULL, circle_lat = NULL,
                           lo_km = 0, hi_km = 0, show_rings = FALSE) {
  map <- maplibre(bounds = bounds) |>
    add_navigation_control(position = "top-left") |>
    add_satellite_layer()

  # Distance rings
  if (show_rings && !is.null(circle_lon)) {
    map <- add_distance_rings(map, circle_lon, circle_lat, lo_km, hi_km, show = TRUE)
  }

  # Municipal boundaries
  if (!is.null(muni_bnd)) {
    map <- map |>
      add_fill_layer(
        id = paste0(id_prefix, "_muni_fill"),
        source = muni_bnd,
        fill_color = get_column("fill_color"),
        fill_opacity = 0.05,
        tooltip = "tooltip"
      ) |>
      add_line_layer(
        id = paste0(id_prefix, "_muni_line"),
        source = muni_bnd,
        line_color = "darkblue",
        line_width = 2,
        line_dasharray = c(5, 5)
      )
  }

  # Winnipeg neighbourhood boundaries
  if (!is.null(wpg_nb_bnd)) {
    map <- map |>
      add_fill_layer(
        id = paste0(id_prefix, "_wpg_nb_fill"),
        source = wpg_nb_bnd,
        fill_color = get_column("nb_fill_color"),
        fill_opacity = 0.10,
        tooltip = "tooltip"
      ) |>
      add_line_layer(
        id = paste0(id_prefix, "_wpg_nb_line"),
        source = wpg_nb_bnd,
        line_color = get_column("nb_fill_color"),
        line_width = 1.5,
        line_opacity = 0.7
      )
  }

  # Satellite toggle control
  map |>
    add_layers_control(
      position = "top-right",
      layers = list("Satellite" = "satellite-layer")
    )
}

# Prepare municipal boundary attributes once (fill_color + tooltip)
prep_muni_bnd <- function(bnd, color_map) {
  if (is.null(bnd)) return(NULL)
  bnd$fill_color <- color_map[tools::toTitleCase(tolower(bnd$MUNI_LIST_NAME_WITH_TYPE))]
  bnd$tooltip <- bnd$MUNI_LIST_NAME_WITH_TYPE
  bnd
}

# Prepare Winnipeg neighbourhood boundary attributes once (nb_fill_color + tooltip)
prep_wpg_nb_bnd <- function(bnd) {
  if (is.null(bnd)) return(NULL)
  bnd$nb_fill_color <- get_nb_color(bnd$Neighborhood)
  bnd$tooltip <- bnd$Neighborhood
  bnd
}

# Placeholder chart for insufficient data
empty_chart <- function(msg = "Insufficient data for this chart") {
  ggplot() +
    annotate("text", x = 0.5, y = 0.5, label = msg, size = 6) +
    theme_void()
}

# Placeholder map for empty data
empty_map <- function() {
  maplibre() |> add_navigation_control(position = "top-left")
}

# Urban centre lookup lists
WpgMetro <- data.frame(Municipality = c("Winnipeg (City)", "Macdonald (RM)", "Rosser (RM)",
  "Ritchot (RM)", "Springfield (RM)", "West St. Paul (RM)", "East St. Paul (RM)", "Headingley (RM)",
  "Niverville (Town)", "Tache (RM)", "Rockwood (RM)", "Stonewall (Town)", "St. Andrews (RM)",
  "St. Clements (RM)", "Dunnottar (Village)", "Selkirk (City)", "St. Francois-Xavier (RM)", "Cartier (RM)"))

WpgCapital <- data.frame(Municipality = c("Winnipeg (City)", "Macdonald (RM)", "Rosser (RM)",
  "Ritchot (RM)", "Springfield (RM)", "West St. Paul (RM)", "East St. Paul (RM)", "Headingley (RM)"))

UC3K <- data.frame(City = c("Winnipeg", "Brandon", "Steinbach", "Winkler", "Portage la Prairie",
  "Thompson", "Selkirk", "Morden", "Dauphin", "Niverville", "Neepawa", "The Pas", "Norway House",
  "Stonewall", "Oakbank", "Flin Flon", "Altona", "Swan River", "Lorette", "St. Theresa Point",
  "Beausejour", "Mitchell", "Virden", "Carman", "Garden Hill First Nation", "Peguis 1B"))

# Base directory for shared reference files
base_files_dir <- "D:/Dropbox/Appraisal/RProjects/BaseFiles"

# Helper: resolve file from base dir first, then local, or NULL
resolve_file <- function(filename, base_dir = base_files_dir) {
  base_path <- file.path(base_dir, filename)
  if (file.exists(base_path)) return(base_path)
  if (file.exists(filename)) return(filename)
  NULL
}

# OPTIONAL MUNICIPAL BOUNDARIES (base dir -> local -> skip)
muni_all <- NULL
muni_path <- resolve_file("MBMunicipalities.geojson")
if (!is.null(muni_path)) {
  muni_all <- tryCatch({
    st_read(muni_path, quiet = TRUE)
  }, error = function(e) {
    message("Error reading MBMunicipalities.geojson: ", e$message)
    NULL
  })
}

# Function to filter municipal boundaries for a dataset
get_filtered_muni_boundaries <- function(df_to_match, boundaries = muni_all) {
  # df_to_match is the variable name inside the function
  if(is.null(boundaries)) return(NULL)

  # Normalize the names in your data: Remove dots, uppercase, trim spaces
  cleaned_names <- unique(df_to_match$Municipality) %>%
    gsub("\\.", "", .) %>% 
    toupper() %>%
    trimws()

  # Filter the GeoJSON boundaries using the same normalization
  filtered_bnd <- boundaries %>%
    filter(toupper(gsub("\\.", "", MUNI_LIST_NAME_WITH_TYPE)) %in% cleaned_names)

  if(nrow(filtered_bnd) == 0) return(NULL)

  return(filtered_bnd)
}

# ==============================================================================
# OPTIONAL WINNIPEG NEIGHBOURHOOD BOUNDARIES (base dir -> local -> skip)
# ==============================================================================
wpg_neighbourhoods <- NULL
wpg_neighbourhoods_clustered <- NULL

wpg_nb_path <- resolve_file("WpgNeighbourhoodClusters.geojson")
if (!is.null(wpg_nb_path)) {
  wpg_neighbourhoods <- tryCatch({
    st_read(wpg_nb_path, quiet = TRUE)
  }, error = function(e) {
    message("Error reading WpgNeighbourhoodClusters.geojson: ", e$message)
    NULL
  })

  # File is already dissolved into ~20 cluster polygons — just rename `cluster` -> Neighborhood.
  if (!is.null(wpg_neighbourhoods) && "cluster" %in% names(wpg_neighbourhoods)) {
    wpg_neighbourhoods_clustered <- wpg_neighbourhoods %>%
      rename(Neighborhood = cluster)
  }
}

# Function to get Winnipeg neighbourhood boundaries for a dataset
get_filtered_wpg_nb_boundaries <- function(data_for_filter, boundaries = wpg_neighbourhoods_clustered) {
  if (is.null(boundaries)) return(NULL)

  # Only return boundaries if data includes Winnipeg (City)
  if (!"Winnipeg (City)" %in% data_for_filter$Municipality) return(NULL)

  # Return all neighbourhood boundaries (not filtered by matching data)
  boundaries
}

# Neighbourhood Master Palette - Hard-coded Winnipeg WRHA cluster colors
# These colors match the official WRHA neighbourhood cluster map
wrha_cluster_colors <- c(
  "Assiniboine South" = "#4169E1",
  "Downtown East" = "#FFD700",
  "Downtown West" = "#FF69B4",
  "Fort Garry North" = "#6495ED",
  "Fort Garry South" = "#5B9BD5",
  "Inkster East" = "#D2B48C",
  "Inkster West" = "#DEB887",
  "Point Douglas North" = "#DAA520",
  "Point Douglas South" = "#F0E68C",
  "River East East" = "#228B22",
  "River East South" = "#32CD32",
  "River East West" = "#90EE90",
  "River Heights East" = "#4682B4",
  "River Heights West" = "#87CEEB",
  "Seven Oaks East" = "#20B2AA",
  "Seven Oaks West" = "#AFEEEE",
  "St. Boniface East" = "#FF8C00",
  "St. Boniface West" = "#FFA500",
  "St. James-Assiniboia East" = "#FFA07A",
  "St. James-Assiniboia West" = "#B0C4DE",
  "St. Vital North" = "#98FB98",
  "St. Vital South" = "#3CB371",
  "Transcona" = "#9370DB"
)

# Helper function to safely get neighborhood color
# Handles "St" vs "St." mismatch between data sources
get_nb_color <- function(neighborhood) {
  # Build a normalized lookup: strip periods from palette keys
  norm_lookup <- wrha_cluster_colors
  names(norm_lookup) <- gsub("\\.", "", names(norm_lookup))
  # Combine both so exact matches (with period) and normalized (without) both work
  combined_lookup <- c(wrha_cluster_colors, norm_lookup)
  # Remove duplicates (keep first = original with-period version)
  combined_lookup <- combined_lookup[!duplicated(names(combined_lookup))]

  sapply(neighborhood, function(nb) {
    if (is.na(nb) || nb == "Unknown") {
      "#808080"
    } else if (nb %in% names(combined_lookup)) {
      combined_lookup[nb]
    } else {
      "#808080"
    }
  }, USE.NAMES = FALSE)
}

#' Roll small neighbourhoods into an "Other" bucket for boxplots
#'
#' Takes the raw data frame used by a neighbourhood boxplot and returns
#' (1) the raw rows re-tagged so that any neighbourhood outside the top
#' `max_bars` by sale count is labelled `"Other (k nbhds)"`, and (2) a
#' stats frame (med, q3, n) in the same shape the existing boxplots
#' already consume. The returned `Neighborhood` factor is ordered by
#' ascending median so `coord_flip()` keeps the highest at the top.
#'
#' @param df          Raw data frame with `Neighborhood` and the price column.
#' @param price_col   Name of the numeric price column (character).
#' @param max_bars    Max individual neighbourhood boxes to keep (default 10).
#' @return list(df, stats, colors) where
#'   - df      : raw rows with `Neighborhood` re-tagged and factored
#'   - stats   : per-group med/q3/n, `Neighborhood` factored same as df
#'   - colors  : named character vector mapping label -> hex (grey for "Other")
rollup_neighbourhoods_for_boxplot <- function(df, price_col, max_bars = 10) {
  df <- df %>%
    filter(!is.na(Neighborhood), Neighborhood != "",
           !is.na(.data[[price_col]]))

  if (nrow(df) == 0) {
    return(list(df = df, stats = NULL, colors = character()))
  }

  nb_counts <- df %>% count(Neighborhood, sort = TRUE)
  n_total   <- nrow(nb_counts)

  if (n_total <= max_bars) {
    keep_names  <- nb_counts$Neighborhood
    other_label <- NA_character_
  } else {
    keep_names  <- nb_counts$Neighborhood[seq_len(max_bars)]
    n_other     <- n_total - max_bars
    other_label <- paste0("Other (", n_other, " nbhds)")
  }

  df <- df %>%
    mutate(nb_group = ifelse(
      Neighborhood %in% keep_names,
      as.character(Neighborhood),
      other_label
    ))

  stats <- df %>%
    group_by(nb_group) %>%
    summarise(
      med = median(.data[[price_col]], na.rm = TRUE),
      q3  = quantile(.data[[price_col]], 0.75, na.rm = TRUE),
      n   = dplyr::n(),
      .groups = "drop"
    ) %>%
    arrange(med)

  # Build ordered labels "Neighbourhood (n)" and factor both frames
  labels <- paste0(stats$nb_group, " (", stats$n, ")")
  stats$Neighborhood <- factor(labels, levels = labels)

  df$Neighborhood <- factor(
    df$nb_group,
    levels = stats$nb_group,
    labels = labels
  )

  # Colors: real neighbourhoods via palette, "Other" as neutral grey
  base_colors <- get_nb_color(stats$nb_group)
  if (!is.na(other_label)) {
    base_colors[stats$nb_group == other_label] <- "#808080"
  }
  colors <- setNames(base_colors, labels)

  list(df = df, stats = stats, colors = colors)
}

# Helper to get color palette values
get_mapgl_colors <- function(values, palette_name = "Set1", n_bins = NULL) {
  if(is.null(n_bins)) {
    n_unique <- length(unique(values))
    colors <- RColorBrewer::brewer.pal(min(max(3, n_unique), 9), palette_name)
    if(n_unique > length(colors)) {
      colors <- colorRampPalette(colors)(n_unique)
    }
  } else {
    colors <- RColorBrewer::brewer.pal(min(max(3, n_bins), 9), palette_name)
  }
  colors
}

# ==============================================================================
# CATEGORICAL LEGEND HELPER FUNCTIONS
# ==============================================================================

# Build a robust quantile classification for discrete range-bucket legends.
create_quantile_classification <- function(data, column, n = 5) {
  palette_fn <- \(k) rev(colorRampPalette(RColorBrewer::brewer.pal(9, "RdYlBu"))(k))

  cls <- suppressWarnings(
    tryCatch(
      step_quantile(data = data, column = column, n = n, palette = palette_fn),
      error = function(e) NULL
    )
  )

  if (is.null(cls) || is.null(cls$labels) || length(cls$labels) == 0 || all(is.na(cls$breaks))) {
    unique_vals <- length(unique(na.omit(data[[column]])))
    fallback_n <- if (unique_vals >= 2) min(n, unique_vals) else 2
    cls <- suppressWarnings(
      step_equal_interval(data = data, column = column, n = fallback_n, palette = palette_fn)
    )
  }

  cls
}

# Assign each row to a bucket label based on classification breaks.
# Returns a list with: bucket_col (column values), color_map (named vector), labels (ordered)
assign_buckets <- function(data, column, classification, label_formatter = NULL) {
  values <- data[[column]]
  raw_breaks <- classification$breaks
  colors <- classification$colors

  # step_quantile/step_equal_interval return breaks including min and max boundaries.
  # Extract only internal thresholds (remove first and last) to match label generation.
  if (length(raw_breaks) > 2) {
    breaks <- raw_breaks[-c(1, length(raw_breaks))]
  } else {
    breaks <- raw_breaks
  }

  # Create bucket labels from breaks
  n_buckets <- length(breaks) + 1
  labels <- character(n_buckets)

  if (!is.null(label_formatter)) {
    # label_formatter may return a list with $labels and $breaks (rounded thresholds)
    # or a plain character vector (legacy). When rounded breaks are provided, use them
    # for classification so that map colors match the legend text exactly.
    fmt_result <- label_formatter(breaks)
    if (is.list(fmt_result) && !is.null(fmt_result$labels)) {
      labels <- fmt_result$labels
      if (!is.null(fmt_result$breaks)) {
        breaks <- fmt_result$breaks
        n_buckets <- length(breaks) + 1
      }
    } else {
      labels <- fmt_result
    }
  } else {
    # Default currency formatting
    labels[1] <- paste0("< ", scales::dollar(breaks[1], accuracy = 1))
    if (length(breaks) > 1) {
      for (i in 2:length(breaks)) {
        labels[i] <- paste0(scales::dollar(breaks[i-1], accuracy = 1), " - ", scales::dollar(breaks[i], accuracy = 1))
      }
    }
    labels[n_buckets] <- paste0(scales::dollar(breaks[length(breaks)], accuracy = 1), "+")
  }

  # Ensure colors match label count
  if (length(colors) != length(labels)) {
    colors <- colorRampPalette(colors)(length(labels))
  }

  # Assign each value to a bucket
  bucket_col <- character(length(values))
  for (i in seq_along(values)) {
    val <- values[i]
    if (is.na(val)) {
      bucket_col[i] <- NA_character_
    } else if (val < breaks[1]) {
      bucket_col[i] <- labels[1]
    } else if (val >= breaks[length(breaks)]) {
      bucket_col[i] <- labels[n_buckets]
    } else {
      for (j in 2:length(breaks)) {
        if (val >= breaks[j-1] && val < breaks[j]) {
          bucket_col[i] <- labels[j]
          break
        }
      }
    }
  }

  # Create color map (labels -> colors)
  color_map <- setNames(colors, labels)

  list(
    bucket_col = bucket_col,
    color_map = color_map,
    labels = labels
  )
}

nice_step <- function(values, n_buckets = 5, min_step = NULL) {
  vals <- as.numeric(values)
  vals <- vals[is.finite(vals)]
  if (length(vals) == 0) return(ifelse(is.null(min_step), 1, min_step))

  span <- diff(range(vals))
  target <- if (span > 0) span / n_buckets else max(abs(vals), na.rm = TRUE) / n_buckets
  if (!is.finite(target) || target <= 0) target <- ifelse(is.null(min_step), 1, min_step)

  pow10 <- 10 ^ floor(log10(target))
  ratio <- target / pow10
  mult <- if (ratio <= 1) 1 else if (ratio <= 2) 2 else if (ratio <= 5) 5 else 10
  step <- mult * pow10

  if (!is.null(min_step)) step <- max(step, min_step)
  step
}

currency_min_step <- function(values, profile = c("unit_price", "price_per_lot")) {
  profile <- match.arg(profile)
  vals <- as.numeric(values)
  vals <- vals[is.finite(vals)]
  if (length(vals) == 0) return(1)
  max_abs <- max(abs(vals), na.rm = TRUE)

  if (profile == "price_per_lot") {
    if (max_abs >= 5000000) return(50000)
    if (max_abs >= 1000000) return(10000)
    if (max_abs >= 500000)  return(5000)
    if (max_abs >= 100000)  return(1000)
    if (max_abs >= 50000)   return(500)
    if (max_abs >= 10000)   return(100)
    return(10)
  }

  if (max_abs >= 10000) return(100)
  if (max_abs >= 5000)  return(50)
  if (max_abs >= 1000)  return(10)
  if (max_abs >= 500)   return(5)
  1
}

build_bucket_labels <- function(thresholds, currency = TRUE, step = 1) {
  th <- as.numeric(thresholds)
  th <- th[is.finite(th)]
  if (length(th) == 0) return(character(0))

  # Keep thresholds strictly increasing after rounding so ranges remain readable.
  if (length(th) > 1) {
    for (i in 2:length(th)) {
      if (th[i] <= th[i - 1]) th[i] <- th[i - 1] + step
    }
  }

  label_fmt <- function(x) {
    if (currency) {
      scales::dollar(x, accuracy = max(1, step), big.mark = ",")
    } else {
      scales::number(x, accuracy = step, big.mark = ",")
    }
  }

  labels <- character(length(th) + 1)
  labels[1] <- paste0("< ", label_fmt(th[1]))
  if (length(th) > 1) {
    for (i in 2:length(th)) {
      labels[i] <- paste0(label_fmt(th[i - 1]), " - ", label_fmt(th[i]))
    }
  }
  labels[length(labels)] <- paste0(label_fmt(th[length(th)]), "+")
  labels
}

format_price_bucket_labels <- function(scale_obj, unit_label, kind = c("unit_price", "price_per_lot")) {
  kind <- match.arg(kind)
  cuts <- scale_obj$breaks[-c(1, length(scale_obj$breaks))]
  cuts <- as.numeric(cuts[is.finite(cuts)])

  if (length(cuts) == 0) return(get_legend_labels(scale_obj, format = "currency", digits = 0))

  if (kind == "unit_price" && toupper(unit_label) == "sf") {
    # Request: price/sf legend cutoffs should land on even dollars.
    step <- 2
  } else {
    # For FF/Acre and Price-per-Lot, choose a rounded step based on scale.
    min_step <- currency_min_step(
      cuts,
      profile = if (kind == "price_per_lot") "price_per_lot" else "unit_price"
    )
    step <- nice_step(cuts, n_buckets = 5, min_step = min_step)
  }

  rounded_cuts <- round(cuts / step) * step
  labels <- build_bucket_labels(rounded_cuts, currency = TRUE, step = step)
  list(labels = labels, breaks = rounded_cuts)
}

# ==============================================================================
# FEATURE IMPORTANCE HELPER
# ==============================================================================
# Uses explore::explain_forest() to generate ML feature importance bar charts.
# Whitelist approach: only known predictor columns are considered as features.
# The target column and any all-NA / zero-variance columns are automatically excluded.

fi_prepare_and_plot <- function(df, target_col, ntree = 50) {
  # Whitelist of potential predictor columns across all dashboard types
  feature_candidates <- c(
    "GBA", "YrBlt", "FAR", "Acres", "LandSF", "Stories", "Units",
    "SubDist", "RefDist", "DOM", "CapRate", "CeilingHt",
    "DoorsGrade", "DoorsDock", "ExpRatio",
    "PropMajor", "Condition", "Quality", "Zoning", "ZoningType",
    "Neighborhood", "Visibility", "Access", "View", "MASC"
  )

  # Intersect with columns that actually exist, then remove the target
  available_features <- intersect(feature_candidates, names(df))
  available_features <- setdiff(available_features, target_col)

  # Build analysis dataframe: target + features only
  analysis_df <- df[, c(target_col, available_features), drop = FALSE]

  # Remove rows where target is NA
  analysis_df <- analysis_df[!is.na(analysis_df[[target_col]]), , drop = FALSE]

  # Drop columns that are all-NA, zero-variance, or >50% NA (too sparse)
  n_rows <- nrow(analysis_df)
  keep_cols <- vapply(analysis_df, function(x) {
    na_frac <- sum(is.na(x)) / n_rows
    if (na_frac > 0.5) return(FALSE)
    if (all(is.na(x))) return(FALSE)
    if (is.numeric(x)) {
      valid <- x[!is.na(x)]
      return(length(valid) >= 2 && sd(valid) > 0)
    }
    if (is.character(x) || is.factor(x)) return(length(unique(na.omit(x))) > 1)
    TRUE
  }, logical(1))
  keep_cols[target_col] <- TRUE
  analysis_df <- analysis_df[, keep_cols, drop = FALSE]

  # Convert character columns to factors (randomForest requires factors)
  char_cols <- vapply(analysis_df, is.character, logical(1))
  analysis_df[char_cols] <- lapply(analysis_df[char_cols], as.factor)

  # Impute remaining NAs: median for numeric, "Missing" level for factors
  # (randomForest cannot handle any NA values; na.omit is too aggressive)
  for (col in names(analysis_df)) {
    if (col == target_col) next
    if (any(is.na(analysis_df[[col]]))) {
      if (is.numeric(analysis_df[[col]])) {
        analysis_df[[col]][is.na(analysis_df[[col]])] <- median(analysis_df[[col]], na.rm = TRUE)
      } else if (is.factor(analysis_df[[col]])) {
        levels(analysis_df[[col]]) <- c(levels(analysis_df[[col]]), "Missing")
        analysis_df[[col]][is.na(analysis_df[[col]])] <- "Missing"
      }
    }
  }

  # Need at least 2 feature columns and 10 rows for a meaningful forest
  feature_count <- ncol(analysis_df) - 1
  if (feature_count < 2 || nrow(analysis_df) < 10) {
    return(ggplot() +
      annotate("text", x = 0.5, y = 0.5,
               label = "Insufficient data for feature importance analysis",
               size = 6) +
      theme_void())
  }

  # Run the random forest and return the ggplot object
  tryCatch(
    explore::explain_forest(analysis_df,
                            target = !!rlang::sym(target_col),
                            ntree = ntree,
                            out = "plot"),
    error = function(e) {
      ggplot() +
        annotate("text", x = 0.5, y = 0.5,
                 label = paste0("Feature importance error:\n", e$message),
                 size = 5) +
        theme_void()
    }
  )
}
```

```{r load_data_with_caching, include=FALSE, warning=FALSE}
# ==============================================================================
# DATA LOADING WITH SMART CACHING
# ==============================================================================
# Only re-imports from CSV if SearchPropResults.csv has been modified since
# the last preprocessing. Otherwise loads from cache for faster rendering.

csv_file <- "./SearchPropResults.csv"
cache_file <- "./ADF_preprocessed.RDS"

needs_refresh <- TRUE

if (file.exists(cache_file) && file.exists(csv_file)) {
  cache <- readRDS(cache_file)
  csv_mtime <- file.mtime(csv_file)

  # Check if cache has timestamp and if CSV hasn't changed
  if (!is.null(cache$csv_mtime) && cache$csv_mtime >= csv_mtime) {
    ADF <- cache$data
    needs_refresh <- FALSE
    cat("Loaded", nrow(ADF), "records from cache (CSV unchanged)\n")
  }
}

if (needs_refresh) {
  cat("CSV file changed or no cache - importing fresh data...\n")

  # Load raw data
  ADF <- read_csv(csv_file,
    col_types = cols(
      `Property Id` = col_double(),
      `Ready For Use` = col_character(),
      `Property Type` = col_character(),
      `Property Major Type` = col_character(),
      `Property Sub Type` = col_character(),
      `Land Unit Type` = col_character(),
      Address = col_character(),
      City = col_character(),
      County = col_character(),
      State = col_character(),
      Date = col_date(format = "%m-%d-%Y"),
      Acres = col_double(),
      `Land SF` = col_double(),
      `Land Units` = col_double(),
      View = col_character(),
      Zoning = col_character(),
      GBA = col_double(),
      `No. of Units` = col_double(),
      Quality = col_character(),
      Condition = col_character(),
      `Year Built` = col_character(),
      `Ceiling Height` = col_character(),
      `Transaction Type` = col_character(),
      Price = col_double(),
      `Price Per Acre` = col_double(),
      `Price Per Land SF` = col_double(),
      `Price Per SF` = col_double(),
      `Price Per Unit` = col_double(),
      `Price Per Land Unit` = col_double(),
      `Cap Rate` = col_double(),
      `TOS Cap Rate` = col_double(),
      `Original List Price` = col_double(),
      `Original List Price Difference` = col_double(),
      `Current List Price` = col_double(),
      `Current List Price Difference` = col_double(),
      `Days on Market` = col_double(),
      `Tax ID` = col_character(),
      `Expense Ratio` = col_double(),
      `Year Built Numeric` = col_double(),
      `NOI Per Unit` = col_double(),
      `Improvement Value Per SF` = col_double(),
      `Land Value` = col_double(),
      Grantor = col_character(),
      Grantee = col_character(),
      Latitude = col_double(),
      Longitude = col_double(),
      `MASC Rating` = col_character(),
      Visibility = col_character(),
      Access = col_character(),
      `Percent Tillable` = col_double(),
      Dimensions = col_character(),
      Neighborhood = col_character()
    ), show_col_types = FALSE
  )

  # Rename columns
  rename_map <- c(
    N1ID = "Property Id",
    Ready = "Ready For Use",
    PropMajor = "Property Type",
    PropTypeMajor = "Property Major Type",
    PropSubType = "Property Sub Type",
    LandUnitType = "Land Unit Type",
    Municipality = "County",
    Province = "State",
    Lat = "Latitude",
    Lon = "Longitude",
    LandSF = "Land SF",
    Units = "No. of Units",
    LandUnits = "Land Units",
    DateSold = "Date",
    TrxType = "Transaction Type",
    PriceSold = "Price",
    PriceAcre = "Price Per Acre",
    PriceLandSF = "Price Per Land SF",
    PriceSF = "Price Per SF",
    PriceUnit = "Price Per Unit",
    PriceLandUnit = "Price Per Land Unit",
    DOM = "Days On Market",
    TaxID = "Tax ID",
    CapRate = "Cap Rate",
    PriceListOrig = "Original List Price",
    PriceListOrigDiff = "Original List Price Difference",
    CeilingHt = "Ceiling Height",
    YrBlt = "Year Built Numeric",
    PriceBldgSF = "Improvement Value Per SF",
    LandValue = "Land Value",
    MASC = "MASC Rating",
    PercentCult = "Percent Tillable"
  )

  # Check which columns exist and rename
  existing_cols <- rename_map[rename_map %in% names(ADF)]
  if(length(existing_cols) > 0) {
    ADF <- rename(ADF, !!!existing_cols)
  }

  # Support either source-header casing for DOM and normalize to DOM.
  if (!"DOM" %in% names(ADF)) {
    dom_candidates <- c("Days on Market", "Days On Market")
    dom_col <- dom_candidates[dom_candidates %in% names(ADF)][1]
    if (!is.na(dom_col) && nzchar(dom_col)) {
      ADF <- rename(ADF, DOM = all_of(dom_col))
    }
  }

  # Select relevant columns
  desired_cols <- c("N1ID", "City", "Municipality", "Address", "DateSold",
                    "PriceSold", "Acres", "PriceAcre", "LandSF", "PriceLandSF",
                    "LandUnits", "LandUnitType", "PriceLandUnit", "Zoning",
                    "Neighborhood", "PropMajor", "PropSubType", "TaxID",
                    "Lat", "Lon", "TrxType", "DOM", "PriceListOrig",
                    "PriceListOrigDiff", "Dimensions", "Visibility", "Access")

  ADF <- ADF[, intersect(desired_cols, names(ADF)), drop = FALSE]

  # Filter out listings and pending contracts
  ADF <- filter(ADF, !(TrxType %in% c("Listing", "Pending Contract")))

  # Calculate derived columns
  ADF <- ADF %>% mutate(SaleYear = year(DateSold))

  # Round numeric columns for display
  ADF$PriceAcre <- round(ADF$PriceAcre, 2)
  ADF$PriceLandSF <- round(ADF$PriceLandSF, 4)
  ADF$PriceLandUnit <- round(ADF$PriceLandUnit, 0)

  # Calculate Land Units/Acre density if both columns exist
  if("LandUnits" %in% names(ADF) && "Acres" %in% names(ADF)) {
    ADF <- ADF %>% mutate(DUAcre = ifelse(!is.na(LandUnits) & !is.na(Acres) & Acres > 0,
                                           LandUnits / Acres, NA))
  }

  # Convert DOM to numeric
  ADF$DOM <- as.numeric(as.character(ADF$DOM))

  # Save to cache with CSV timestamp
  saveRDS(list(data = ADF, csv_mtime = file.mtime(csv_file)), cache_file)
  cat("Processed and cached", nrow(ADF), "records\n")
}

# ==============================================================================
# DYNAMIC METRIC SWITCHBOARD
# ==============================================================================
target_price_col <- if(params$AcOrSF == "sf") "PriceLandSF" else "PriceAcre"
target_size_col  <- if(params$AcOrSF == "sf") "LandSF" else "Acres"
unit_label       <- if(params$AcOrSF == "sf") "SF" else "Acre"
unit_label_full  <- if(params$AcOrSF == "sf") "Square Feet" else "Acres"

# Global map circle radius (used by every add_circle_layer call)
circle_radius <- 6

# Dynamic size filter bounds
lo_size <- if(params$AcOrSF == "sf") params$LoLandSizeSF else params$LoLandSizeAc
hi_size <- if(params$AcOrSF == "sf") params$HiLandSizeSF else params$HiLandSizeAc

# Calculate the total range of the X-axis
size_range <- hi_size - lo_size

# Set accuracy based on the SPAN of the data, not just the max value
size_accuracy <- if(params$AcOrSF == "sf") {
  1  # Square feet always rounds to the nearest whole number
} else {
  if(size_range <= 3) 0.01 else  # Tiny range: show 2 decimals (e.g., 2.25)
  if(size_range <= 15) 0.1 else  # Small range: show 1 decimal (e.g., 2.5)
  1                              # Large range: whole numbers only
}

price_accuracy  <- if(params$AcOrSF == "sf") 0.01 else 1
unit_precision   <- if(params$AcOrSF == "sf") 4 else 2
sub_lot_size     <- if(params$AcOrSF == "sf") params$SubLotSF else params$SubLotAc

cat("Switchboard configured for:", toupper(params$AcOrSF), "\n")
```

```{r calculate_parameter_dependent_fields, include=FALSE}
# ------------------------------------------------------------------
# Fill missing Neighborhood via spatial join against WpgNeighbourhoods.
# Any ADF row with a blank/NA Neighborhood but a valid Lat/Lon inside a
# Winnipeg cluster polygon gets that cluster's name. Rows outside all
# polygons (e.g. industrial areas) or outside Winnipeg are handled by
# the City-fallback step below.
# ------------------------------------------------------------------
if (!"Neighborhood" %in% names(ADF)) {
  ADF$Neighborhood <- NA_character_
}

if (!is.null(wpg_neighbourhoods_clustered) && all(c("Lat", "Lon") %in% names(ADF))) {
  needs_nb <- (is.na(ADF$Neighborhood) | ADF$Neighborhood == "") &
              !is.na(ADF$Lat) & !is.na(ADF$Lon)

  if (any(needs_nb)) {
    idx <- which(needs_nb)
    pts <- sf::st_as_sf(
      data.frame(Lon = ADF$Lon[idx], Lat = ADF$Lat[idx]),
      coords = c("Lon", "Lat"),
      crs = 4326
    )

    nb_bnd <- sf::st_transform(
      wpg_neighbourhoods_clustered[, "Neighborhood"],
      sf::st_crs(pts)
    )

    joined <- suppressMessages(
      sf::st_join(pts, nb_bnd, join = sf::st_intersects, left = TRUE)
    )

    matched <- as.character(joined$Neighborhood)
    has_match <- !is.na(matched)
    if (any(has_match)) {
      ADF$Neighborhood[idx[has_match]] <- matched[has_match]
      message(sprintf(
        "Filled %d missing Neighborhood value(s) via spatial join on WpgNeighbourhoodClusters.geojson",
        sum(has_match)
      ))
    }
  }
}

# ------------------------------------------------------------------
# City fallback for non-Winnipeg records.
# Any row that still has a blank/NA Neighborhood and is NOT inside
# Winnipeg (City) gets its City value copied into Neighborhood so that
# downstream charts/filters group these sales by their municipality.
# ------------------------------------------------------------------
if ("City" %in% names(ADF)) {
  still_missing <- is.na(ADF$Neighborhood) | ADF$Neighborhood == ""
  not_winnipeg  <- if ("Municipality" %in% names(ADF)) {
    is.na(ADF$Municipality) | ADF$Municipality != "Winnipeg (City)"
  } else {
    rep(TRUE, nrow(ADF))
  }
  city_has_value <- !is.na(ADF$City) & ADF$City != ""
  use_city <- still_missing & not_winnipeg & city_has_value

  if (any(use_city)) {
    ADF$Neighborhood[use_city] <- as.character(ADF$City[use_city])
    message(sprintf(
      "Filled %d missing Neighborhood value(s) from City for non-Winnipeg records",
      sum(use_city)
    ))
  }
}

# Calculate distance and popup fields (depend on parameters)
ADF$SubDist <- round(distHaversine(cbind(ADF$Lon, ADF$Lat),
                                    c(params$SubLon, params$SubLat)) / 1000, 1)
ADF$RefDist <- round(distHaversine(cbind(ADF$Lon, ADF$Lat),
                                    c(params$RefLon, params$RefLat)) / 1000, 1)
ADF$ChgInDays <- ymd(params$EffDate) - ymd(ADF$DateSold)

# ==============================================================================
# DYNAMIC POPUPS (UNIT-AWARE)
# ==============================================================================
ADF$popup <- paste0(
  "<b>N1 ID:</b> ", ADF$N1ID, "<br>",
  "<b>Address:</b> ", ADF$Address, "<br>",
  "<b>City:</b> ", ADF$City, "<br>",
  "<b>Sale Date:</b> ", ADF$DateSold, "<br>",
  "<b>Price:</b> ", scales::dollar(ADF$PriceSold, accuracy = 1, big.mark = ","), "<br>",

  # Dynamic Size Line
  "<b>", unit_label_full, ":</b> ",
  scales::number(as.numeric(ADF[[target_size_col]]),
                 accuracy = size_accuracy,
                 big.mark = ","), "<br>",

  # Dynamic Price per Unit Line
  "<b>Price/", unit_label, ":</b> ",
  scales::dollar(ADF[[target_price_col]],
                 accuracy = price_accuracy,
                 big.mark = ","), "<br>",

  "<b>Zoning:</b> ", ADF$Zoning, "<br>",
  "<b>Sub Distance:</b> ", ADF$SubDist, " km<br>",
  "<b>Ref Distance:</b> ", ADF$RefDist, " km"
)

# Set circle coordinates for maps
circle_lat <- ifelse(params$SubRef == "Sub", params$SubLat, params$RefLat)
circle_lon <- ifelse(params$SubRef == "Sub", params$SubLon, params$RefLon)

# Create user-defined lists
UDC <- data.frame(City = params$CityList)
# Parse pipe-delimited outliers: "N1ID|Reason" or just "N1ID"
CMSOutliers <- if(length(params$Outliers) > 0 && any(params$Outliers != "")) {
  do.call(rbind, lapply(params$Outliers, function(x) {
    parts <- strsplit(as.character(x), "\\|")[[1]]
    data.frame(
      N1ID = trimws(parts[1]),
      Reason = if(length(parts) > 1) trimws(parts[2]) else "",
      stringsAsFactors = FALSE
    )
  }))
} else {
  data.frame(N1ID = character(0), Reason = character(0), stringsAsFactors = FALSE)
}
ZoningFilterList <- data.frame(N1ID = as.character(params$ZoningFilter))

# Subject property data frame for reference lines
Subject <- data.frame(
  RefDist = round(distHaversine(c(params$SubLon, params$SubLat),
                                 c(params$RefLon, params$RefLat)) / 1000, 1),
  SubDist = 0
)

# Date variables for subtitles
LoDate <- as.Date(params$LoSaleDate)
HiDate <- as.Date(HiSaleDate)

# Find unique property types for color palette
UniquePropTypeADF <- unique(ADF$PropMajor)

cat("Parameter-dependent fields calculated\n")

# Function to add subject and reference markers
add_property_markers <- function(map, params) {
  # Create subject property marker
  subject_marker <- st_sf(
    label = "Subject Property",
    geometry = st_sfc(st_point(c(params$SubLon, params$SubLat)), crs = 4326)
  )

  map <- map |>
    mapgl::add_markers(
      data = subject_marker,
      color = "red",
      popup = "label"
    )

  # Add reference marker if needed
  if (params$SubRef != "Sub") {
    ref_marker <- st_sf(
      label = "Reference Point",
      geometry = st_sfc(st_point(c(params$RefLon, params$RefLat)), crs = 4326)
    )
    map <- map |>
      mapgl::add_markers(
        data = ref_marker,
        color = "black",
        popup = "label"
      )
  }

  map
}
cat("Property Marker Function Defined\n")

# Returns a numeric vector c(xmin, ymin, xmax, ymax) suitable for maplibre(bounds = ...).
compute_map_bounds <- function(sf_data = NULL, params, radius_km = NULL) {
  circle_lat <- ifelse(params$SubRef == "Sub", params$SubLat, params$RefLat)
  circle_lon <- ifelse(params$SubRef == "Sub", params$SubLon, params$RefLon)

  has_sf_data <- !is.null(sf_data) && inherits(sf_data, "sf") && nrow(sf_data) > 0
  if (has_sf_data) {
    data_bbox <- st_bbox(sf_data)
    xmin <- data_bbox["xmin"]
    xmax <- data_bbox["xmax"]
    ymin <- data_bbox["ymin"]
    ymax <- data_bbox["ymax"]
  } else {
    xmin <- xmax <- circle_lon
    ymin <- ymax <- circle_lat
  }

  # Always include the subject marker.
  xmin <- min(xmin, params$SubLon)
  xmax <- max(xmax, params$SubLon)
  ymin <- min(ymin, params$SubLat)
  ymax <- max(ymax, params$SubLat)

  # Include reference marker when applicable.
  if (params$SubRef != "Sub") {
    xmin <- min(xmin, params$RefLon)
    xmax <- max(xmax, params$RefLon)
    ymin <- min(ymin, params$RefLat)
    ymax <- max(ymax, params$RefLat)
  }

  # Fit to the outer distance ring (and top label offset) ONLY when
  # params$ShowRadius == "Y". Otherwise the bbox stays at data extent so the
  # map zooms tight to the points. Default (missing param) = "N".
  show_radius <- !is.null(params$ShowRadius) &&
                 toupper(as.character(params$ShowRadius)) == "Y"
  if (show_radius && !is.null(radius_km) && is.finite(radius_km) && radius_km > 0) {
    lat_rad <- circle_lat * pi / 180
    lat_offset <- radius_km / 111
    lon_offset <- radius_km / (111 * cos(lat_rad))
    label_offset <- (radius_km / 111) * 0.15 + 0.005

    xmin <- min(xmin, circle_lon - lon_offset)
    xmax <- max(xmax, circle_lon + lon_offset)
    ymin <- min(ymin, circle_lat - lat_offset)
    ymax <- max(ymax, circle_lat + lat_offset + label_offset)
  }

  # Avoid zero-width/height bounds for single-point maps.
  if (isTRUE(all.equal(xmin, xmax))) {
    xmin <- xmin - 0.005
    xmax <- xmax + 0.005
  }
  if (isTRUE(all.equal(ymin, ymax))) {
    ymin <- ymin - 0.005
    ymax <- ymax + 0.005
  }

  # Pad the bbox so edge markers aren't clipped in exported PNGs / tight
  # dashboard views. When ShowRadius == "Y" the radius ring already provides
  # slack, so we use a smaller pad; when ShowRadius == "N" the bbox hugs the
  # data tightly and needs a bigger pad (~8% of span each side).
  pad_frac <- if (show_radius) 0.02 else 0.07
  x_span <- xmax - xmin
  y_span <- ymax - ymin
  xmin <- xmin - x_span * pad_frac
  xmax <- xmax + x_span * pad_frac
  ymin <- ymin - y_span * pad_frac
  ymax <- ymax + y_span * pad_frac

  as.numeric(c(xmin, ymin, xmax, ymax))
}
cat("Map Bounds Function Defined\n")
```

```{r apply_cms_filters, include=FALSE}
# ==============================================================================
# APPLY FILTERS TO CREATE CMS (Comparable Market Set) - SWITCHBOARD PATTERN
# ==============================================================================

# Determine filter mode flags
prop_major_filter <- length(params$PropMajorInc) > 0 &&
                     !all(params$PropMajorInc == "")

# Apply CMS filters using switchboard variables (lo_size, hi_size, target_size_col)
CMS1 <- ADF %>%
  filter(
    between(DateSold, as.Date(params$LoSaleDate), as.Date(HiSaleDate)),
    !N1ID %in% CMSOutliers$N1ID
  ) %>%
  # Dynamic Land Size Filter using switchboard
  filter(between(as.numeric(.data[[target_size_col]]), lo_size, hi_size)) %>%
  # Zoning Filter Logic
  {if (!is.null(params$ZoningFilter) && length(params$ZoningFilter) > 0 && any(params$ZoningFilter != "")) {
    filter(., Zoning %in% params$ZoningFilter)
  } else .} %>%
  # Apply distance filter
  {if(params$SubRef == "Ref") {
    filter(., between(RefDist, params$LoDistKM, params$HiDistKM))
  } else {
    filter(., SubDist <= params$HiDistKM)
  }} %>%
  # Apply property major type filter
  {if(prop_major_filter) {
    filter(., PropMajor %in% params$PropMajorInc)
  } else .} %>%
  # Apply UC filter
  apply_uc_filter(params$UCFilter, params$UCFilterList) %>%
  # Filter by Neighborhood (only exclude when NeighborhoodExcl has real values)
  filter(
    if ("Neighborhood" %in% names(.) &&
        length(params$NeighborhoodExcl) > 0 &&
        any(params$NeighborhoodExcl != "")) {
      !Neighborhood %in% params$NeighborhoodExcl
    } else {
      TRUE
    }
  )

cat(paste0("CMS Filtered using ", unit_label, ": ", nrow(CMS1), " records\n"))

CMS1$popup <- ADF$popup[ADF$N1ID %in% CMS1$N1ID]

cat("CMS filtered:", nrow(CMS1), "records\n")

# ==============================================================================
# MULTI-FAMILY DATA PREPARATION (CMSLU)
# Built from CMS1: first drop records with no LandUnits, then apply the
# YAML LoLandSizeUnit/HiLandSizeUnit range filter, then optionally filter
# by Land Unit Type (Apartment/Condo/Lot/Other) per LandUnitType YAML param.
# ==============================================================================
if(params$PricePerUnit == "Y") {
  # Determine whether the LandUnitType filter is active.
  # Empty list, all-blank list, or NULL = include ALL records (no filter).
  lut_filter_active <- !is.null(params$LandUnitType) &&
                       length(params$LandUnitType) > 0 &&
                       any(params$LandUnitType != "")

  CMSLU <- CMS1 %>%
    # 1. Drop records where LandUnits / PriceLandUnit are missing or non-positive
    filter(
      !is.na(LandUnits),
      !is.na(PriceLandUnit),
      PriceLandUnit > 0
    ) %>%
    # 2. Apply unit-count range filter from YAML params
    filter(between(LandUnits, params$LoLandSizeUnit, params$HiLandSizeUnit)) %>%
    # 3. Optionally filter by Land Unit Type
    {if (lut_filter_active && "LandUnitType" %in% names(.)) {
      filter(., LandUnitType %in% params$LandUnitType)
    } else .}

  cat("Multi-Family CMS (CMSLU) created with", nrow(CMSLU), "records",
      if(lut_filter_active) paste0(" (LandUnitType filter: ", paste(params$LandUnitType, collapse=", "), ")") else " (no LandUnitType filter)",
      ".\n", sep="")
} else {
  CMSLU <- data.frame() # Empty if not enabled
}

cat("CMS with Land Units (Filtered):", nrow(CMSLU), "records\n")
```

```{r market_condition_adjustments, include=FALSE}
# ==============================================================================
# MARKET CONDITION ANALYSIS (DYNAMIC UNIT VERSION)
# ==============================================================================

# 1. INITIAL ANALYSIS (Full CMS1) - Using switchboard pattern
if(nrow(CMS1) > 2) {
  # Dynamic Regression formula
  formula_str <- paste(target_price_col, "~ as.numeric(DateSold)")
  MktCond1 <- lm(as.formula(formula_str), data = CMS1)
  MktCondVal1 <- round(coef(MktCond1)[2], 6)

  # Calculate statistics
  MedianPriceUnit1 <- median(CMS1[[target_price_col]], na.rm = TRUE)
  MeanPriceUnit1 <- mean(CMS1[[target_price_col]], na.rm = TRUE)

  # Apply time adjustments to CMS1
  CMS1 <- CMS1 %>%
    mutate(
      MktCondAdj = coef(MktCond1)[2],
      AdjPrice = round((MktCondAdj * as.numeric(ChgInDays)) + .data[[target_price_col]], unit_precision)
    )

  # Calculate annual increase
  AnnualIncreaseDol1 <- coef(MktCond1)[2] * 365
  AnnualIncreasePer1 <- AnnualIncreaseDol1 / MedianPriceUnit1
} else {
  MktCondVal1 <- 0
  MedianPriceUnit1 <- NA_real_
  AnnualIncreasePer1 <- 0
  CMS1$AdjPrice <- CMS1[[target_price_col]]
}

# ----------------------------------------------------------------------------
# CMS1 PRICE-PER-ACRE TIME ADJUSTMENT (always fitted, regardless of AcOrSF)
# Used by all multi-family / CMSLU time-adjusted charts so that the rate is
# anchored to the broader CMS1 trend rather than refitted on the smaller
# CMSLU subset.
# ----------------------------------------------------------------------------
if(nrow(CMS1) > 2 && "PriceAcre" %in% names(CMS1)) {
  MktCondAc1 <- lm(PriceAcre ~ as.numeric(DateSold), data = CMS1)
  MktCondValAc1 <- round(coef(MktCondAc1)[2], 6)   # $/Acre/day
  MedianPriceAc1 <- median(CMS1$PriceAcre, na.rm = TRUE)
  PctChgPerDayAc1 <- if(!is.na(MedianPriceAc1) && MedianPriceAc1 > 0) {
    MktCondValAc1 / MedianPriceAc1
  } else 0
} else {
  MktCondValAc1 <- 0
  MedianPriceAc1 <- NA_real_
  PctChgPerDayAc1 <- 0
}

# 2. LAND UNIT ANALYSIS (if enabled)
# Time adjustments are NOT refitted on CMSLU - they reuse the CMS1-derived
# daily rate (MktCondVal1, which is $/Acre/day or $/SF/day depending on the
# AcOrSF switchboard) and the $/Ac-based percentage-per-day rate
# (PctChgPerDayAc1) for the per-unit percentage adjustment.
if(params$PricePerUnit == "Y" && nrow(CMSLU) > 2) {
  CMSLU <- CMSLU %>%
    mutate(
      # Dynamic per-unit (Acre or SF) adjustment: adds the CMS1 daily rate
      # to whichever nominal price column is selected by AcOrSF.
      AdjPriceLU = round(.data[[target_price_col]] +
                         MktCondVal1 * as.numeric(ChgInDays),
                         unit_precision),
      # Per-Land-Unit adjustment: percentage growth derived from CMS1 $/Ac trend
      AdjPriceUnit = round(PriceLandUnit * (1 + PctChgPerDayAc1 * as.numeric(ChgInDays)), 0)
    )
}

# 3. OUTLIER-RESISTANT ANALYSIS (CMS2: 5th-95th Percentile)
if(nrow(CMS1) > 5) {
  # Calculate quantiles based on selected unit
  CMS_Quantiles1 <- quantile(CMS1[[target_price_col]], probs = c(0.05, 0.95), na.rm = TRUE)

  CMS2 <- CMS1 %>%
    filter(.data[[target_price_col]] >= CMS_Quantiles1[["5%"]] &
           .data[[target_price_col]] <= CMS_Quantiles1[["95%"]])

  if(nrow(CMS2) > 2) {
    formula_str2 <- paste(target_price_col, "~ as.numeric(DateSold)")
    MktCond2 <- lm(as.formula(formula_str2), data = CMS2)
    MktCondVal2 <- round(coef(MktCond2)[2], unit_precision)
    MedianPriceUnit2 <- median(CMS2[[target_price_col]], na.rm = TRUE)

    # Apply secondary adjustments to CMS2
    CMS2 <- CMS2 %>%
      mutate(
        # Ensure CMS2 market-condition columns are based on the CMS2 trend, not inherited CMS1 values.
        MktCondAdj = coef(MktCond2)[2],
        AdjPrice = round((MktCondAdj * as.numeric(ChgInDays)) + .data[[target_price_col]], unit_precision)
      )

    AnnualIncreaseDol2 <- coef(MktCond2)[2] * 365
    AnnualIncreasePer2 <- AnnualIncreaseDol2 / MedianPriceUnit2
  } else {
    MktCondVal2 <- 0
    MedianPriceUnit2 <- NA_real_
    AnnualIncreasePer2 <- 0
    CMS2 <- CMS2 %>%
      mutate(
        MktCondAdj = MktCondVal2,
        AdjPrice = .data[[target_price_col]]
      )
  }
} else {
  CMS2 <- CMS1
  MktCondVal2 <- MktCondVal1
  MedianPriceUnit2 <- MedianPriceUnit1
  AnnualIncreasePer2 <- AnnualIncreasePer1
  CMS2 <- CMS2 %>%
    mutate(
      MktCondAdj = MktCondVal2,
      AdjPrice = round((MktCondAdj * as.numeric(ChgInDays)) + .data[[target_price_col]], unit_precision)
    )
}

# Date formatting for axis labels - max 6 breaks
cms_date_min <- min(CMS1$DateSold, na.rm = TRUE)
cms_date_max <- max(CMS1$DateSold, na.rm = TRUE)
date_breaks_vec <- pretty(c(cms_date_min, cms_date_max), n = 5)
date_breaks_vec <- as.Date(date_breaks_vec, origin = "1970-01-01")
date_label_format <- "%b-%Y"

# Dynamic subtitle templates
Subtitle1 <- paste0("CMS; ",
  ifelse(params$SubRef == "Ref",
         paste0(params$LoDistKM, "-", params$HiDistKM),
         paste0(params$LoDistKM, "-", params$HiDistKM)),
  " km from ",
  ifelse(params$SubRef == "Ref", params$RefPoint, "subject"),
  "; ",
  if(params$AcOrSF == "sf") paste0(format(lo_size, big.mark=","), "-", format(hi_size, big.mark=","), " sf")
  else paste0(lo_size, "-", hi_size, " acres"),
  "; ", format(LoDate, "%b-%Y"), " to ", format(HiDate, "%b-%Y")
)

Subtitle2 <- paste0("CMS (Time-Adjusted); ",
  ifelse(params$SubRef == "Ref",
         paste0(params$LoDistKM, "-", params$HiDistKM),
         paste0(params$LoDistKM, "-", params$HiDistKM)),
  " km from ",
  ifelse(params$SubRef == "Ref", params$RefPoint, "subject"),
  "; ",
  if(params$AcOrSF == "sf") paste0(format(lo_size, big.mark=","), "-", format(hi_size, big.mark=","), " SF")
  else paste0(lo_size, "-", hi_size, " acres"),
  "; ", format(LoDate, "%b-%Y"), " to ", format(HiDate, "%b-%Y")
)

Subtitle3 <- paste0("CMS (5th-95th Percentile); ",
  ifelse(params$SubRef == "Ref",
         paste0(params$LoDistKM, "-", params$HiDistKM),
         paste0(params$LoDistKM, "-", params$HiDistKM)),
  " km from ",
  ifelse(params$SubRef == "Ref", params$RefPoint, "subject"),
  "; ",
  if(params$AcOrSF == "sf") paste0(format(lo_size, big.mark=","), "-", format(hi_size, big.mark=","), " SF")
  else paste0(lo_size, "-", hi_size, " acres"),
  "; ", format(LoDate, "%b-%Y"), " to ", format(HiDate, "%b-%Y")
)

Subtitle4 <- paste0("CMS (5th-95th Percentile, Time-Adjusted); ",
  ifelse(params$SubRef == "Ref",
         paste0(params$LoDistKM, "-", params$HiDistKM),
         paste0(params$LoDistKM, "-", params$HiDistKM)),
  " km from ",
  ifelse(params$SubRef == "Ref", params$RefPoint, "subject"),
  "; ",
  if(params$AcOrSF == "sf") paste0(format(lo_size, big.mark=","), "-", format(hi_size, big.mark=","), " SF")
  else paste0(lo_size, "-", hi_size, " acres"),
  "; ", format(LoDate, "%b-%Y"), " to ", format(HiDate, "%b-%Y")
)

cat("Market conditions calculated\n")
cat("  CMS1: Daily", unit_label, "change = $", MktCondVal1, "\n")
cat("  CMS2:", nrow(CMS2), "records (5th-95th percentile)\n")
```

```{r exposure_data_prep, include=FALSE}
# Only prepare exposure data if ExposureCharts is enabled
if(params$ExposureCharts == "Y") {
  ADF_Exp <- ADF %>%
    filter(
      !is.na(DOM),
      DateSold >= params$LoSaleDate,
      DateSold <= params$HiSaleDate,
      PriceSold >= params$ExposurePriceMin,
      PriceSold <= params$ExposurePriceMax
    ) %>%
    mutate(DOM_capped = pmin(DOM, 1170))

  CMS_Exp <- CMS1 %>%
    filter(
      !is.na(DOM),
      PriceSold >= params$ExposurePriceMin,
      PriceSold <= params$ExposurePriceMax
    ) %>%
    mutate(DOM_capped = pmin(DOM, 1170))

  cat("Exposure data prepared:", nrow(CMS_Exp), "records\n")
} else {
  # Create empty dataframes to prevent errors if ExposureCharts = N
  ADF_Exp <- data.frame()
  CMS_Exp <- data.frame()
}
```

```{r color_palettes, include=FALSE}
# Property type color palette using Set1 colors
prop_types <- unique(ADF$PropMajor)
set1_colors <- c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00",
                 "#ffff33", "#a65628", "#f781bf", "#999999")
prop_color_map <- setNames(set1_colors[1:length(prop_types)], prop_types)

# Zoning color palette using Set2 colors
zoning_types <- unique(ADF$Zoning)
zoning_colors <- get_mapgl_colors(zoning_types, "Set2")
zoning_color_map <- setNames(zoning_colors[1:length(zoning_types)], zoning_types)

# Municipality colors
muni_levels <- unique(ADF$Municipality)
muni_colors <- get_mapgl_colors(muni_levels, "Set1")
muni_color_map <- setNames(muni_colors[1:length(muni_levels)], muni_levels)

# Pre-compute colors for ADF
ADF$fill_color <- prop_color_map[ADF$PropMajor]
ADF$zoning_fill_color <- zoning_color_map[ADF$Zoning]

# Helper function to create sf object from data frame with lat/lon
make_points_sf <- function(df) {
  df %>%
    filter(!is.na(Lon) & !is.na(Lat)) %>%
    st_as_sf(coords = c("Lon", "Lat"), crs = 4326)
}

# Add satellite layer helper for mapgl
add_satellite_layer <- function(map, source_id = "satellite-source", layer_id = "satellite-layer") {
  map |>
    add_raster_source(
      id = source_id,
      tiles = "https://server.arcgisonline.com/ArcGIS/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}",
      tileSize = 256,
      maxzoom = 19
    ) |>
    add_raster_layer(
      id = layer_id,
      source = source_id,
      visibility = "none"
    )
}
```

```{r precompute_spatial, include=FALSE}
# ==============================================================================
# PRECOMPUTE SHARED SPATIAL OBJECTS
# Boundary subsets and base sf objects are identical across multiple map chunks.
# Computing them once here avoids redundant work during rendering.
# ==============================================================================

# ADF: base sf + boundaries (shared by 2 ADF map chunks)
ADF <- ADF %>% mutate(tooltip = make_tooltip(cur_data(), unit_label, params$AcOrSF))
ADF_sf_base <- make_points_sf(ADF)
muni_bnd_adf <- prep_muni_bnd(get_filtered_muni_boundaries(ADF), muni_color_map)
wpg_nb_bnd_adf <- prep_wpg_nb_bnd(get_filtered_wpg_nb_boundaries(ADF))
map_bbox_adf <- compute_map_bounds(ADF_sf_base, params)

# CMS1: base sf + boundaries (shared by 3 CMS map chunks)
if (nrow(CMS1) > 0) {
  CMS1$fill_color <- prop_color_map[CMS1$PropMajor]
  CMS1$zoning_fill_color <- zoning_color_map[CMS1$Zoning]
  CMS1 <- CMS1 %>% mutate(tooltip = make_tooltip(cur_data(), unit_label, params$AcOrSF))
  CMS1_sf_base <- make_points_sf(CMS1)
  muni_bnd_cms1 <- prep_muni_bnd(get_filtered_muni_boundaries(CMS1), muni_color_map)
  wpg_nb_bnd_cms1 <- prep_wpg_nb_bnd(get_filtered_wpg_nb_boundaries(CMS1))
  map_bbox_cms1 <- compute_map_bounds(CMS1_sf_base, params, radius_km = params$HiDistKM)
}

# CMS2: base sf + boundaries (shared by CMS2 map chunks)
if (nrow(CMS2) > 0) {
  CMS2$fill_color <- prop_color_map[CMS2$PropMajor]
  CMS2$zoning_fill_color <- zoning_color_map[CMS2$Zoning]
  CMS2 <- CMS2 %>% mutate(tooltip = make_tooltip(cur_data(), unit_label, params$AcOrSF))
  CMS2_sf_base <- make_points_sf(CMS2)
  muni_bnd_cms2 <- prep_muni_bnd(get_filtered_muni_boundaries(CMS2), muni_color_map)
  wpg_nb_bnd_cms2 <- prep_wpg_nb_bnd(get_filtered_wpg_nb_boundaries(CMS2))
  map_bbox_cms2 <- compute_map_bounds(CMS2_sf_base, params, radius_km = params$HiDistKM)
}
```

# ADF Overview {orientation="rows"}

## Row {height=50% .tabset}

### Heatmap - Property Type
```{r adf_map, warning=FALSE}
#| title: "ADF - All Data by Property Type"

# Create spatial version if Dimensions exist
ADF_spatial <- ADF %>%
  filter(!is.na(Dimensions) & Dimensions != "") %>%
  mutate(geometry = st_as_sfc(Dimensions, crs = 4326)) %>%
  st_as_sf()

# Add fill_color to spatial data
if(nrow(ADF_spatial) > 0) {
  ADF_spatial$fill_color <- prop_color_map[ADF_spatial$PropMajor]
}

# Use precomputed sf with tooltip already on ADF
ADF_sf <- ADF_sf_base

# Create match expression for categorical coloring by property type
adf_proptype_match_expr <- match_expr(
  column = "PropMajor",
  values = names(prop_color_map),
  stops = unname(prop_color_map),
  default = "#808080"
)

# Build base map with boundaries
Map1ADF <- build_base_map(
  bounds = map_bbox_adf,
  muni_bnd = muni_bnd_adf, wpg_nb_bnd = wpg_nb_bnd_adf,
  muni_color_map = muni_color_map, id_prefix = "adf_proptype",
  circle_lon = circle_lon, circle_lat = circle_lat,
  lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = FALSE
)

# Add polygons if spatial data exists
if(nrow(ADF_spatial) > 0) {
  Map1ADF <- Map1ADF |>
    add_fill_layer(
      id = "adf-polygons-fill",
      source = ADF_spatial,
      fill_color = get_column("fill_color"),
      fill_opacity = 0.3,
      popup = "popup"
    ) |>
    add_line_layer(
      id = "adf-polygons-outline",
      source = ADF_spatial,
      line_color = "black",
      line_width = 1
    )
}

Map1ADF <- Map1ADF |>
  add_circle_layer(
    id = "adf-points",
    source = ADF_sf,
    circle_color = adf_proptype_match_expr,
    circle_radius = circle_radius,
    circle_stroke_color = "black",
    circle_stroke_width = 1,
    circle_opacity = 0.7,
    tooltip = "tooltip",
    popup = "popup"
  ) |>
  add_property_markers(params) |>
  add_legend(
    legend_title = "Property Type",
    values = sort(names(prop_color_map)),
    colors = unname(prop_color_map[sort(names(prop_color_map))]),
    type = "categorical",
    layer_id = "adf-points",
    interactive = TRUE,
    position = "bottom-right"
  )
Map1ADF
```

```{r map_adf_heatmap, warning=FALSE}
#| title: !expr paste("ADF - All Data by Price/", unit_label)

# Use precomputed sf with tooltip (filter for non-NA price)
ADF_sf <- ADF_sf_base %>% filter(!is.na(.data[[target_price_col]]))

# Discrete quantile color scale (5 buckets with rounded values)
adf_price_scale <- create_quantile_classification(
  data = ADF_sf,
  column = target_price_col,
  n = 5
)

# Assign each point to a price bucket for categorical legend interactivity
adf_buckets <- assign_buckets(
  data = ADF_sf,
  column = target_price_col,
  classification = adf_price_scale,
  label_formatter = function(breaks) format_price_bucket_labels(adf_price_scale, unit_label, kind = "unit_price")
)
ADF_sf$price_bucket <- adf_buckets$bucket_col

# Create match expression for categorical coloring
adf_price_match_expr <- match_expr(
  column = "price_bucket",
  values = adf_buckets$labels,
  stops = unname(adf_buckets$color_map),
  default = "#808080"
)

# Build base map with boundaries
Map1ADFH <- build_base_map(
  bounds = map_bbox_adf,
  muni_bnd = muni_bnd_adf, wpg_nb_bnd = wpg_nb_bnd_adf,
  muni_color_map = muni_color_map, id_prefix = "adf_heatmap",
  circle_lon = circle_lon, circle_lat = circle_lat,
  lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = FALSE
)

# Add data layer and categorical legend (click legend items to show/hide)
Map1ADFH <- Map1ADFH |>
  add_circle_layer(
    id = "adf-heatmap",
    source = ADF_sf,
    circle_color = adf_price_match_expr,
    circle_radius = circle_radius,
    circle_stroke_color = "black",
    circle_stroke_width = 1,
    circle_opacity = 0.8,
    tooltip = "tooltip",
    popup = "popup"
  ) |>
  add_property_markers(params) |>
  add_legend(
    legend_title = paste0("Sale Price/", unit_label),
    values = adf_buckets$labels,
    colors = unname(adf_buckets$color_map),
    type = "categorical",
    layer_id = "adf-heatmap",
    interactive = TRUE,
    position = "bottom-right"
  )

Map1ADFH
```
### Heatmap - Zoning
```{r adf_map_zoning, warning=FALSE}
#| title: "ADF - All Data by Zoning"

# Create spatial version if Dimensions exist
ADF_spatial_z <- ADF %>%
  filter(!is.na(Dimensions) & Dimensions != "") %>%
  mutate(geometry = st_as_sfc(Dimensions, crs = 4326)) %>%
  st_as_sf()

# Add zoning fill_color to spatial data
if(nrow(ADF_spatial_z) > 0) {
  ADF_spatial_z$zoning_fill_color <- zoning_color_map[ADF_spatial_z$Zoning]
}

# Use precomputed sf with tooltip already on ADF
ADF_sf_z <- ADF_sf_base

# Create match expression for categorical coloring by zoning
adf_zoning_match_expr <- match_expr(
  column = "Zoning",
  values = names(zoning_color_map),
  stops = unname(zoning_color_map),
  default = "#808080"
)

# Build base map with boundaries
Map1ADF_Z <- build_base_map(
  bounds = map_bbox_adf,
  muni_bnd = muni_bnd_adf, wpg_nb_bnd = wpg_nb_bnd_adf,
  muni_color_map = muni_color_map, id_prefix = "adf_zoning",
  circle_lon = circle_lon, circle_lat = circle_lat,
  lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = FALSE
)

# Add polygons if spatial data exists
if(nrow(ADF_spatial_z) > 0) {
  Map1ADF_Z <- Map1ADF_Z |>
    add_fill_layer(
      id = "adf-zoning-polygons-fill",
      source = ADF_spatial_z,
      fill_color = get_column("zoning_fill_color"),
      fill_opacity = 0.3,
      popup = "popup"
    ) |>
    add_line_layer(
      id = "adf-zoning-polygons-outline",
      source = ADF_spatial_z,
      line_color = "black",
      line_width = 1
    )
}

Map1ADF_Z <- Map1ADF_Z |>
  add_circle_layer(
    id = "adf-zoning-points",
    source = ADF_sf_z,
    circle_color = adf_zoning_match_expr,
    circle_radius = circle_radius,
    circle_stroke_color = "black",
    circle_stroke_width = 1,
    circle_opacity = 0.7,
    tooltip = "tooltip",
    popup = "popup"
  ) |>
  add_property_markers(params) |>
  add_legend(
    legend_title = "Zoning",
    values = sort(names(zoning_color_map)),
    colors = unname(zoning_color_map[sort(names(zoning_color_map))]),
    type = "categorical",
    layer_id = "adf-zoning-points",
    interactive = TRUE,
    position = "bottom-right"
  )
Map1ADF_Z
```

```{r adf_map_neighbourhood, warning=FALSE}
#| title: "ADF - All Data by Neighbourhood"

if ("Neighborhood" %in% names(ADF) && sum(!is.na(ADF$Neighborhood) & ADF$Neighborhood != "") > 0) {
  # Create neighbourhood color map using WRHA palette
  adf_neighborhoods <- unique(ADF$Neighborhood[!is.na(ADF$Neighborhood) & ADF$Neighborhood != ""])
  adf_nb_colors <- get_nb_color(adf_neighborhoods)
  adf_nb_color_map <- setNames(adf_nb_colors, adf_neighborhoods)

  # Create sf from ADF with neighbourhood data
  ADF_sf_nb <- ADF %>%
    filter(!is.na(Lon) & !is.na(Lat) & !is.na(Neighborhood) & Neighborhood != "") %>%
    st_as_sf(coords = c("Lon", "Lat"), crs = 4326)

  # Create match expression for categorical coloring by neighbourhood
  adf_nb_match_expr <- match_expr(
    column = "Neighborhood",
    values = names(adf_nb_color_map),
    stops = unname(adf_nb_color_map),
    default = "#808080"
  )

  # Build base map with neighbourhood boundaries (no muni boundaries)
  MapADFN <- build_base_map(
    bounds = map_bbox_adf,
    muni_bnd = NULL, wpg_nb_bnd = wpg_nb_bnd_adf,
    muni_color_map = muni_color_map, id_prefix = "adf_nb",
    circle_lon = circle_lon, circle_lat = circle_lat,
    lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = FALSE
  ) |>
    add_property_markers(params)

  MapADFN <- MapADFN |>
    add_circle_layer(
      id = "adf-neighborhood-points",
      source = ADF_sf_nb,
      circle_color = adf_nb_match_expr,
      circle_radius = circle_radius,
      circle_stroke_color = "black",
      circle_stroke_width = 1,
      circle_opacity = 0.7,
      tooltip = "tooltip",
      popup = "popup"
    ) |>
    add_legend(
      legend_title = "Neighbourhood",
      values = sort(names(adf_nb_color_map)),
      colors = unname(adf_nb_color_map[sort(names(adf_nb_color_map))]),
      type = "categorical",
      layer_id = "adf-neighborhood-points",
      interactive = TRUE,
      position = "bottom-right"
    )

  MapADFN
} else {
  empty_map()
}
```

## Row {height=50% .tabset}

### Price/`r unit_label` Over Time
```{r adf_trend, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#| title: !expr paste("ADF - Overall Trend - All Data by Price/", unit_label)

# ADF date axis: always use year-based breaks and labels
adf_range_years <- as.numeric(difftime(max(ADF$DateSold, na.rm = TRUE),
                                       min(ADF$DateSold, na.rm = TRUE),
                                       units = "days")) / 365
adf_break_interval <- case_when(
  adf_range_years <= 3 ~ "1 year",
  adf_range_years <= 10 ~ "2 years",
  TRUE ~ "5 years"
)
adf_label_format <- "%Y"

ADFTrend <- ggplot(ADF, aes(DateSold, .data[[target_price_col]])) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F, color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F, color = "red4", linewidth = 1,
              linetype = "dashed") +
  scale_y_continuous(labels = dollar, limits = c(0, NA), breaks = scales::pretty_breaks(n = 5)) +
  scale_x_date(date_breaks = adf_break_interval, date_labels = adf_label_format) +
  theme_custom() +
  theme_point_colour() +
  labs(title = paste0("Overall Trend - Land Sale Price per ", unit_label),
       subtitle = "Assignment Data Frame (ADF)",
       x = "Sale Date",
       y = paste0("Sale Price per ", unit_label),
       caption = params$Company)
ADFTrend
```

```{r adf_interactive_trend, warning=FALSE}
#| title: !expr paste("ADF - Interactive Data by Price/", unit_label)

p <- ggplot(ADF, aes(DateSold, .data[[target_price_col]])) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  geom_point(aes(fill = PropMajor, color = PropMajor,
                 text = paste0("N1ID: ", N1ID, "<br>",
                                "Address: ", Address, "<br>",
                                "City: ", City, "<br>",
                                "Type: ", PropMajor, "<br>",
                                "Zoning: ", Zoning, "<br>",
                                unit_label_full, ": ", scales::number(.data[[target_size_col]], accuracy = size_accuracy, big.mark = ","), "<br>",
                                "Price/", unit_label, ": ", dollar(.data[[target_price_col]], accuracy = price_accuracy))),
             shape = 21, size = 3, alpha = 0.6, stroke = 0.5) +
  scale_fill_manual(values = prop_color_map) +
  scale_color_manual(values = prop_color_map) +
  scale_y_continuous(labels = dollar, limits = c(0, NA)) +
  theme_custom() +
  labs(
    title = paste0("ADF Land Price per ", unit_label, " Over Time (Interactive)"),
    x = "Sale Date",
    y = paste0("Price per ", unit_label),
    fill = "Property Type",
    color = "Property Type"
  )

ggplotly(p, tooltip = "text")
```

```{r adf_interactive_size, warning=FALSE}
#| title: !expr paste("ADF - Interactive Price per", unit_label, "by Parcel Size")

p_size <- ggplot(ADF, aes(.data[[target_size_col]], .data[[target_price_col]])) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  geom_point(aes(fill = PropMajor, color = PropMajor,
                 text = paste0("N1ID: ", N1ID, "<br>",
                                "Address: ", Address, "<br>",
                                "City: ", City, "<br>",
                                "Type: ", PropMajor, "<br>",
                                "Zoning: ", Zoning, "<br>",
                                unit_label_full, ": ", scales::number(.data[[target_size_col]], accuracy = size_accuracy, big.mark = ","), "<br>",
                                "Price/", unit_label, ": ", dollar(.data[[target_price_col]], accuracy = price_accuracy))),
             shape = 21, size = 3, alpha = 0.6, stroke = 0.5) +
  scale_fill_manual(values = prop_color_map) +
  scale_color_manual(values = prop_color_map) +
  scale_y_continuous(labels = dollar, limits = c(0, NA)) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  theme_custom() +
  labs(
    title = paste0("ADF Land Price per ", unit_label, " by Parcel Size (Interactive)"),
    x = unit_label_full,
    y = paste0("Price per ", unit_label),
    fill = "Property Type",
    color = "Property Type"
  )

ggplotly(p_size, tooltip = "text")
```

### Price/`r unit_label` by Neighbourhood
```{r adf_neighbourhood_boxplot, echo=FALSE, message=FALSE, warning=FALSE}
#| title: !expr paste("ADF - Price/", unit_label, "by Neighbourhood")

if ("Neighborhood" %in% names(ADF) && length(unique(ADF$Neighborhood[!is.na(ADF$Neighborhood) & ADF$Neighborhood != ""])) > 0) {
  .rollup <- rollup_neighbourhoods_for_boxplot(ADF, target_price_col, max_bars = 10)
  adf_nb        <- .rollup$df
  nb_stats      <- .rollup$stats
  nb_colors_adf <- .rollup$colors

  ggplot(adf_nb, aes(x = Neighborhood, y = .data[[target_price_col]], fill = Neighborhood)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_jitter(width = 0.15, size = 1.5, alpha = 0.4, color = "steelblue4") +
    geom_text(data = nb_stats,
              aes(x = Neighborhood, y = q3, label = dollar(med, accuracy = price_accuracy)),
              hjust = -0.15, vjust = -0.7, size = 3.5, color = "grey30", fontface = "italic",
              inherit.aes = FALSE) +
    scale_fill_manual(values = nb_colors_adf) +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.18))) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Price per ", unit_label, " by Neighbourhood"),
      subtitle = "Assignment Data Frame (ADF)",
      x = NULL,
      y = paste0("Price per ", unit_label),
      caption = params$Company
    )
} else {
  empty_chart("No neighbourhood data available")
}
```

```{r adf_interactive_neighbourhood_boxplot, warning=FALSE}
#| title: !expr paste("ADF - Interactive Price/", unit_label, "by Neighbourhood")

if ("Neighborhood" %in% names(ADF) && length(unique(ADF$Neighborhood[!is.na(ADF$Neighborhood) & ADF$Neighborhood != ""])) > 0) {
  .rollup <- rollup_neighbourhoods_for_boxplot(ADF, target_price_col, max_bars = 10)
  adf_nb_i    <- .rollup$df
  nb_stats_i  <- .rollup$stats
  nb_colors_i <- .rollup$colors

  p_nb <- ggplot(adf_nb_i, aes(x = Neighborhood, y = .data[[target_price_col]],
                                fill = Neighborhood)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_point(aes(text = paste0("N1ID: ", N1ID, "<br>",
                                  "Address: ", Address, "<br>",
                                  "City: ", City, "<br>",
                                  "Zoning: ", Zoning, "<br>",
                                  unit_label_full, ": ", scales::number(.data[[target_size_col]], accuracy = size_accuracy, big.mark = ","), "<br>",
                                  "Price/", unit_label, ": ", dollar(.data[[target_price_col]], accuracy = price_accuracy))),
               position = position_jitter(width = 0.15), size = 1.5, alpha = 0.4,
               color = "steelblue4") +
    scale_fill_manual(values = nb_colors_i) +
    scale_y_continuous(labels = dollar, limits = c(0, NA)) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Price per ", unit_label, " by Neighbourhood (Interactive)"),
      x = NULL,
      y = paste0("Price per ", unit_label)
    )

  ggplotly(p_nb, tooltip = "text")
} else {
  empty_chart("No neighbourhood data available")
}
```

### Price/`r unit_label` by Zoning
```{r adf_zoning_boxplot, echo=FALSE, message=FALSE, warning=FALSE}
#| title: !expr paste("ADF - Price/", unit_label, "by Zoning")

if ("Zoning" %in% names(ADF) && length(unique(ADF$Zoning[!is.na(ADF$Zoning) & ADF$Zoning != ""])) > 0) {
  adf_zn <- ADF %>%
    filter(!is.na(Zoning), Zoning != "")

  # Order zonings by median price (ascending so highest is at top after coord_flip)
  # Minimum 3 sales to include a zoning category
  zn_stats <- adf_zn %>%
    group_by(Zoning) %>%
    summarise(med = median(.data[[target_price_col]], na.rm = TRUE),
              q3 = quantile(.data[[target_price_col]], 0.75, na.rm = TRUE),
              n = n()) %>%
    filter(n >= 3) %>%
    arrange(med)

  adf_zn <- adf_zn %>% filter(Zoning %in% zn_stats$Zoning)

  # Create labelled factor: "Zoning (n)"
  zn_labels <- paste0(zn_stats$Zoning, " (", zn_stats$n, ")")
  adf_zn$Zoning <- factor(adf_zn$Zoning,
                          levels = zn_stats$Zoning,
                          labels = zn_labels)

  # Map zoning colors from the precomputed Set2 palette (keyed to original names)
  zn_colors_adf <- zoning_color_map[zn_stats$Zoning]

  # Annotation: median price positioned at Q3 (right edge of box)
  zn_stats$Zoning <- factor(zn_labels, levels = zn_labels)

  ggplot(adf_zn, aes(x = Zoning, y = .data[[target_price_col]], fill = Zoning)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_jitter(width = 0.15, size = 1.5, alpha = 0.4, color = "steelblue4") +
    geom_text(data = zn_stats,
              aes(x = Zoning, y = q3, label = dollar(med, accuracy = price_accuracy)),
              hjust = -0.15, vjust = -0.7, size = 3.5, color = "grey30", fontface = "italic",
              inherit.aes = FALSE) +
    scale_fill_manual(values = setNames(zn_colors_adf, zn_labels)) +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.18))) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Price per ", unit_label, " by Zoning"),
      subtitle = "Assignment Data Frame (ADF); Min. 3 sales per zoning",
      x = NULL,
      y = paste0("Price per ", unit_label),
      caption = params$Company
    )
} else {
  empty_chart("No zoning data available")
}
```

```{r adf_interactive_zoning_boxplot, warning=FALSE}
#| title: !expr paste("ADF - Interactive Price/", unit_label, "by Zoning")

if ("Zoning" %in% names(ADF) && length(unique(ADF$Zoning[!is.na(ADF$Zoning) & ADF$Zoning != ""])) > 0) {
  adf_zn_i <- ADF %>%
    filter(!is.na(Zoning), Zoning != "")

  zn_stats_i <- adf_zn_i %>%
    group_by(Zoning) %>%
    summarise(med = median(.data[[target_price_col]], na.rm = TRUE),
              n = n()) %>%
    filter(n >= 3) %>%
    arrange(med)

  adf_zn_i <- adf_zn_i %>% filter(Zoning %in% zn_stats_i$Zoning)

  zn_labels_i <- paste0(zn_stats_i$Zoning, " (", zn_stats_i$n, ")")
  zn_colors_i <- zoning_color_map[zn_stats_i$Zoning]
  adf_zn_i$Zoning <- factor(adf_zn_i$Zoning,
                            levels = zn_stats_i$Zoning,
                            labels = zn_labels_i)

  p_zn <- ggplot(adf_zn_i, aes(x = Zoning, y = .data[[target_price_col]],
                                fill = Zoning)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_point(aes(text = paste0("N1ID: ", N1ID, "<br>",
                                  "Address: ", Address, "<br>",
                                  "City: ", City, "<br>",
                                  "Neighbourhood: ", Neighborhood, "<br>",
                                  unit_label_full, ": ", scales::number(.data[[target_size_col]], accuracy = size_accuracy, big.mark = ","), "<br>",
                                  "Price/", unit_label, ": ", dollar(.data[[target_price_col]], accuracy = price_accuracy))),
               position = position_jitter(width = 0.15), size = 1.5, alpha = 0.4,
               color = "steelblue4") +
    scale_fill_manual(values = setNames(zn_colors_i, zn_labels_i)) +
    scale_y_continuous(labels = dollar, limits = c(0, NA)) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Price per ", unit_label, " by Zoning (Interactive)"),
      subtitle = "Min. 3 sales per zoning",
      x = NULL,
      y = paste0("Price per ", unit_label)
    )

  ggplotly(p_zn, tooltip = "text")
} else {
  empty_chart("No zoning data available")
}
```

# CMS Maps & Trends  {orientation="rows"}

## Row {height=50% .tabset}

### Heatmap - Price/`r unit_label` & Property Type
```{r map_cms_heatmap}
#| title: !expr paste("CMS Heatmap - Price/", unit_label)

if(nrow(CMS1) > 0) {
  # Use precomputed sf with tooltip (filter for non-NA price)
  CMS1_sf <- CMS1_sf_base %>% filter(!is.na(.data[[target_price_col]]))

  # Discrete quantile color scale (5 buckets with rounded values)
  cms_price_scale <- create_quantile_classification(
    data = CMS1_sf,
    column = target_price_col,
    n = 5
  )

  # Assign each point to a price bucket for categorical legend interactivity
  cms_buckets <- assign_buckets(
    data = CMS1_sf,
    column = target_price_col,
    classification = cms_price_scale,
    label_formatter = function(breaks) format_price_bucket_labels(cms_price_scale, unit_label, kind = "unit_price")
  )
  CMS1_sf$price_bucket <- cms_buckets$bucket_col

  # Create match expression for categorical coloring
  cms_price_match_expr <- match_expr(
    column = "price_bucket",
    values = cms_buckets$labels,
    stops = unname(cms_buckets$color_map),
    default = "#808080"
  )

  # Build base map with boundaries and distance rings
  Map1CMSH <- build_base_map(
    bounds = map_bbox_cms1,
    muni_bnd = muni_bnd_cms1, wpg_nb_bnd = wpg_nb_bnd_cms1,
    muni_color_map = muni_color_map, id_prefix = "cms_heatmap",
    circle_lon = circle_lon, circle_lat = circle_lat,
    lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = TRUE
  )

  # Add data layer and categorical legend (click legend items to show/hide)
  Map1CMSH <- Map1CMSH |>
    add_circle_layer(
      id = "cms-heatmap",
      source = CMS1_sf,
      circle_color = cms_price_match_expr,
      circle_radius = circle_radius,
      circle_stroke_color = "black",
      circle_stroke_width = 1,
      circle_opacity = 0.8,
      tooltip = "tooltip",
      popup = "popup"
    ) |>
    add_property_markers(params) |>
    add_legend(
      legend_title = paste0("Sale Price/", unit_label),
      values = cms_buckets$labels,
      colors = unname(cms_buckets$color_map),
      type = "categorical",
      layer_id = "cms-heatmap",
      interactive = TRUE,
      position = "bottom-right"
    )

  Map1CMSH
} else {
  empty_map()
}
```

```{r cms_map_property_type, warning=FALSE}
#| title: "CMS - Map by Property Type"

if(nrow(CMS1) > 0) {
  # Create spatial version if Dimensions exist
  CMS_spatial <- CMS1 %>%
    filter(!is.na(Dimensions) & Dimensions != "") %>%
    mutate(geometry = st_as_sfc(Dimensions, crs = 4326)) %>%
    st_as_sf()

  # Add fill_color to spatial data
  if(nrow(CMS_spatial) > 0) {
    CMS_spatial$fill_color <- prop_color_map[CMS_spatial$PropMajor]
  }

  # Use precomputed sf with tooltip (fill_color already set in precompute)
  CMS1_sf <- CMS1_sf_base

  # Create match expression for categorical coloring by property type
  cms_proptype_match_expr <- match_expr(
    column = "PropMajor",
    values = names(prop_color_map),
    stops = unname(prop_color_map),
    default = "#808080"
  )

  # Build base map with boundaries and distance rings
  Map1CMS1 <- build_base_map(
    bounds = map_bbox_cms1,
    muni_bnd = muni_bnd_cms1, wpg_nb_bnd = wpg_nb_bnd_cms1,
    muni_color_map = muni_color_map, id_prefix = "cms_proptype",
    circle_lon = circle_lon, circle_lat = circle_lat,
    lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = TRUE
  ) |>
    add_property_markers(params)

  # Add polygons if spatial data exists
  if(nrow(CMS_spatial) > 0) {
    Map1CMS1 <- Map1CMS1 |>
      add_fill_layer(
        id = "cms-polygons-fill",
        source = CMS_spatial,
        fill_color = get_column("fill_color"),
        fill_opacity = 0.3,
        popup = "popup"
      ) |>
      add_line_layer(
        id = "cms-polygons-outline",
        source = CMS_spatial,
        line_color = "black",
        line_width = 1
      )
  }

  # Filter legend to only property types present in CMS1
  cms1_prop_types <- unique(CMS1$PropMajor[!is.na(CMS1$PropMajor)])
  cms1_prop_color_map <- prop_color_map[names(prop_color_map) %in% cms1_prop_types]

  Map1CMS1 <- Map1CMS1 |>
    add_circle_layer(
      id = "cms-points",
      source = CMS1_sf,
      circle_color = cms_proptype_match_expr,
      circle_radius = circle_radius,
      circle_stroke_color = "black",
      circle_stroke_width = 1,
      circle_opacity = 0.7,
      tooltip = "tooltip",
      popup = "popup"
    ) |>
    add_legend(
      legend_title = "Property Type",
      values = sort(names(cms1_prop_color_map)),
      colors = unname(cms1_prop_color_map[sort(names(cms1_prop_color_map))]),
      type = "categorical",
      layer_id = "cms-points",
      interactive = TRUE,
      position = "bottom-right"
    )

  Map1CMS1
} else {
  empty_map()
}
```

### Map by Zoning & Neighbourhood
```{r cms_map_zoning, warning=FALSE}
#| title: "CMS - Map by Zoning"

if(nrow(CMS1) > 0) {
  # Create spatial version if Dimensions exist
  CMS_spatial_z <- CMS1 %>%
    filter(!is.na(Dimensions) & Dimensions != "") %>%
    mutate(geometry = st_as_sfc(Dimensions, crs = 4326)) %>%
    st_as_sf()

  # Add zoning fill_color to spatial data
  if(nrow(CMS_spatial_z) > 0) {
    CMS_spatial_z$zoning_fill_color <- zoning_color_map[CMS_spatial_z$Zoning]
  }

  # Use precomputed sf with tooltip
  CMS1_sf_z <- CMS1_sf_base

  # Filter zoning color map to only zones present in CMS1
  cms_zoning_types <- unique(CMS1$Zoning[!is.na(CMS1$Zoning)])
  cms_zoning_cmap <- zoning_color_map[names(zoning_color_map) %in% cms_zoning_types]

  # Create match expression for categorical coloring by zoning
  cms_zoning_match_expr <- match_expr(
    column = "Zoning",
    values = names(cms_zoning_cmap),
    stops = unname(cms_zoning_cmap),
    default = "#808080"
  )

  # Build base map with boundaries and distance rings
  Map1CMS_Z <- build_base_map(
    bounds = map_bbox_cms1,
    muni_bnd = muni_bnd_cms1, wpg_nb_bnd = wpg_nb_bnd_cms1,
    muni_color_map = muni_color_map, id_prefix = "cms_zoning",
    circle_lon = circle_lon, circle_lat = circle_lat,
    lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = TRUE
  ) |>
    add_property_markers(params)

  # Add polygons if spatial data exists
  if(nrow(CMS_spatial_z) > 0) {
    Map1CMS_Z <- Map1CMS_Z |>
      add_fill_layer(
        id = "cms-zoning-polygons-fill",
        source = CMS_spatial_z,
        fill_color = get_column("zoning_fill_color"),
        fill_opacity = 0.3,
        popup = "popup"
      ) |>
      add_line_layer(
        id = "cms-zoning-polygons-outline",
        source = CMS_spatial_z,
        line_color = "black",
        line_width = 1
      )
  }

  Map1CMS_Z <- Map1CMS_Z |>
    add_circle_layer(
      id = "cms-zoning-points",
      source = CMS1_sf_z,
      circle_color = cms_zoning_match_expr,
      circle_radius = circle_radius,
      circle_stroke_color = "black",
      circle_stroke_width = 1,
      circle_opacity = 0.7,
      tooltip = "tooltip",
      popup = "popup"
    ) |>
    add_legend(
      legend_title = "Zoning",
      values = sort(names(cms_zoning_cmap)),
      colors = unname(cms_zoning_cmap[sort(names(cms_zoning_cmap))]),
      type = "categorical",
      layer_id = "cms-zoning-points",
      interactive = TRUE,
      position = "bottom-right"
    )

  Map1CMS_Z
} else {
  empty_map()
}
```

```{r map_cms_neighborhoods}
#| title: "CMS - Map by Neighbourhood"

  # Check if Neighborhood column exists
if("Neighborhood" %in% names(CMS1) && sum(!is.na(CMS1$Neighborhood)) > 0) {
  # Create neighbourhood color map using WRHA palette
  neighborhoods <- unique(CMS1$Neighborhood[!is.na(CMS1$Neighborhood)])
  neighborhood_colors <- get_nb_color(neighborhoods)
  neighborhood_color_map <- setNames(neighborhood_colors, neighborhoods)

  # Pre-compute colors (added to CMS1 which already has tooltip)
  CMS1$neighborhood_color <- neighborhood_color_map[CMS1$Neighborhood]

  # Create sf from updated CMS1 (neighborhood_color was just added, can't use CMS1_sf_base)
  CMS1_sf_n <- CMS1 %>%
    filter(!is.na(Lon) & !is.na(Lat) & !is.na(Neighborhood)) %>%
    st_as_sf(coords = c("Lon", "Lat"), crs = 4326)

  # Build base map with boundaries and distance rings (no muni boundaries)
  MapN <- build_base_map(
    bounds = map_bbox_cms1,
    muni_bnd = NULL, wpg_nb_bnd = wpg_nb_bnd_cms1,
    muni_color_map = muni_color_map, id_prefix = "cms_nb",
    circle_lon = circle_lon, circle_lat = circle_lat,
    lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = TRUE
  ) |>
    add_property_markers(params)

  # Create match expression for categorical coloring by neighbourhood
  cms_nb_match_expr <- match_expr(
    column = "Neighborhood",
    values = names(neighborhood_color_map),
    stops = unname(neighborhood_color_map),
    default = "#808080"
  )

  MapN <- MapN |>
    add_circle_layer(
      id = "neighborhood-points",
      source = CMS1_sf_n,
      circle_color = cms_nb_match_expr,
      circle_radius = circle_radius,
      circle_stroke_color = "black",
      circle_stroke_width = 1,
      circle_opacity = 0.7,
      tooltip = "tooltip",
      popup = "popup"
    ) |>
    add_legend(
      legend_title = "Neighbourhood",
      values = sort(names(neighborhood_color_map)),
      colors = unname(neighborhood_color_map[sort(names(neighborhood_color_map))]),
      type = "categorical",
      layer_id = "neighborhood-points",
      interactive = TRUE,
      position = "bottom-right"
    )

  MapN
} else {
  maplibre(
    center = c(circle_lon, circle_lat),
    zoom = 9
  ) |>
    add_navigation_control(position = "top-left")
}
```

## Row {height=50% .tabset}

### Price Trends Over Time {width=50%}
```{r trend_price_over_time, warning=FALSE}
#| title: !expr paste("CMS - Price per", unit_label, "Over Time")

CMS1Trend <- ggplot(CMS1, aes(DateSold, .data[[target_price_col]])) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  scale_y_continuous(labels = dollar, limits = c(0, NA),
                     breaks = scales::pretty_breaks(n = 7),
                     expand = expansion(mult = c(0.005, 0.05))) +
  scale_x_date(breaks = date_breaks_vec,
               labels = scales::date_format(date_label_format)) +
  theme_custom() +
  theme_point_colour() +
  labs(
    title = paste0("Land Price per ", unit_label, " Over Time"),
    subtitle = str_wrap(Subtitle1, 66),
    x = "Sale Date",
    y = paste0("Price per ", unit_label),
    caption = paste0("Daily Change: $", MktCondVal1,
                     "; Median Price/", unit_label, ": ", label_dollar(accuracy = price_accuracy)(MedianPriceUnit1),
                     "; ", label_percent(accuracy = .01)(AnnualIncreasePer1),
                     " per year | ", params$Company)
  )
CMS1Trend
```

```{r interactive_trend, warning=FALSE}
#| title: !expr paste("CMS - Interactive Price per", unit_label, "Over Time")

p <- ggplot(CMS1, aes(DateSold, .data[[target_price_col]])) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  geom_point(aes(text = paste0("N1ID: ", N1ID, "<br>",
                                "Address: ", Address, "<br>",
                                "City: ", City, "<br>",
                                "Zoning: ", Zoning, "<br>",
                                unit_label_full, ": ", scales::number(.data[[target_size_col]], accuracy = size_accuracy, big.mark = ","), "<br>",
                                "Price/", unit_label, ": ", dollar(.data[[target_price_col]], accuracy = price_accuracy))),
             shape = 21, size = 3, fill = "steelblue1", alpha = 0.6,
             color = "steelblue4", stroke = 0.5) +
  scale_y_continuous(labels = dollar, limits = c(0, NA)) +
  theme_custom() +
  labs(
    title = paste0("Land Price per ", unit_label, " Over Time (Interactive)"),
    subtitle = Subtitle1,
    x = "Sale Date",
    y = paste0("Price per ", unit_label)
  )

ggplotly(p, tooltip = "text")
```
### Price per `r unit_label` by Parcel Size
```{r size_price_by_size}
#| title: !expr paste("Price per", unit_label, "by Parcel Size")

# Adaptive x-axis precision and break count based on data range
cms1_size_range <- diff(range(CMS1[[target_size_col]], na.rm = TRUE))
x_accuracy1 <- dplyr::case_when(
  cms1_size_range < 10  ~ 0.01,
  cms1_size_range < 100 ~ 1,
  TRUE                  ~ size_accuracy
)
x_n_breaks1 <- dplyr::case_when(
  cms1_size_range < 1  ~ 5L,
  cms1_size_range < 10 ~ 7L,
  cms1_size_range < 50 ~ 8L,
  TRUE                 ~ 10L
)

# Predict price at subject lot size from linear model
size_lm1 <- lm(reformulate(target_size_col, target_price_col), data = CMS1)
size_pred1 <- predict(size_lm1, newdata = setNames(data.frame(sub_lot_size), target_size_col))

CMS1Size <- ggplot(CMS1, aes(.data[[target_size_col]], .data[[target_price_col]])) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  geom_vline(aes(xintercept = sub_lot_size), color = "dodgerblue2",
             linewidth = 1.5, linetype = "dashed") +
  scale_y_continuous(labels = dollar, limits = c(0, NA),
                     breaks = scales::pretty_breaks(n = 7),
                     expand = expansion(mult = c(0.005, 0.05))) +
  scale_x_continuous(labels = scales::number_format(accuracy = x_accuracy1, big.mark = ","),
                     breaks = scales::pretty_breaks(n = x_n_breaks1),
                     expand = expansion(mult = c(0.005, 0.05))) +
  theme_custom() +
  theme_point_colour() +
  labs(
    title = paste0("Price per ", unit_label, " by Parcel Size"),
    subtitle = str_wrap(Subtitle1, 66),
    x = paste0("Parcel Size (", unit_label_full, ")"),
    y = paste0("Price per ", unit_label),
    caption = paste0("Subject property: ", scales::number(sub_lot_size, accuracy = x_accuracy1, big.mark = ","), " ", unit_label,
                     " (blue line); Trend value: ", label_dollar(accuracy = price_accuracy)(size_pred1),
                     "/", unit_label, " | ", params$Company)
  )
CMS1Size
```

```{r interactive_size, warning=FALSE}
#| title: !expr paste("CMS - Interactive Price per", unit_label, "by Parcel Size")

p_size <- ggplot(CMS1, aes(.data[[target_size_col]], .data[[target_price_col]])) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  geom_vline(aes(xintercept = sub_lot_size), color = "dodgerblue2",
             linewidth = 1.5, linetype = "dashed") +
  geom_point(aes(text = paste0("N1ID: ", N1ID, "<br>",
                                "Address: ", Address, "<br>",
                                "City: ", City, "<br>",
                                "Zoning: ", Zoning, "<br>",
                                unit_label_full, ": ", scales::number(.data[[target_size_col]], accuracy = size_accuracy, big.mark = ","), "<br>",
                                "Price/", unit_label, ": ", dollar(.data[[target_price_col]], accuracy = price_accuracy))),
             shape = 21, size = 3, fill = "steelblue1", alpha = 0.6,
             color = "steelblue4", stroke = 0.5) +
  scale_y_continuous(labels = dollar, limits = c(0, NA)) +
  scale_x_continuous(labels = scales::number_format(accuracy = x_accuracy1, big.mark = ",")) +
  theme_custom() +
  labs(
    title = paste0("Price per ", unit_label, " by Parcel Size (Interactive)"),
    subtitle = Subtitle1,
    x = paste0("Parcel Size (", unit_label_full, ")"),
    y = paste0("Price per ", unit_label)
  )

ggplotly(p_size, tooltip = "text")
```

```{r size_adj_price_by_size}
#| title: !expr paste("Time Adjusted Price per", unit_label, "by Parcel Size")

# Predict adjusted price at subject lot size from linear model
size_adj_lm1 <- lm(reformulate(target_size_col, "AdjPrice"), data = CMS1)
size_adj_pred1 <- predict(size_adj_lm1, newdata = setNames(data.frame(sub_lot_size), target_size_col))

CMS1SizeAdj <- ggplot(CMS1, aes(.data[[target_size_col]], AdjPrice)) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  geom_vline(aes(xintercept = sub_lot_size), color = "dodgerblue2",
             linewidth = 1.5, linetype = "dashed") +
  scale_y_continuous(labels = dollar, limits = c(0, NA),
                     breaks = scales::pretty_breaks(n = 7),
                     expand = expansion(mult = c(0.005, 0.05))) +
  scale_x_continuous(labels = scales::number_format(accuracy = x_accuracy1, big.mark = ","),
                     breaks = scales::pretty_breaks(n = x_n_breaks1),
                     expand = expansion(mult = c(0.005, 0.05))) +
  theme_custom() +
  theme_point_colour() +
  labs(
    title = paste0("Price per ", unit_label, " by Parcel Size"),
    subtitle = str_wrap(Subtitle2, 66),
    x = paste0("Parcel Size (", unit_label_full, ")"),
    y = paste0("Adjusted Price per ", unit_label),
    caption = paste0("Subject: ", scales::number(sub_lot_size, accuracy = x_accuracy1, big.mark = ","), " ", unit_label,
                     "; Trend value: ", label_dollar(accuracy = price_accuracy)(size_adj_pred1),
                     "/", unit_label, "; Adjusted $", MktCondVal1, "/day | ", params$Company)
  )
CMS1SizeAdj
```

### Price per `r unit_label` by Distance
```{r dist_price_by_distance}
#| title: !expr paste("Price per", unit_label, "by Distance")

# Select distance column and label based on SubRef setting
dist_col <- if (params$SubRef == "Ref") "RefDist" else "SubDist"
dist_label <- if (params$SubRef == "Ref") params$RefPoint else "subject"
dist_vline <- if (params$SubRef == "Ref") Subject$RefDist else Subject$SubDist

# Predict price at vline distance from linear model
dist_lm1 <- lm(reformulate(dist_col, target_price_col), data = CMS1)
dist_pred1 <- predict(dist_lm1, newdata = setNames(data.frame(dist_vline), dist_col))
dist_adj_lm1 <- lm(reformulate(dist_col, "AdjPrice"), data = CMS1)
dist_adj_pred1 <- predict(dist_adj_lm1, newdata = setNames(data.frame(dist_vline), dist_col))

CMS1Dist <- ggplot(CMS1, aes(.data[[dist_col]], .data[[target_price_col]])) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  {if (params$SubRef == "Ref") geom_vline(aes(xintercept = dist_vline), color = "dodgerblue2",
             linewidth = 1.5, linetype = "dashed")} +
  scale_y_continuous(labels = dollar, limits = c(0, NA),
                     breaks = scales::pretty_breaks(n = 6),
                     expand = expansion(mult = c(0.005, 0.05))) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10),
                     expand = expansion(mult = c(0.005, 0.05))) +
  theme_custom() +
  theme_point_colour() +
  labs(
    title = paste0("Price per ", unit_label, " by Distance from ", dist_label),
    subtitle = str_wrap(Subtitle1, 66),
    x = paste0("Distance from ", dist_label, " (km)"),
    y = paste0("Price per ", unit_label),
    caption = if (params$SubRef == "Ref") paste0("Subject property distance: ", dist_vline, " km; Trend value: ", label_dollar(accuracy = price_accuracy)(dist_pred1), "/", unit_label, " | ", params$Company) else paste0("Trend value at subject: ", label_dollar(accuracy = price_accuracy)(dist_pred1), "/", unit_label, " | ", params$Company)
  )
CMS1Dist
```

```{r dist_adj_price_by_distance}
#| title: !expr paste("Time Adjusted Price per", unit_label, "by Distance")

CMS1DistAdj <- ggplot(CMS1, aes(.data[[dist_col]], AdjPrice)) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  {if (params$SubRef == "Ref") geom_vline(aes(xintercept = dist_vline), color = "dodgerblue2",
             linewidth = 1.5, linetype = "dashed")} +
  scale_y_continuous(labels = dollar, limits = c(0, NA),
                     breaks = scales::pretty_breaks(n = 6),
                     expand = expansion(mult = c(0.005, 0.05))) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10),
                     expand = expansion(mult = c(0.005, 0.05))) +
  theme_custom() +
  theme_point_colour() +
  labs(
    title = paste0("Price per ", unit_label, " by Distance from ", dist_label),
    subtitle = str_wrap(Subtitle2, 66),
    x = paste0("Distance from ", dist_label, " (km)"),
    y = paste0("Adjusted Price per ", unit_label),
    caption = if (params$SubRef == "Ref") paste0("Subject distance: ", dist_vline, " km; Trend value: ", label_dollar(accuracy = price_accuracy)(dist_adj_pred1), "/", unit_label, "; Adjusted $", MktCondVal1, "/day | ", params$Company) else paste0("Trend value at subject: ", label_dollar(accuracy = price_accuracy)(dist_adj_pred1), "/", unit_label, "; Adjusted $", MktCondVal1, "/day | ", params$Company)
  )
CMS1DistAdj
```

### Price/`r unit_label` by Neighbourhood
```{r cms1_neighbourhood_boxplot, echo=FALSE, message=FALSE, warning=FALSE}
#| title: !expr paste("CMS - Price/", unit_label, "by Neighbourhood")

if ("Neighborhood" %in% names(CMS1) && nrow(CMS1) > 0 &&
    length(unique(CMS1$Neighborhood[!is.na(CMS1$Neighborhood) & CMS1$Neighborhood != ""])) > 0) {
  .rollup <- rollup_neighbourhoods_for_boxplot(CMS1, target_price_col, max_bars = 10)
  cms1_nb        <- .rollup$df
  nb_stats1      <- .rollup$stats
  nb_colors_cms1 <- .rollup$colors

  ggplot(cms1_nb, aes(x = Neighborhood, y = .data[[target_price_col]], fill = Neighborhood)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_jitter(width = 0.15, size = 1.5, alpha = 0.4, color = "steelblue4") +
    geom_text(data = nb_stats1,
              aes(x = Neighborhood, y = q3, label = dollar(med, accuracy = price_accuracy)),
              hjust = -0.15, vjust = -0.7, size = 3.5, color = "grey30", fontface = "italic",
              inherit.aes = FALSE) +
    scale_fill_manual(values = nb_colors_cms1) +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.18))) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Price per ", unit_label, " by Neighbourhood"),
      subtitle = str_wrap(Subtitle1, 80),
      x = NULL,
      y = paste0("Price per ", unit_label),
      caption = params$Company
    )
} else {
  empty_chart("No neighbourhood data available in CMS")
}
```

```{r cms1_adj_neighbourhood_boxplot, echo=FALSE, message=FALSE, warning=FALSE}
#| title: !expr paste("CMS - Time Adjusted Price/", unit_label, "by Neighbourhood")

if ("Neighborhood" %in% names(CMS1) && nrow(CMS1) > 0 &&
    length(unique(CMS1$Neighborhood[!is.na(CMS1$Neighborhood) & CMS1$Neighborhood != ""])) > 0) {
  .rollup <- rollup_neighbourhoods_for_boxplot(CMS1, "AdjPrice", max_bars = 10)
  cms1_nb         <- .rollup$df
  nb_stats1a      <- .rollup$stats
  nb_colors_cms1a <- .rollup$colors

  ggplot(cms1_nb, aes(x = Neighborhood, y = AdjPrice, fill = Neighborhood)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_jitter(width = 0.15, size = 1.5, alpha = 0.4, color = "steelblue4") +
    geom_text(data = nb_stats1a,
              aes(x = Neighborhood, y = q3, label = dollar(med, accuracy = price_accuracy)),
              hjust = -0.15, vjust = -0.7, size = 3.5, color = "grey30", fontface = "italic",
              inherit.aes = FALSE) +
    scale_fill_manual(values = nb_colors_cms1a) +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.18))) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Adjusted Price per ", unit_label, " by Neighbourhood"),
      subtitle = str_wrap(Subtitle2, 80),
      x = NULL,
      y = paste0("Adjusted Price per ", unit_label),
      caption = paste0("Adjusted $", MktCondVal1, "/day | ", params$Company)
    )
} else {
  empty_chart("No neighbourhood data available in CMS")
}
```

### Price/`r unit_label` by Zoning
```{r cms1_zoning_boxplot, echo=FALSE, message=FALSE, warning=FALSE}
#| title: !expr paste("CMS - Price/", unit_label, "by Zoning")

if ("Zoning" %in% names(CMS1) && nrow(CMS1) > 0 &&
    length(unique(CMS1$Zoning[!is.na(CMS1$Zoning) & CMS1$Zoning != ""])) > 0) {
  cms1_zn <- CMS1 %>%
    filter(!is.na(Zoning), Zoning != "")

  zn_stats1 <- cms1_zn %>%
    group_by(Zoning) %>%
    summarise(med = median(.data[[target_price_col]], na.rm = TRUE),
              q3 = quantile(.data[[target_price_col]], 0.75, na.rm = TRUE),
              n = n()) %>%
    filter(n >= 3) %>%
    arrange(med)

  cms1_zn <- cms1_zn %>% filter(Zoning %in% zn_stats1$Zoning)

  zn_labels1 <- paste0(zn_stats1$Zoning, " (", zn_stats1$n, ")")
  cms1_zn$Zoning <- factor(cms1_zn$Zoning,
                           levels = zn_stats1$Zoning,
                           labels = zn_labels1)

  zn_colors_cms1 <- zoning_color_map[zn_stats1$Zoning]
  zn_stats1$Zoning <- factor(zn_labels1, levels = zn_labels1)

  ggplot(cms1_zn, aes(x = Zoning, y = .data[[target_price_col]], fill = Zoning)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_jitter(width = 0.15, size = 1.5, alpha = 0.4, color = "steelblue4") +
    geom_text(data = zn_stats1,
              aes(x = Zoning, y = q3, label = dollar(med, accuracy = price_accuracy)),
              hjust = -0.15, vjust = -0.7, size = 3.5, color = "grey30", fontface = "italic",
              inherit.aes = FALSE) +
    scale_fill_manual(values = setNames(zn_colors_cms1, zn_labels1)) +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.18))) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Price per ", unit_label, " by Zoning"),
      subtitle = str_wrap(paste0(Subtitle1, "; Min. 3 sales per zoning"), 80),
      x = NULL,
      y = paste0("Price per ", unit_label),
      caption = params$Company
    )
} else {
  empty_chart("No zoning data available in CMS")
}
```

```{r cms1_adj_zoning_boxplot, echo=FALSE, message=FALSE, warning=FALSE}
#| title: !expr paste("CMS - Time Adjusted Price/", unit_label, "by Zoning")

if ("Zoning" %in% names(CMS1) && nrow(CMS1) > 0 &&
    length(unique(CMS1$Zoning[!is.na(CMS1$Zoning) & CMS1$Zoning != ""])) > 0) {
  cms1_zn <- CMS1 %>%
    filter(!is.na(Zoning), Zoning != "")

  zn_stats1a <- cms1_zn %>%
    group_by(Zoning) %>%
    summarise(med = median(AdjPrice, na.rm = TRUE),
              q3 = quantile(AdjPrice, 0.75, na.rm = TRUE),
              n = n()) %>%
    filter(n >= 3) %>%
    arrange(med)

  cms1_zn <- cms1_zn %>% filter(Zoning %in% zn_stats1a$Zoning)

  zn_labels1a <- paste0(zn_stats1a$Zoning, " (", zn_stats1a$n, ")")
  cms1_zn$Zoning <- factor(cms1_zn$Zoning,
                           levels = zn_stats1a$Zoning,
                           labels = zn_labels1a)

  zn_colors_cms1a <- zoning_color_map[zn_stats1a$Zoning]
  zn_stats1a$Zoning <- factor(zn_labels1a, levels = zn_labels1a)

  ggplot(cms1_zn, aes(x = Zoning, y = AdjPrice, fill = Zoning)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_jitter(width = 0.15, size = 1.5, alpha = 0.4, color = "steelblue4") +
    geom_text(data = zn_stats1a,
              aes(x = Zoning, y = q3, label = dollar(med, accuracy = price_accuracy)),
              hjust = -0.15, vjust = -0.7, size = 3.5, color = "grey30", fontface = "italic",
              inherit.aes = FALSE) +
    scale_fill_manual(values = setNames(zn_colors_cms1a, zn_labels1a)) +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.18))) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Adjusted Price per ", unit_label, " by Zoning"),
      subtitle = str_wrap(paste0(Subtitle2, "; Min. 3 sales per zoning"), 80),
      x = NULL,
      y = paste0("Adjusted Price per ", unit_label),
      caption = paste0("Adjusted $", MktCondVal1, "/day | ", params$Company)
    )
} else {
  empty_chart("No zoning data available in CMS")
}
```

# CMS2 Maps & Trends (5th-95th Percentile) {orientation="rows"}

## Row {height=50% .tabset}

### Heatmap - Price/`r unit_label` & Property Type
```{r map_cms2_heatmap}
#| title: !expr paste("CMS2 Heatmap - Price/", unit_label, "(5th-95th Percentile)")

if (nrow(CMS2) > 0) {
  # Use precomputed sf with tooltip (filter for non-NA price)
  CMS2_sf <- CMS2_sf_base %>% filter(!is.na(.data[[target_price_col]]))

  if (nrow(CMS2_sf) > 0) {
    # Discrete quantile color scale (5 buckets with rounded values)
    cms2_price_scale <- create_quantile_classification(
      data = CMS2_sf,
      column = target_price_col,
      n = 5
    )

    # Assign each point to a price bucket for categorical legend interactivity
    cms2_buckets <- assign_buckets(
      data = CMS2_sf,
      column = target_price_col,
      classification = cms2_price_scale,
      label_formatter = function(breaks) format_price_bucket_labels(cms2_price_scale, unit_label, kind = "unit_price")
    )
    CMS2_sf$price_bucket <- cms2_buckets$bucket_col

    # Create match expression for categorical coloring
    cms2_price_match_expr <- match_expr(
      column = "price_bucket",
      values = cms2_buckets$labels,
      stops = unname(cms2_buckets$color_map),
      default = "#808080"
    )

    # Build base map with boundaries and distance rings
    Map1CMS2H <- build_base_map(
      bounds = map_bbox_cms2,
      muni_bnd = muni_bnd_cms2, wpg_nb_bnd = wpg_nb_bnd_cms2,
      muni_color_map = muni_color_map, id_prefix = "cms2_heatmap",
      circle_lon = circle_lon, circle_lat = circle_lat,
      lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = TRUE
    )

    # Add data layer and categorical legend (click legend items to show/hide)
    Map1CMS2H <- Map1CMS2H |>
      add_circle_layer(
        id = "cms2-heatmap",
        source = CMS2_sf,
        circle_color = cms2_price_match_expr,
        circle_radius = circle_radius,
        circle_stroke_color = "black",
        circle_stroke_width = 1,
        circle_opacity = 0.8,
        tooltip = "tooltip",
        popup = "popup"
      ) |>
      add_property_markers(params) |>
      add_legend(
        legend_title = paste0("Sale Price/", unit_label),
        values = cms2_buckets$labels,
        colors = unname(cms2_buckets$color_map),
        type = "categorical",
        layer_id = "cms2-heatmap",
        interactive = TRUE,
        position = "bottom-right"
      )

    Map1CMS2H
  } else {
    empty_map()
  }
} else {
  empty_map()
}
```

```{r cms2_map_property_type, warning=FALSE}
#| title: "CMS2 - Comparable Market Set by Property Type"

if (nrow(CMS2) > 0) {
  # Create spatial version if Dimensions exist
  CMS2_spatial <- CMS2 %>%
    filter(!is.na(Dimensions) & Dimensions != "") %>%
    mutate(geometry = st_as_sfc(Dimensions, crs = 4326)) %>%
    st_as_sf()

  # Add fill_color to spatial data
  if (nrow(CMS2_spatial) > 0) {
    CMS2_spatial$fill_color <- prop_color_map[CMS2_spatial$PropMajor]
  }

  # Use precomputed sf with tooltip (fill_color already set in precompute)
  CMS2_sf <- CMS2_sf_base

  # Create match expression for categorical coloring by property type
  cms2_proptype_match_expr <- match_expr(
    column = "PropMajor",
    values = names(prop_color_map),
    stops = unname(prop_color_map),
    default = "#808080"
  )

  # Build base map with boundaries and distance rings
  Map1CMS2PropType <- build_base_map(
    bounds = map_bbox_cms2,
    muni_bnd = muni_bnd_cms2, wpg_nb_bnd = wpg_nb_bnd_cms2,
    muni_color_map = muni_color_map, id_prefix = "cms2_proptype",
    circle_lon = circle_lon, circle_lat = circle_lat,
    lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = TRUE
  ) |>
    add_property_markers(params)

  # Add polygons if spatial data exists
  if (nrow(CMS2_spatial) > 0) {
    Map1CMS2PropType <- Map1CMS2PropType |>
      add_fill_layer(
        id = "cms2-polygons-fill",
        source = CMS2_spatial,
        fill_color = get_column("fill_color"),
        fill_opacity = 0.3,
        popup = "popup"
      ) |>
      add_line_layer(
        id = "cms2-polygons-outline",
        source = CMS2_spatial,
        line_color = "black",
        line_width = 1
      )
  }

  # Filter legend to only property types present in CMS2
  cms2_prop_types <- unique(CMS2$PropMajor[!is.na(CMS2$PropMajor)])
  cms2_prop_color_map <- prop_color_map[names(prop_color_map) %in% cms2_prop_types]

  Map1CMS2PropType <- Map1CMS2PropType |>
    add_circle_layer(
      id = "cms2-points",
      source = CMS2_sf,
      circle_color = cms2_proptype_match_expr,
      circle_radius = circle_radius,
      circle_stroke_color = "black",
      circle_stroke_width = 1,
      circle_opacity = 0.7,
      tooltip = "tooltip",
      popup = "popup"
    ) |>
    add_legend(
      legend_title = "Property Type",
      values = sort(names(cms2_prop_color_map)),
      colors = unname(cms2_prop_color_map[sort(names(cms2_prop_color_map))]),
      type = "categorical",
      layer_id = "cms2-points",
      interactive = TRUE,
      position = "bottom-right"
    )

  Map1CMS2PropType
} else {
  empty_map()
}
```

### Map by Zoning & Neighbourhood
```{r cms2_map_zoning, warning=FALSE}
#| title: "CMS2 - Comparable Market Set by Zoning"

if (nrow(CMS2) > 0) {
  # Create spatial version if Dimensions exist
  CMS2_spatial_z <- CMS2 %>%
    filter(!is.na(Dimensions) & Dimensions != "") %>%
    mutate(geometry = st_as_sfc(Dimensions, crs = 4326)) %>%
    st_as_sf()

  # Add zoning fill_color to spatial data
  if (nrow(CMS2_spatial_z) > 0) {
    CMS2_spatial_z$zoning_fill_color <- zoning_color_map[CMS2_spatial_z$Zoning]
  }

  # Use precomputed sf with tooltip
  CMS2_sf_z <- CMS2_sf_base

  # Filter zoning color map to only zones present in CMS2
  cms2_zoning_types <- unique(CMS2$Zoning[!is.na(CMS2$Zoning)])
  cms2_zoning_cmap <- zoning_color_map[names(zoning_color_map) %in% cms2_zoning_types]

  # Create match expression for categorical coloring by zoning
  cms2_zoning_match_expr <- match_expr(
    column = "Zoning",
    values = names(cms2_zoning_cmap),
    stops = unname(cms2_zoning_cmap),
    default = "#808080"
  )

  # Build base map with boundaries and distance rings
  Map1CMS2_Z <- build_base_map(
    bounds = map_bbox_cms2,
    muni_bnd = muni_bnd_cms2, wpg_nb_bnd = wpg_nb_bnd_cms2,
    muni_color_map = muni_color_map, id_prefix = "cms2_zoning",
    circle_lon = circle_lon, circle_lat = circle_lat,
    lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = TRUE
  ) |>
    add_property_markers(params)

  # Add polygons if spatial data exists
  if (nrow(CMS2_spatial_z) > 0) {
    Map1CMS2_Z <- Map1CMS2_Z |>
      add_fill_layer(
        id = "cms2-zoning-polygons-fill",
        source = CMS2_spatial_z,
        fill_color = get_column("zoning_fill_color"),
        fill_opacity = 0.3,
        popup = "popup"
      ) |>
      add_line_layer(
        id = "cms2-zoning-polygons-outline",
        source = CMS2_spatial_z,
        line_color = "black",
        line_width = 1
      )
  }

  Map1CMS2_Z <- Map1CMS2_Z |>
    add_circle_layer(
      id = "cms2-zoning-points",
      source = CMS2_sf_z,
      circle_color = cms2_zoning_match_expr,
      circle_radius = circle_radius,
      circle_stroke_color = "black",
      circle_stroke_width = 1,
      circle_opacity = 0.7,
      tooltip = "tooltip",
      popup = "popup"
    ) |>
    add_legend(
      legend_title = "Zoning",
      values = sort(names(cms2_zoning_cmap)),
      colors = unname(cms2_zoning_cmap[sort(names(cms2_zoning_cmap))]),
      type = "categorical",
      layer_id = "cms2-zoning-points",
      interactive = TRUE,
      position = "bottom-right"
    )

  Map1CMS2_Z
} else {
  empty_map()
}
```

```{r map_cms2_neighborhoods}
# CMS2 map colored by Winnipeg neighbourhood cluster (5th-95th percentile subset).
if ("Neighborhood" %in% names(CMS2) && sum(!is.na(CMS2$Neighborhood)) > 0) {
  # Create neighbourhood color map using WRHA palette
  neighborhoods <- unique(CMS2$Neighborhood[!is.na(CMS2$Neighborhood)])
  neighborhood_colors <- get_nb_color(neighborhoods)
  neighborhood_color_map <- setNames(neighborhood_colors, neighborhoods)

  # Pre-compute colors
  CMS2$neighborhood_color <- neighborhood_color_map[CMS2$Neighborhood]

  # Create sf from updated CMS2
  CMS2_sf_n <- CMS2 %>%
    filter(!is.na(Lon) & !is.na(Lat) & !is.na(Neighborhood)) %>%
    st_as_sf(coords = c("Lon", "Lat"), crs = 4326)

  # Create match expression for categorical coloring by neighbourhood
  cms2_nb_match_expr <- match_expr(
    column = "Neighborhood",
    values = names(neighborhood_color_map),
    stops = unname(neighborhood_color_map),
    default = "#808080"
  )

  # Build base map with boundaries and distance rings (no muni boundaries)
  Map2CMS2N <- build_base_map(
    bounds = map_bbox_cms2,
    muni_bnd = NULL, wpg_nb_bnd = wpg_nb_bnd_cms2,
    muni_color_map = muni_color_map, id_prefix = "cms2_nb",
    circle_lon = circle_lon, circle_lat = circle_lat,
    lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = TRUE
  ) |>
    add_property_markers(params)

  Map2CMS2N <- Map2CMS2N |>
    add_circle_layer(
      id = "cms2-neighborhood-points",
      source = CMS2_sf_n,
      circle_color = cms2_nb_match_expr,
      circle_radius = circle_radius,
      circle_stroke_color = "black",
      circle_stroke_width = 1,
      circle_opacity = 0.7,
      tooltip = "tooltip",
      popup = "popup"
    ) |>
    add_legend(
      legend_title = "Neighbourhood",
      values = sort(names(neighborhood_color_map)),
      colors = unname(neighborhood_color_map[sort(names(neighborhood_color_map))]),
      type = "categorical",
      layer_id = "cms2-neighborhood-points",
      interactive = TRUE,
      position = "bottom-right"
    )

  Map2CMS2N
} else {
  empty_map()
}
```

## Row {height=50% .tabset}

### Price Trends Over Time {width=50%}
```{r trend_price_over_time_cms2, warning=FALSE}
#| title: !expr paste("CMS2 - Price per", unit_label, "Over Time")

if (nrow(CMS2) > 1) {
  CMS2Trend <- ggplot(CMS2, aes(DateSold, .data[[target_price_col]])) +
    geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
                color = "black", linewidth = 0.8) +
    geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
                color = "red4", linewidth = 1, linetype = "dashed") +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 7),
                       expand = expansion(mult = c(0.005, 0.05))) +
    scale_x_date(breaks = date_breaks_vec,
                 labels = scales::date_format(date_label_format)) +
    theme_custom() +
    theme_point_colour() +
    labs(
      title = paste0("Price per ", unit_label, " Over Time"),
      subtitle = str_wrap(Subtitle3, 66),
      x = "Sale Date",
      y = paste0("Price per ", unit_label),
      caption = paste0("Daily Change: $", MktCondVal2,
                       "; Median Price/", unit_label, ": ", label_dollar(accuracy = price_accuracy)(MedianPriceUnit2),
                       "; ", label_percent(accuracy = .01)(AnnualIncreasePer2),
                       " per year | ", params$Company)
    )
  CMS2Trend
} else {
  empty_chart("Insufficient CMS2 data for trend chart")
}
```

```{r interactive_trend_cms2, warning=FALSE}
#| title: !expr paste("CMS2 - Interactive Price per", unit_label, "Over Time")

if (nrow(CMS2) > 1) {
  p <- ggplot(CMS2, aes(DateSold, .data[[target_price_col]])) +
    geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
                color = "black", linewidth = 0.8) +
    geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
                color = "red4", linewidth = 1, linetype = "dashed") +
    geom_point(aes(text = paste0("N1ID: ", N1ID, "<br>",
                                  "Address: ", Address, "<br>",
                                  "City: ", City, "<br>",
                                  "Zoning: ", Zoning, "<br>",
                                  unit_label_full, ": ", scales::number(.data[[target_size_col]], accuracy = size_accuracy, big.mark = ","), "<br>",
                                  "Price/", unit_label, ": ", dollar(.data[[target_price_col]], accuracy = price_accuracy))),
               shape = 21, size = 3, fill = "steelblue1", alpha = 0.6,
               color = "steelblue4", stroke = 0.5) +
    scale_y_continuous(labels = dollar, limits = c(0, NA)) +
    theme_custom() +
    labs(
      title = paste0("Price per ", unit_label, " Over Time (5th-95th Percentile, Interactive)"),
      subtitle = Subtitle3,
      x = "Sale Date",
      y = paste0("Price per ", unit_label)
    )

  ggplotly(p, tooltip = "text")
} else {
  empty_chart("Insufficient CMS2 data for interactive trend chart")
}
```

### Price per `r unit_label` by Parcel Size
```{r size_price_by_size_cms2}
#| title: !expr paste("CMS2 Price per", unit_label, "by Parcel Size")

if (nrow(CMS2) > 1) {
  # Adaptive x-axis precision and break count based on data range
  cms2_size_range <- diff(range(CMS2[[target_size_col]], na.rm = TRUE))
  x_accuracy2 <- dplyr::case_when(
    cms2_size_range < 10  ~ 0.01,
    cms2_size_range < 100 ~ 1,
    TRUE                  ~ size_accuracy
  )
  x_n_breaks2 <- dplyr::case_when(
    cms2_size_range < 1  ~ 5L,
    cms2_size_range < 10 ~ 7L,
    cms2_size_range < 50 ~ 8L,
    TRUE                 ~ 10L
  )

  # Predict price at subject lot size from linear model
  size_lm2 <- lm(reformulate(target_size_col, target_price_col), data = CMS2)
  size_pred2 <- predict(size_lm2, newdata = setNames(data.frame(sub_lot_size), target_size_col))

  CMS2Size <- ggplot(CMS2, aes(.data[[target_size_col]], .data[[target_price_col]])) +
    geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
                color = "black", linewidth = 0.8) +
    geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
                color = "red4", linewidth = 1, linetype = "dashed") +
    geom_vline(aes(xintercept = sub_lot_size), color = "dodgerblue2",
               linewidth = 1.5, linetype = "dashed") +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 7),
                       expand = expansion(mult = c(0.005, 0.05))) +
    scale_x_continuous(labels = scales::number_format(accuracy = x_accuracy2, big.mark = ","),
                       breaks = scales::pretty_breaks(n = x_n_breaks2),
                       expand = expansion(mult = c(0.005, 0.05))) +
    theme_custom() +
    theme_point_colour() +
    labs(
      title = paste0("Price per ", unit_label, " by Parcel Size"),
      subtitle = str_wrap(Subtitle3, 66),
      x = paste0("Parcel Size (", unit_label_full, ")"),
      y = paste0("Price per ", unit_label),
      caption = paste0("Subject property: ", scales::number(sub_lot_size, accuracy = x_accuracy2, big.mark = ","), " ", unit_label,
                       " (blue line); Trend value: ", label_dollar(accuracy = price_accuracy)(size_pred2),
                       "/", unit_label, " | ", params$Company)
    )
  CMS2Size
} else {
  empty_chart("Insufficient CMS2 data for parcel-size chart")
}
```

```{r interactive_size_cms2, warning=FALSE}
#| title: !expr paste("CMS2 - Interactive Price per", unit_label, "by Parcel Size")

if (nrow(CMS2) > 1) {
  p_size2 <- ggplot(CMS2, aes(.data[[target_size_col]], .data[[target_price_col]])) +
    geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
                color = "black", linewidth = 0.8) +
    geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
                color = "red4", linewidth = 1, linetype = "dashed") +
    geom_vline(aes(xintercept = sub_lot_size), color = "dodgerblue2",
               linewidth = 1.5, linetype = "dashed") +
    geom_point(aes(text = paste0("N1ID: ", N1ID, "<br>",
                                  "Address: ", Address, "<br>",
                                  "City: ", City, "<br>",
                                  "Zoning: ", Zoning, "<br>",
                                  unit_label_full, ": ", scales::number(.data[[target_size_col]], accuracy = size_accuracy, big.mark = ","), "<br>",
                                  "Price/", unit_label, ": ", dollar(.data[[target_price_col]], accuracy = price_accuracy))),
               shape = 21, size = 3, fill = "steelblue1", alpha = 0.6,
               color = "steelblue4", stroke = 0.5) +
    scale_y_continuous(labels = dollar, limits = c(0, NA)) +
    scale_x_continuous(labels = scales::number_format(accuracy = x_accuracy2, big.mark = ",")) +
    theme_custom() +
    labs(
      title = paste0("Price per ", unit_label, " by Parcel Size (5th-95th Percentile, Interactive)"),
      subtitle = Subtitle3,
      x = paste0("Parcel Size (", unit_label_full, ")"),
      y = paste0("Price per ", unit_label)
    )

  ggplotly(p_size2, tooltip = "text")
} else {
  empty_chart("Insufficient CMS2 data for interactive parcel-size chart")
}
```

```{r size_adj_price_by_size_cms2}
#| title: !expr paste("CMS2 Adjusted Price per", unit_label, "by Parcel Size")

if (nrow(CMS2) > 1) {
  # Predict adjusted price at subject lot size from linear model
  size_adj_lm2 <- lm(reformulate(target_size_col, "AdjPrice"), data = CMS2)
  size_adj_pred2 <- predict(size_adj_lm2, newdata = setNames(data.frame(sub_lot_size), target_size_col))

  CMS2SizeAdj <- ggplot(CMS2, aes(.data[[target_size_col]], AdjPrice)) +
    geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
                color = "black", linewidth = 0.8) +
    geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
                color = "red4", linewidth = 1, linetype = "dashed") +
    geom_vline(aes(xintercept = sub_lot_size), color = "dodgerblue2",
               linewidth = 1.5, linetype = "dashed") +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 7),
                       expand = expansion(mult = c(0.005, 0.05))) +
    scale_x_continuous(labels = scales::number_format(accuracy = x_accuracy2, big.mark = ","),
                       breaks = scales::pretty_breaks(n = x_n_breaks2),
                       expand = expansion(mult = c(0.005, 0.05))) +
    theme_custom() +
    theme_point_colour() +
    labs(
      title = paste0("Price per ", unit_label, " by Parcel Size"),
      subtitle = str_wrap(Subtitle4, 66),
      x = paste0("Parcel Size (", unit_label_full, ")"),
      y = paste0("Adjusted Price per ", unit_label),
      caption = paste0("Subject: ", scales::number(sub_lot_size, accuracy = x_accuracy2, big.mark = ","), " ", unit_label,
                       "; Trend value: ", label_dollar(accuracy = price_accuracy)(size_adj_pred2),
                       "/", unit_label, "; Adjusted $", MktCondVal2, "/day | ", params$Company)
    )
  CMS2SizeAdj
} else {
  empty_chart("Insufficient CMS2 data for adjusted parcel-size chart")
}
```

### Price per `r unit_label` by Distance
```{r dist_price_by_distance_cms2}
#| title: !expr paste("CMS2 Price per", unit_label, "by Distance")

if (nrow(CMS2) > 1) {
  # Select distance column and label based on SubRef setting
  dist_col <- if (params$SubRef == "Ref") "RefDist" else "SubDist"
  dist_label <- if (params$SubRef == "Ref") params$RefPoint else "subject"
  dist_vline <- if (params$SubRef == "Ref") Subject$RefDist else Subject$SubDist

  # Predict price at vline distance from linear model
  dist_lm2 <- lm(reformulate(dist_col, target_price_col), data = CMS2)
  dist_pred2 <- predict(dist_lm2, newdata = setNames(data.frame(dist_vline), dist_col))
  dist_adj_lm2 <- lm(reformulate(dist_col, "AdjPrice"), data = CMS2)
  dist_adj_pred2 <- predict(dist_adj_lm2, newdata = setNames(data.frame(dist_vline), dist_col))

  CMS2Dist <- ggplot(CMS2, aes(.data[[dist_col]], .data[[target_price_col]])) +
    geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
                color = "black", linewidth = 0.8) +
    geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
                color = "red4", linewidth = 1, linetype = "dashed") +
    {if (params$SubRef == "Ref") geom_vline(aes(xintercept = dist_vline), color = "dodgerblue2",
               linewidth = 1.5, linetype = "dashed")} +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.05))) +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 10),
                       expand = expansion(mult = c(0.005, 0.05))) +
    theme_custom() +
    theme_point_colour() +
    labs(
      title = paste0("Price per ", unit_label, " by Distance from ", dist_label),
      subtitle = str_wrap(Subtitle3, 66),
      x = paste0("Distance from ", dist_label, " (km)"),
      y = paste0("Price per ", unit_label),
      caption = if (params$SubRef == "Ref") paste0("Subject property distance: ", dist_vline, " km; Trend value: ", label_dollar(accuracy = price_accuracy)(dist_pred2), "/", unit_label, " | ", params$Company) else paste0("Trend value at subject: ", label_dollar(accuracy = price_accuracy)(dist_pred2), "/", unit_label, " | ", params$Company)
    )
  CMS2Dist
} else {
  empty_chart("Insufficient CMS2 data for distance chart")
}
```

```{r dist_adj_price_by_distance_cms2}
#| title: !expr paste("CMS2 Adjusted Price per", unit_label, "by Distance")

if (nrow(CMS2) > 1) {
  CMS2DistAdj <- ggplot(CMS2, aes(.data[[dist_col]], AdjPrice)) +
    geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
                color = "black", linewidth = 0.8) +
    geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
                color = "red4", linewidth = 1, linetype = "dashed") +
    {if (params$SubRef == "Ref") geom_vline(aes(xintercept = dist_vline), color = "dodgerblue2",
               linewidth = 1.5, linetype = "dashed")} +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.05))) +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 10),
                       expand = expansion(mult = c(0.005, 0.05))) +
    theme_custom() +
    theme_point_colour() +
    labs(
      title = paste0("Price per ", unit_label, " by Distance from ", dist_label),
      subtitle = str_wrap(Subtitle4, 66),
      x = paste0("Distance from ", dist_label, " (km)"),
      y = paste0("Adjusted Price per ", unit_label),
      caption = if (params$SubRef == "Ref") paste0("Subject distance: ", dist_vline, " km; Trend value: ", label_dollar(accuracy = price_accuracy)(dist_adj_pred2), "/", unit_label, "; Adjusted $", MktCondVal2, "/day | ", params$Company) else paste0("Trend value at subject: ", label_dollar(accuracy = price_accuracy)(dist_adj_pred2), "/", unit_label, "; Adjusted $", MktCondVal2, "/day | ", params$Company)
    )
  CMS2DistAdj
} else {
  empty_chart("Insufficient CMS2 data for adjusted distance chart")
}
```

### Price/`r unit_label` by Neighbourhood
```{r cms2_neighbourhood_boxplot, echo=FALSE, message=FALSE, warning=FALSE}
#| title: !expr paste("CMS2 - Price/", unit_label, "by Neighbourhood")

if ("Neighborhood" %in% names(CMS2) && nrow(CMS2) > 0 &&
    length(unique(CMS2$Neighborhood[!is.na(CMS2$Neighborhood) & CMS2$Neighborhood != ""])) > 0) {
  .rollup <- rollup_neighbourhoods_for_boxplot(CMS2, target_price_col, max_bars = 10)
  cms2_nb        <- .rollup$df
  nb_stats2      <- .rollup$stats
  nb_colors_cms2 <- .rollup$colors

  ggplot(cms2_nb, aes(x = Neighborhood, y = .data[[target_price_col]], fill = Neighborhood)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_jitter(width = 0.15, size = 1.5, alpha = 0.4, color = "steelblue4") +
    geom_text(data = nb_stats2,
              aes(x = Neighborhood, y = q3, label = dollar(med, accuracy = price_accuracy)),
              hjust = -0.15, vjust = -0.7, size = 3.5, color = "grey30", fontface = "italic",
              inherit.aes = FALSE) +
    scale_fill_manual(values = nb_colors_cms2) +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.18))) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Price per ", unit_label, " by Neighbourhood"),
      subtitle = str_wrap(Subtitle3, 80),
      x = NULL,
      y = paste0("Price per ", unit_label),
      caption = params$Company
    )
} else {
  empty_chart("No neighbourhood data available in CMS2")
}
```

```{r cms2_adj_neighbourhood_boxplot, echo=FALSE, message=FALSE, warning=FALSE}
#| title: !expr paste("CMS2 - Time Adjusted Price/", unit_label, "by Neighbourhood")

if ("Neighborhood" %in% names(CMS2) && nrow(CMS2) > 0 &&
    length(unique(CMS2$Neighborhood[!is.na(CMS2$Neighborhood) & CMS2$Neighborhood != ""])) > 0) {
  .rollup <- rollup_neighbourhoods_for_boxplot(CMS2, "AdjPrice", max_bars = 10)
  cms2_nb         <- .rollup$df
  nb_stats2a      <- .rollup$stats
  nb_colors_cms2a <- .rollup$colors

  ggplot(cms2_nb, aes(x = Neighborhood, y = AdjPrice, fill = Neighborhood)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_jitter(width = 0.15, size = 1.5, alpha = 0.4, color = "steelblue4") +
    geom_text(data = nb_stats2a,
              aes(x = Neighborhood, y = q3, label = dollar(med, accuracy = price_accuracy)),
              hjust = -0.15, vjust = -0.7, size = 3.5, color = "grey30", fontface = "italic",
              inherit.aes = FALSE) +
    scale_fill_manual(values = nb_colors_cms2a) +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.18))) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Adjusted Price per ", unit_label, " by Neighbourhood"),
      subtitle = str_wrap(Subtitle4, 80),
      x = NULL,
      y = paste0("Adjusted Price per ", unit_label),
      caption = paste0("Adjusted $", MktCondVal2, "/day | ", params$Company)
    )
} else {
  empty_chart("No neighbourhood data available in CMS2")
}
```

### Price/`r unit_label` by Zoning
```{r cms2_zoning_boxplot, echo=FALSE, message=FALSE, warning=FALSE}
#| title: !expr paste("CMS2 - Price/", unit_label, "by Zoning")

if ("Zoning" %in% names(CMS2) && nrow(CMS2) > 0 &&
    length(unique(CMS2$Zoning[!is.na(CMS2$Zoning) & CMS2$Zoning != ""])) > 0) {
  cms2_zn <- CMS2 %>%
    filter(!is.na(Zoning), Zoning != "")

  zn_stats2 <- cms2_zn %>%
    group_by(Zoning) %>%
    summarise(med = median(.data[[target_price_col]], na.rm = TRUE),
              q3 = quantile(.data[[target_price_col]], 0.75, na.rm = TRUE),
              n = n()) %>%
    filter(n >= 3) %>%
    arrange(med)

  cms2_zn <- cms2_zn %>% filter(Zoning %in% zn_stats2$Zoning)

  zn_labels2 <- paste0(zn_stats2$Zoning, " (", zn_stats2$n, ")")
  cms2_zn$Zoning <- factor(cms2_zn$Zoning,
                           levels = zn_stats2$Zoning,
                           labels = zn_labels2)

  zn_colors_cms2 <- zoning_color_map[zn_stats2$Zoning]
  zn_stats2$Zoning <- factor(zn_labels2, levels = zn_labels2)

  ggplot(cms2_zn, aes(x = Zoning, y = .data[[target_price_col]], fill = Zoning)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_jitter(width = 0.15, size = 1.5, alpha = 0.4, color = "steelblue4") +
    geom_text(data = zn_stats2,
              aes(x = Zoning, y = q3, label = dollar(med, accuracy = price_accuracy)),
              hjust = -0.15, vjust = -0.7, size = 3.5, color = "grey30", fontface = "italic",
              inherit.aes = FALSE) +
    scale_fill_manual(values = setNames(zn_colors_cms2, zn_labels2)) +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.18))) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Price per ", unit_label, " by Zoning"),
      subtitle = str_wrap(paste0(Subtitle3, "; Min. 3 sales per zoning"), 80),
      x = NULL,
      y = paste0("Price per ", unit_label),
      caption = params$Company
    )
} else {
  empty_chart("No zoning data available in CMS2")
}
```

```{r cms2_adj_zoning_boxplot, echo=FALSE, message=FALSE, warning=FALSE}
#| title: !expr paste("CMS2 - Time Adjusted Price/", unit_label, "by Zoning")

if ("Zoning" %in% names(CMS2) && nrow(CMS2) > 0 &&
    length(unique(CMS2$Zoning[!is.na(CMS2$Zoning) & CMS2$Zoning != ""])) > 0) {
  cms2_zn <- CMS2 %>%
    filter(!is.na(Zoning), Zoning != "")

  zn_stats2a <- cms2_zn %>%
    group_by(Zoning) %>%
    summarise(med = median(AdjPrice, na.rm = TRUE),
              q3 = quantile(AdjPrice, 0.75, na.rm = TRUE),
              n = n()) %>%
    filter(n >= 3) %>%
    arrange(med)

  cms2_zn <- cms2_zn %>% filter(Zoning %in% zn_stats2a$Zoning)

  zn_labels2a <- paste0(zn_stats2a$Zoning, " (", zn_stats2a$n, ")")
  cms2_zn$Zoning <- factor(cms2_zn$Zoning,
                           levels = zn_stats2a$Zoning,
                           labels = zn_labels2a)

  zn_colors_cms2a <- zoning_color_map[zn_stats2a$Zoning]
  zn_stats2a$Zoning <- factor(zn_labels2a, levels = zn_labels2a)

  ggplot(cms2_zn, aes(x = Zoning, y = AdjPrice, fill = Zoning)) +
    geom_boxplot(alpha = 0.6, color = "steelblue4",
                 outlier.shape = 21, outlier.fill = "red4", outlier.alpha = 0.6) +
    geom_jitter(width = 0.15, size = 1.5, alpha = 0.4, color = "steelblue4") +
    geom_text(data = zn_stats2a,
              aes(x = Zoning, y = q3, label = dollar(med, accuracy = price_accuracy)),
              hjust = -0.15, vjust = -0.7, size = 3.5, color = "grey30", fontface = "italic",
              inherit.aes = FALSE) +
    scale_fill_manual(values = setNames(zn_colors_cms2a, zn_labels2a)) +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.18))) +
    coord_flip() +
    theme_custom() +
    theme(axis.text.y = element_text(size = 9),
          legend.position = "none") +
    labs(
      title = paste0("Adjusted Price per ", unit_label, " by Zoning"),
      subtitle = str_wrap(paste0(Subtitle4, "; Min. 3 sales per zoning"), 80),
      x = NULL,
      y = paste0("Adjusted Price per ", unit_label),
      caption = paste0("Adjusted $", MktCondVal2, "/day | ", params$Company)
    )
} else {
  empty_chart("No zoning data available in CMS2")
}
```

`r if(params$PricePerUnit == "Y") '# CMS MF Density {orientation="rows"}'`

```{r subtitles_lu, include=FALSE}
#| eval: !expr params$PricePerUnit == "Y"

# Define LU subtitles (used by multiple charts including density)
SubtitleLU1 <- paste0("CMS; ",
  ifelse(params$SubRef == "Ref",
         paste0(params$LoDistKM, "-", params$HiDistKM),
         paste0(params$LoDistKM, "-", params$HiDistKM)),
  " km from ",
  ifelse(params$SubRef == "Ref", params$RefPoint, "subject"),
  "; ", params$LoLandSizeUnit, "-", params$HiLandSizeUnit,
  " Units; ", format(LoDate, "%b-%Y")," to ", format(HiDate, "%b-%Y")
)

SubtitleLU2 <- paste0("CMS (Time-Adjusted); ",
  ifelse(params$SubRef == "Ref",
         paste0(params$LoDistKM, "-", params$HiDistKM),
         paste0(params$LoDistKM, "-", params$HiDistKM)),
  " km from ",
  ifelse(params$SubRef == "Ref", params$RefPoint, "subject"),
  "; ", params$LoLandSizeUnit, "-", params$HiLandSizeUnit,
  " Units; ", format(LoDate, "%b-%Y")," to ", format(HiDate, "%b-%Y")
)
```

`r if(params$PricePerUnit == "Y") '## Row {height=50% .tabset}'`

`r if(params$PricePerUnit == "Y") '### Heatmap - Price/Land Unit'`
```{r map_cms_heatmap_lu}
#| eval: !expr params$PricePerUnit == "Y" && nrow(CMSLU) > 0
# Heatmap of CMSLU sales colored by quantile bucket of price per land unit.

# Guard for interactive execution
if(nrow(CMSLU) > 0 && "Lon" %in% names(CMSLU)) {

# Create sf version with tooltip
CMSLU_sf <- CMSLU %>%
  filter(!is.na(Lon) & !is.na(Lat) & !is.na(PriceLandUnit)) %>%
  mutate(tooltip = paste0(
    Address, ", ", City,
    "<br>Date: ", format(DateSold, "%Y-%m-%d"),
    "<br>Price: ", scales::dollar(PriceSold, accuracy = 1),
    "<br>Land Units: ", LandUnits,
    "<br>$/Unit: ", scales::dollar(PriceLandUnit, accuracy = 1),
    "<br>Zoning: ", Zoning
  )) %>%
  st_as_sf(coords = c("Lon", "Lat"), crs = 4326)

# Discrete quantile color scale (5 buckets with rounded values)
cmslu_price_scale <- create_quantile_classification(
  data = CMSLU_sf,
  column = "PriceLandUnit",
  n = 5
)

# Assign each point to a price bucket for categorical legend interactivity
cmslu_buckets <- assign_buckets(
  data = CMSLU_sf,
  column = "PriceLandUnit",
  classification = cmslu_price_scale,
  label_formatter = function(breaks) format_price_bucket_labels(cmslu_price_scale, "Unit", kind = "unit_price")
)
CMSLU_sf$price_bucket <- cmslu_buckets$bucket_col

# Create match expression for categorical coloring
cmslu_price_match_expr <- match_expr(
  column = "price_bucket",
  values = cmslu_buckets$labels,
  stops = unname(cmslu_buckets$color_map),
  default = "#808080"
)

# Get and prepare municipal boundaries for CMSLU
muni_bnd_cmslu <- prep_muni_bnd(get_filtered_muni_boundaries(CMSLU), muni_color_map)

# Get and prepare Winnipeg neighbourhood boundaries (if available)
wpg_nb_bnd_cmslu <- prep_wpg_nb_bnd(get_filtered_wpg_nb_boundaries(CMSLU))

# Compute bbox for CMSLU (conditionally created)
map_bbox_cmslu <- compute_map_bounds(CMSLU_sf, params, radius_km = params$HiDistKM)

# Build base map with boundaries and distance rings
Map1CMSHLU <- build_base_map(
  bounds = map_bbox_cmslu,
  muni_bnd = muni_bnd_cmslu, wpg_nb_bnd = wpg_nb_bnd_cmslu,
  muni_color_map = muni_color_map, id_prefix = "cmslu_heatmap",
  circle_lon = circle_lon, circle_lat = circle_lat,
  lo_km = params$LoDistKM, hi_km = params$HiDistKM, show_rings = TRUE
)

# Add data layer and categorical legend (click legend items to show/hide)
Map1CMSHLU <- Map1CMSHLU |>
  add_circle_layer(
    id = "cms-heatmap-lu",
    source = CMSLU_sf,
    circle_color = cmslu_price_match_expr,
    circle_radius = circle_radius,
    circle_stroke_color = "black",
    circle_stroke_width = 1,
    circle_opacity = 0.8,
    tooltip = "tooltip",
    popup = "popup"
  ) |>
  add_property_markers(params) |>
  add_legend(
    legend_title = "Sale Price/Land Unit",
    values = cmslu_buckets$labels,
    colors = unname(cmslu_buckets$color_map),
    type = "categorical",
    layer_id = "cms-heatmap-lu",
    interactive = TRUE,
    position = "bottom-right"
  )

Map1CMSHLU
} # End guard
```

`r if(params$PricePerUnit == "Y") '## Row {height=50% .tabset}'`

`r if(params$PricePerUnit == "Y") '### Price Trends/Land Unit {width=50%}'`

```{r trend_price_over_time_lu, warning=FALSE}
#| eval: !expr params$PricePerUnit == "Y" && nrow(CMSLU) > 0
# Static trend chart: price per land unit over time.
# Note: time-adjustment metrics are derived from CMS1 ($/Acre), not refitted
# on CMSLU per-unit values, so per-unit daily-change/annual-change metrics
# are intentionally omitted from the caption.

# Guard for interactive execution
if(nrow(CMSLU) > 0 && "PriceLandUnit" %in% names(CMSLU)) {

CMSLUTrend <- ggplot(CMSLU, aes(DateSold, PriceLandUnit)) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  scale_y_continuous(labels = dollar, limits = c(0,NA),
                     breaks = scales::pretty_breaks(n = 7),
                     expand = expansion(mult = c(0.005, 0.05))) +
  scale_x_date(breaks = date_breaks_vec,
               labels = scales::date_format(date_label_format)) +
  theme_custom() +
  theme_point_colour() +
  labs(
    title = "Land Price per Land Unit Over Time",
    subtitle = str_wrap(SubtitleLU1, 66),
    x = "Sale Date",
    y = "Price per Land Unit",
    caption = params$Company
  )
CMSLUTrend
} # End guard
```

```{r interactive_trend_lu, warning=FALSE}
#| eval: !expr params$PricePerUnit == "Y" && nrow(CMSLU) > 0
# Plotly interactive version of the price per land unit trend chart.

if(nrow(CMSLU) > 0) {
p <- ggplot(CMSLU, aes(DateSold, PriceLandUnit)) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  geom_point(aes(text = paste0("N1ID: ", N1ID, "<br>",
                                "Address: ", Address, "<br>",
                                "City: ", City, "<br>",
                                "Zoning: ", Zoning, "<br>",
                                "Land Units: ", LandUnits, "<br>",
                               "Price/Land Unit: ", dollar(PriceLandUnit), "<br>",
                                "Acres: ", Acres, "<br>",
                                "Price/Acre: ", dollar(PriceAcre))),
             shape = 21, size = 3, fill = "steelblue1", alpha = 0.6,
             color = "steelblue4", stroke = 0.5) +
  scale_y_continuous(labels = dollar, limits = c(0,NA)) +
  theme_custom() +
  labs(
    title = "Land Price per Land Unit Over Time (Interactive)",
    subtitle = SubtitleLU1,
    x = "Sale Date",
    y = "Price per Land Unit"
  )

ggplotly(p, tooltip = "text")
} # End guard
```

`r if(params$PricePerUnit == "Y") '### Price per Unit by Project Size'`
```{r plot_lu_size}
#| eval: !expr params$PricePerUnit == "Y" && nrow(CMSLU) > 0
#| title: "Price per Unit vs. Total Units"

if(nrow(CMSLU) > 0) {
ggplot(CMSLU, aes(LandUnits, PriceLandUnit)) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F, color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F, color = "red4", linewidth = 1, linetype="dashed") +
  #geom_vline(aes(xintercept = params$SubLandUnits), color = "dodgerblue2", linetype = "dashed", linewidth = 1.1) +
  #annotate("label", x = params$SubLandUnits, y = Inf, label = "Subject", color = "dodgerblue2", fill = "white", fontface = "bold", vjust = 2) +
  scale_y_continuous(labels = dollar, limits = c(0,NA), breaks = breaks_pretty(n = 5)) +
  scale_x_continuous(labels = scales::comma, limits = c(0, NA), breaks = breaks_pretty(n = 6)) +
  theme_custom() +
  theme_point_colour() +
  labs(title = "Price per Unit by Total Units",
  subtitle = str_wrap(SubtitleLU1, 66), x = "Total Land Units", y = "Price per Land Unit", caption = params$Company)
} # End guard
```

```{r plot_lu_size_adj}
#| eval: !expr params$PricePerUnit == "Y" && nrow(CMSLU) > 0
#| title: "Price per Unit vs. Total Units (Time-Adjusted)"

if(nrow(CMSLU) > 0) {
ggplot(CMSLU, aes(LandUnits, AdjPriceUnit)) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F, color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F, color = "red4", linewidth = 1, linetype="dashed") +
  #geom_vline(aes(xintercept = params$SubLandUnits), color = "dodgerblue2", linetype = "dashed", linewidth = 1.1) +
  #annotate("label", x = params$SubLandUnits, y = Inf, label = "Subject", color = "dodgerblue2", fill = "white", fontface = "bold", vjust = 2) +
  scale_y_continuous(labels = dollar, limits = c(0,NA), breaks = breaks_pretty(n = 5)) +
  scale_x_continuous(labels = scales::comma, limits = c(0, NA), breaks = breaks_pretty(n = 6)) +
  theme_custom() +
  theme_point_colour() +
  labs(title = "Price per Unit by Total Units",
  subtitle = str_wrap(SubtitleLU2, 66), x = "Total Land Units", y = "Price per Land Unit (Time-Adjusted)", caption = params$Company)
} # End guard
```

`r if(params$PricePerUnit == "Y") paste0('### Price per ', unit_label, ' by Density')`
```{r plot_density_cmslu}
#| title: !expr paste("Price per", unit_label, "by Density (Units/Acre)")
#| eval: !expr params$PricePerUnit == "Y"

# Initialize as NULL so the export chunk doesn't crash
CMSLUDens1 <- NULL

# Perform the check: Column exists AND has enough valid data pairs
if (params$PricePerUnit == "Y" &&
    "DUAcre" %in% names(CMSLU) &&
    target_price_col %in% names(CMSLU) &&
    sum(!is.na(CMSLU$DUAcre) & !is.na(CMSLU[[target_price_col]])) > 2) {

  # 1. Fit the linear model on CMSLU (multi-family filtered set) using the
  #    AcOrSF-selected price column.
  fit_lu <- lm(reformulate("DUAcre", target_price_col), data = CMSLU)

  # 2. Calculate predicted price at subject density
  price_lu_raw <- predict(fit_lu, newdata = data.frame(DUAcre = SubLandUnitDensity1))
  # Round to thousands for $/Acre, to cents for $/SF
  price_lu_rounded <- if (params$AcOrSF == "sf") round(price_lu_raw, 2) else round(price_lu_raw, -3)

  intersection_text_lu <- paste0("Intersection (blue line) @ ",
                                 scales::dollar(price_lu_rounded, accuracy = price_accuracy))

  # 3. Create the plot object
  CMSLUDens1 <- ggplot(CMSLU, aes(DUAcre, .data[[target_price_col]])) +
    geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F, color = "black", linewidth = 0.8) +
    geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F, color = "red4", linewidth = 1, linetype = "dashed") +
    scale_y_continuous(labels = label_dollar(), limits = c(0, NA), breaks = breaks_pretty(n = 5)) +
    scale_x_continuous(labels = scales::comma, limits = c(0, NA), breaks = breaks_pretty(n = 6)) +
    geom_vline(aes(xintercept = SubLandUnitDensity1), color = "dodgerblue2", linewidth = 1.5, linetype = "dashed") +
    theme_custom() +
    theme_point_colour() +
    labs(
      title = paste0("Price per ", unit_label, " by Density"),
      subtitle = str_wrap(SubtitleLU1, 66),
      x = "Land Units per Acre (Density)",
      y = paste0("Price per ", unit_label),
      caption = paste0(intersection_text_lu, " | ", params$Company)
    )

  # Display the plot in the dashboard
  CMSLUDens1

} else {
  # If data is missing, show a placeholder so the dashboard doesn't look broken
  cat("Insufficient density data available for this comparable set.")
}
```
```{r plot_density_cmslu_time_adjusted}
#| title: !expr paste("Price per", unit_label, "by Density (Units/Acre) - Time Adjusted")
#| eval: !expr params$PricePerUnit == "Y"

CMSLUDens2 <- NULL

if (params$PricePerUnit == "Y" &&
    "DUAcre" %in% names(CMSLU) &&
    "AdjPriceLU" %in% names(CMSLU) &&
    sum(!is.na(CMSLU$DUAcre) & !is.na(CMSLU$AdjPriceLU)) > 2) {

  fit_lu_adj <- lm(AdjPriceLU ~ DUAcre, data = CMSLU)
  price_lu_raw_adj <- predict(fit_lu_adj, newdata = data.frame(DUAcre = SubLandUnitDensity1))
  price_lu_rounded_adj <- if (params$AcOrSF == "sf") round(price_lu_raw_adj, 2) else round(price_lu_raw_adj, -3)

  intersection_text_lu_adj <- paste0("Intersection (blue line) @ ",
                                     scales::dollar(price_lu_rounded_adj, accuracy = price_accuracy))

  CMSLUDens2 <- ggplot(CMSLU, aes(DUAcre, AdjPriceLU)) +
    geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F, color = "black", linewidth = 0.8) +
    geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F, color = "red4", linewidth = 1, linetype = "dashed") +
    scale_y_continuous(labels = label_dollar(), limits = c(0, NA), breaks = breaks_pretty(n = 5)) +
    scale_x_continuous(labels = scales::comma, limits = c(0, NA), breaks = breaks_pretty(n = 6)) +
    geom_vline(aes(xintercept = SubLandUnitDensity1), color = "dodgerblue2", linewidth = 1.5, linetype = "dashed") +
    theme_custom() +
    theme_point_colour() +
    labs(
      title = paste0("Price per ", unit_label, " by Density (Time-Adjusted)"),
      subtitle = str_wrap(SubtitleLU2, 66),
      x = "Land Units per Acre (Density)",
      y = paste0("Price per ", unit_label, " (Time-Adjusted)"),
      caption = paste0(intersection_text_lu_adj, " | ", params$Company)
    )

  CMSLUDens2

} else {
  cat("Insufficient density data available for this comparable set.")
}
```

`r if(params$PricePerUnit == "Y") '### Density by Zoning'`
```{r plot_density_by_zoning_cmslu}
#| title: "Density (Units/Acre) by Zoning"
#| eval: !expr params$PricePerUnit == "Y"

# Boxplot of actual built density (DUAcre) grouped by Zoning, drawn from CMSLU.
# Goal: surface the typical units-per-acre that has been built within each
# zoning designation in the comparable set.

CMSLUDensZone <- NULL

if (params$PricePerUnit == "Y" &&
    "DUAcre" %in% names(CMSLU) &&
    "Zoning" %in% names(CMSLU) &&
    sum(!is.na(CMSLU$DUAcre) & !is.na(CMSLU$Zoning) & nzchar(CMSLU$Zoning)) > 0) {

  # Order zonings on the x-axis by median density (ascending) for readability
  CMSLUDensZoneData <- CMSLU %>%
    filter(!is.na(DUAcre), !is.na(Zoning), nzchar(Zoning)) %>%
    mutate(Zoning = forcats::fct_reorder(Zoning, DUAcre, .fun = median, .na_rm = TRUE))

  # Per-zoning summary used for the in-chart annotations placed just above the x-axis
  zone_stats <- CMSLUDensZoneData %>%
    group_by(Zoning) %>%
    summarise(
      n = dplyr::n(),
      med = median(DUAcre, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(label = paste0("n=", n, "\nmed=", round(med, 1)))

  CMSLUDensZone <- ggplot(CMSLUDensZoneData, aes(x = Zoning, y = DUAcre)) +
    geom_boxplot(fill = "steelblue1", color = "steelblue4",
                 alpha = 0.6, outlier.shape = NA) +
    geom_jitter(width = 0.18, height = 0, shape = 21, size = 2,
                fill = "steelblue1", color = "steelblue4",
                alpha = 0.7, stroke = 0.4) +
    geom_hline(aes(yintercept = SubLandUnitDensity1),
               color = "dodgerblue2", linewidth = 1.2, linetype = "dashed") +
    annotate("label", x = Inf, y = SubLandUnitDensity1,
             label = paste0("Subject: ", SubLandUnitDensity1, " u/ac"),
             color = "dodgerblue2", fill = "white", fontface = "bold",
             hjust = 1.05, vjust = -0.3, label.size = 0.4) +
    geom_text(data = zone_stats,
              aes(x = Zoning, y = 0, label = label),
              vjust = -0.1, size = 2.9, color = "gray25",
              lineheight = 0.85, inherit.aes = FALSE) +
    scale_y_continuous(labels = scales::comma, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.08, 0.08))) +
    theme_custom() +
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
    labs(
      title = "Built Density by Zoning",
      subtitle = str_wrap(
        sub("^CMS", "CMS (NOTE: some parcels re-zoned after the land sale)", SubtitleLU1),
        80
      ),
      x = "Zoning",
      y = "Land Units per Acre (Density)",
      caption = params$Company
    )

  CMSLUDensZone

} else {
  cat("Insufficient density-by-zoning data available for this comparable set.")
}
```

`r if(params$PricePerUnit == "Y") '### Price per Land Unit by Distance'`
```{r dist_price_by_distance_lu}
#| title: "Price per Land Unit by Distance"
#| eval: !expr params$PricePerUnit == "Y"

# Price per Land Unit vs distance from RefPoint (or subject), drawn from CMSLU.
# Mirrors dist_price_by_distance on CMS Maps & Trends but plots PriceLandUnit
# from the multi-family-filtered set.

CMSLUDist <- NULL

if (params$PricePerUnit == "Y" &&
    nrow(CMSLU) > 2 &&
    "PriceLandUnit" %in% names(CMSLU)) {

  # Switchboard - same pattern as the CMS1 distance chart
  dist_col_lu <- if (params$SubRef == "Ref") "RefDist" else "SubDist"
  dist_label_lu <- if (params$SubRef == "Ref") params$RefPoint else "subject"
  dist_vline_lu <- if (params$SubRef == "Ref") Subject$RefDist else Subject$SubDist

  # Linear-fit prediction at the subject distance for the caption
  dist_lm_lu <- lm(reformulate(dist_col_lu, "PriceLandUnit"), data = CMSLU)
  dist_pred_lu <- predict(dist_lm_lu, newdata = setNames(data.frame(dist_vline_lu), dist_col_lu))

  CMSLUDist <- ggplot(CMSLU, aes(.data[[dist_col_lu]], PriceLandUnit)) +
    geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
                color = "black", linewidth = 0.8) +
    geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
                color = "red4", linewidth = 1, linetype = "dashed") +
    {if (params$SubRef == "Ref") geom_vline(aes(xintercept = dist_vline_lu),
       color = "dodgerblue2", linewidth = 1.5, linetype = "dashed")} +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.05))) +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 10),
                       expand = expansion(mult = c(0.005, 0.05))) +
    theme_custom() +
    theme_point_colour() +
    labs(
      title = paste0("Price per Land Unit by Distance from ", dist_label_lu),
      subtitle = str_wrap(SubtitleLU1, 66),
      x = paste0("Distance from ", dist_label_lu, " (km)"),
      y = "Price per Land Unit",
      caption = if (params$SubRef == "Ref") {
        paste0("Subject distance: ", dist_vline_lu, " km; Trend value: ",
               label_dollar(accuracy = 1)(dist_pred_lu), "/Unit | ", params$Company)
      } else {
        paste0("Trend value at subject: ", label_dollar(accuracy = 1)(dist_pred_lu),
               "/Unit | ", params$Company)
      }
    )

  CMSLUDist

} else {
  cat("Insufficient distance data available for this comparable set.")
}
```

```{r dist_adj_price_by_distance_lu}
#| title: "Price per Land Unit by Distance (Time-Adjusted)"
#| eval: !expr params$PricePerUnit == "Y"

# Time-adjusted version: uses AdjPriceUnit (computed from the CMS1 $/Ac
# percentage trend - see market_condition_adjustments chunk).

CMSLUDistAdj <- NULL

if (params$PricePerUnit == "Y" &&
    nrow(CMSLU) > 2 &&
    "AdjPriceUnit" %in% names(CMSLU)) {

  dist_col_lu <- if (params$SubRef == "Ref") "RefDist" else "SubDist"
  dist_label_lu <- if (params$SubRef == "Ref") params$RefPoint else "subject"
  dist_vline_lu <- if (params$SubRef == "Ref") Subject$RefDist else Subject$SubDist

  dist_adj_lm_lu <- lm(reformulate(dist_col_lu, "AdjPriceUnit"), data = CMSLU)
  dist_adj_pred_lu <- predict(dist_adj_lm_lu, newdata = setNames(data.frame(dist_vline_lu), dist_col_lu))

  CMSLUDistAdj <- ggplot(CMSLU, aes(.data[[dist_col_lu]], AdjPriceUnit)) +
    geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
                color = "black", linewidth = 0.8) +
    geom_smooth(method = "lm", formula = y ~ poly(x,3), se = F,
                color = "red4", linewidth = 1, linetype = "dashed") +
    {if (params$SubRef == "Ref") geom_vline(aes(xintercept = dist_vline_lu),
       color = "dodgerblue2", linewidth = 1.5, linetype = "dashed")} +
    scale_y_continuous(labels = dollar, limits = c(0, NA),
                       breaks = scales::pretty_breaks(n = 6),
                       expand = expansion(mult = c(0.005, 0.05))) +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 10),
                       expand = expansion(mult = c(0.005, 0.05))) +
    theme_custom() +
    theme_point_colour() +
    labs(
      title = paste0("Price per Land Unit by Distance from ", dist_label_lu),
      subtitle = str_wrap(SubtitleLU2, 66),
      x = paste0("Distance from ", dist_label_lu, " (km)"),
      y = "Adjusted Price per Land Unit",
      caption = if (params$SubRef == "Ref") {
        paste0("Subject distance: ", dist_vline_lu, " km; Trend value: ",
               label_dollar(accuracy = 1)(dist_adj_pred_lu),
               "/Unit; CMS1 Adj $", MktCondValAc1, "/Ac/day | ", params$Company)
      } else {
        paste0("Trend value at subject: ", label_dollar(accuracy = 1)(dist_adj_pred_lu),
               "/Unit; CMS1 Adj $", MktCondValAc1, "/Ac/day | ", params$Company)
      }
    )

  CMSLUDistAdj

} else {
  cat("Insufficient distance data available for this comparable set.")
}
```

`r if(params$ExposureCharts == "Y") '# Exposure Analysis'`

`r if(params$ExposureCharts == "Y") '## Row {height=50%}'`

`r if(params$ExposureCharts == "Y") '### Exposure Histogram'`

```{r exposure_histogram}
#| eval: !expr params$ExposureCharts == "Y"
# Histogram of days-on-market for ADF vs CMS sales in the exposure price band.

if(params$ExposureCharts == "Y") {
# Creates a histogram of Exposure Times for ADF and CMS1
subtitle_hist2 <- '<span style = "color:steelblue2">**ADF**</span> and <span style = "color:steelblue4">**CMS**</span>'
ADF_ExpStats <- summary(ADF_Exp$DOM, probs = c(0.25, 0.5, 0.75), na.rm = FALSE)
# Extract the desired percentiles
Exp25 <- ADF_ExpStats[2]
Exp50 <- ADF_ExpStats[3]
Exp75 <- ADF_ExpStats[5]
ExpHist <-
  ggplot() +
  geom_histogram(data = ADF_Exp, aes(DOM_capped), color = "black", fill = "steelblue2", alpha=0.7, breaks = seq(0,1170,90)) +
  geom_histogram(data = CMS_Exp, aes(DOM_capped), color = "black", fill = "steelblue4", alpha=0.7, breaks = seq(0,1170,90)) +
  theme_custom() +
  theme(axis.text.x = element_text(vjust = 2), plot.subtitle = element_markdown(), legend.position = "none") +
  labs(title = "Exposure Times - Days on Market (DOM)",
       subtitle = paste0(format(LoDate, "%b-%Y")," to ", format(HiDate, "%b-%Y"),"; Price: ", label_dollar(accuracy = 1)(params$ExposurePriceMin),"-", label_dollar(accuracy = 1)(params$ExposurePriceMax),"; ",subtitle_hist2),
       x = "DOM - 90 day brackets; 1080-1170 bracket includes >1170 days",
       y = "Number of Sales",
       caption = paste("ADF Stats - 25th:", Exp25, "days; Median:", Exp50, "days; 75th:", Exp75,"days | ", params$Company))+
  scale_x_continuous(breaks=seq(0,1170,90))+
  scale_y_continuous(breaks = function(x) seq(0, ceiling(max(x)), by = max(1, round(max(x)/5))))
ExpHist
}
```
`r if(params$ExposureCharts == "Y") '## Row {height=50%}'`

`r if(params$ExposureCharts == "Y") '## Column {width=50%}'`

`r if(params$ExposureCharts == "Y") '### Discount by Exposure'`
```{r exposure_discount}
#| eval: !expr params$ExposureCharts == "Y"
# Scatter of list-to-sale discount percentage vs months on market.

if(params$ExposureCharts == "Y") {
# Calculate discount percentage
CMS_Exp <- CMS_Exp %>%
  mutate(
    MonthsOnMarket = DOM / 30,
    DiscountPct = ifelse(!is.na(PriceListOrigDiff) & !is.na(PriceListOrig) & PriceListOrig > 0,
                         (PriceListOrigDiff / PriceListOrig) * 100, NA)
  )

ExpDiscount <- ggplot(CMS_Exp %>% filter(!is.na(DiscountPct)),
       aes(MonthsOnMarket, DiscountPct)) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,2), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  theme_custom() +
  theme_point_colour() +
  labs(
    title = "Discount from Original List Price by Time on Market",
    subtitle = paste0("CMS; Price Range: ", dollar(params$ExposurePriceMin), " to ",
                      dollar(params$ExposurePriceMax)),
    x = "Months on Market",
    y = "Discount from List (%)",
    caption = params$Company
  )
ExpDiscount
}
```

`r if(params$ExposureCharts == "Y") '### DOM by Price'`
```{r exposure_dom_price}
#| eval: !expr params$ExposureCharts == "Y"
# Scatter of sale price vs months on market to show exposure by price level.

if(params$ExposureCharts == "Y") {
ExpDOMPrice <- ggplot(CMS_Exp, aes(MonthsOnMarket, PriceSold)) +
  geom_smooth(method = "lm", formula = y ~ poly(x,1), se = F,
              color = "black", linewidth = 0.8) +
  geom_smooth(method = "lm", formula = y ~ poly(x,2), se = F,
              color = "red4", linewidth = 1, linetype = "dashed") +
  scale_y_continuous(labels = dollar) +
  theme_custom() +
  theme_point_colour() +
  labs(
    title = "Time on Market Required by Sale Price",
    subtitle = paste0("CMS; Price Range: ", dollar(params$ExposurePriceMin), " to ",
                      dollar(params$ExposurePriceMax)),
    x = "Months on Market",
    y = "Sale Price",
    caption = params$Company
  )
ExpDOMPrice
}
```

`r if(params$FeatureImportance == "Y") '# Feature Importance {orientation="rows"}'`

`r if(params$FeatureImportance == "Y") '## Row'`

`r if(params$FeatureImportance == "Y") '### ML Feature Importance'`

```{r fi_price}
#| title: !expr paste0("Feature Importance - Price per ", unit_label, " (CMS)")
#| eval: !expr params$FeatureImportance == "Y"

if(params$FeatureImportance == "Y") {
fi_price <- fi_prepare_and_plot(CMS1, target_price_col)
fi_price
}
```

# CMS Data Table {orientation="rows"}

## Row

### CMS Full Dataset {width=100%}

```{r cms_datatable, warning=FALSE}
#| title: "Interactive Comparable Search"

# 1. Prepare display data (keeping your mutation logic for sorting)
table_data <- CMS1 %>%
  select(
    Address, City, Municipality, DateSold, PriceSold,
    LandSF, PriceLandSF, Acres, PriceAcre, Zoning, SubDist, RefDist, TaxID, N1ID
  ) %>%
  mutate(
    DateSold = format(DateSold, "%b-%Y"),
    Acres = scales::comma(Acres, accuracy = .01),
    LandSF = scales::comma(LandSF, accuracy = 1),
    PriceSold = scales::dollar(PriceSold, accuracy = 1),
    PriceLandSF = scales::dollar(PriceLandSF, accuracy = .01),
    PriceAcre = scales::dollar(PriceAcre, accuracy = 1),
    SubDist = paste0(SubDist, " km"),
    RefDist = paste0(RefDist, " km")
  )

# Define clean headers for the data table
clean_headers <- c(
  "Address", "City", "Municipality", "Sale Date", "Price",
  "Land SF", "$/SF", "Acres", "$/Acre", "Zoning",
  "Dist (Sub)", "Dist (Ref)", "Tax ID", "N1ID"
)

DT::datatable(
  table_data,
  colnames = clean_headers,
  class = "cell-border stripe hover",
  options = list(
    pageLength = 20,
    scrollX = TRUE,
    columnDefs = list(
      list(className = "dt-center", targets = 3:11),  # DateSold..RefDist
      list(width = "200px", targets = 0),             # Address
      list(width = "100px", targets = 1),             # City
      list(width = "70px",  targets = 6),             # Acres (shrink)
      list(
        width = "90px",
        targets = 12,                                 # TaxID (correct)
        render = DT::JS(
          "function(data, type, row) {",
          "  return type === 'display' ? ",
          "    '<div style=\"white-space: normal; width: 90px; font-size: 0.85em;\">' + data + '</div>' : data;",
          "}"
        )
      )
    )
  ),
  rownames = FALSE,
  filter = "top"
)
```

# Excluded Records {orientation="rows"}

## Row

### Excluded Records {width=100%}

```{r outlier_notes}
#| output: asis
# Display excluded outliers with reasons (only if any outliers were specified)
if(nrow(CMSOutliers) > 0 && any(CMSOutliers$N1ID != "")) {
  # Look up property details from ADF for each outlier
  outlier_details <- ADF %>%
    mutate(N1ID = as.character(N1ID)) %>%
    filter(N1ID %in% CMSOutliers$N1ID) %>%
    select(N1ID, Address, City, PriceSold, Acres) %>%
    left_join(CMSOutliers, by = "N1ID") %>%
    mutate(
      PriceSold = scales::dollar(PriceSold, accuracy = 1),
      Acres = scales::comma(Acres, accuracy = 0.01)
    )

  cat("**Excluded Records:**\n\n")
  for(i in seq_len(nrow(outlier_details))) {
    row <- outlier_details[i, ]
    reason_text <- if(!is.na(row$Reason) && row$Reason != "") paste0(" — *", row$Reason, "*") else ""
    cat(paste0("- **N1ID ", row$N1ID, "**: ", row$Address, ", ", row$City,
               " (", row$PriceSold, "; ", row$Acres, " ac)", reason_text, "\n"))
  }
} else {
  cat("No records excluded.\n")
}
```

### Export Charts {.hidden}

```{r export_charts, include=FALSE}
# Export charts and maps to ./charts/ directory
if (params$ExportCharts == "Y") {

  # 1. Create directory safely
  if (!dir.exists("./charts")) {
    dir.create("./charts", recursive = TRUE)
  }

  cat("Exporting charts to ./charts/ directory...\n\n")

  # 2. Refined Helper Function
  smart_save <- function(plot_obj_name, filename, w = 6.5, h = 3.5) {
    # Specify inherits = TRUE to look outside the function's local scope
    if (exists(plot_obj_name, inherits = TRUE)) {
      ggsave(paste0("./charts/", filename), get(plot_obj_name),
             width = w, height = h, units = "in", dpi = 300)
      cat(paste0("  Saved: ", filename, "\n"))
    } else {
      cat(paste0("  Skipped: ", plot_obj_name, " (Object not found)\n"))
    }
  }

  # ============ EXPORT CMS CHARTS ============
  # Filename suffix based on AcOrSF parameter
  unit_suffix <- if(params$AcOrSF == "ac") "Ac" else "SF"

  smart_save("CMS1Trend", paste0("CMS1_Trend", unit_suffix, ".png"))
  smart_save("CMS1Size", paste0("CMS1_Size", unit_suffix, ".png"))
  smart_save("CMS1SizeAdj", paste0("CMS1_SizeAdj", unit_suffix, ".png"))
  smart_save("CMS1Dist", paste0("CMS1_Dist", unit_suffix, ".png"))
  smart_save("CMS1DistAdj", paste0("CMS1_DistAdj", unit_suffix, ".png"))
  smart_save("CMS2Trend", paste0("CMS2_Trend", unit_suffix, ".png"))
  smart_save("CMS2Size", paste0("CMS2_Size", unit_suffix, ".png"))
  smart_save("CMS2SizeAdj", paste0("CMS2_SizeAdj", unit_suffix, ".png"))
  smart_save("CMS2Dist", paste0("CMS2_Dist", unit_suffix, ".png"))
  smart_save("CMS2DistAdj", paste0("CMS2_DistAdj", unit_suffix, ".png"))

  # ============ MULTIFAMILY EXPORTS (LU) ============
  if(params$PricePerUnit == "Y") {
    smart_save("CMSLUTrend", "CMS_Trend_LU.png")
    smart_save("CMSLUDens1", "CMS_Density_LU_Nominal.png")
    smart_save("CMSLUDens2", "CMS_Density_LU_Adjusted.png")
  }
  
  # ============ EXPOSURE CHARTS (Safety added) ============
  # Added exists("CMS_Exp") to prevent crash
  if(params$ExposureCharts == "Y" && exists("CMS_Exp") && nrow(CMS_Exp) > 2) {
    smart_save("ExpHist", "Exposure_Histogram.png")
    smart_save("ExpDiscount", "Exposure_Discount.png")
    smart_save("ExpDOMPrice", "Exposure_DOMPrice.png")
  }

  # ============ FEATURE IMPORTANCE EXPORTS ============
  if(params$FeatureImportance == "Y") {
    cat("\n--- Exporting Feature Importance Charts ---\n")
    smart_save("fi_price", paste0("FI_Price_", unit_label, ".png"))
  }

  # ============ MAP EXPORTS ============
  cat("\nExporting maps (this may take a moment)...\n")

  # Helper function for mapgl maps using mapgl::save_map() (requires chromote + Chrome)
  smart_map_save <- function(map_obj_name, filename, width = 900, height = 500) {
    if(exists(map_obj_name, inherits = TRUE)) {
      tryCatch({
        mapgl::save_map(
          map = get(map_obj_name),
          filename = paste0("./charts/", filename),
          width = width,
          height = height,
          include_legend = TRUE,
          hide_controls = TRUE,
          include_scale_bar = TRUE,
          image_scale = 1.5
        )
        cat(paste0("  Saved: ", filename, "\n"))
      }, error = function(e) {
        cat(paste0("  Error saving ", filename, ": ", e$message, "\n"))
      })
    } else {
      cat(paste0("  Skipped: ", map_obj_name, " (Object not found)\n"))
    }
  }

  # Multifamily Map
  if(params$PricePerUnit == "Y") {
    smart_map_save("Map1CMSHLU", "Map_CMS_HeatmapLU.png")
  }

  # Heatmaps - filename suffix based on AcOrSF parameter
  #smart_map_save("Map1ADFH", paste0("Map_ADF_Heatmap", unit_suffix, ".png"))
  smart_map_save("Map1CMSH", paste0("Map_CMS_Heatmap", unit_suffix, ".png"))
  smart_map_save("Map1CMS2H", paste0("Map_CMS2_Heatmap", unit_suffix, ".png"))
  #smart_map_save("Map1CMS2PropType", paste0("Map_CMS2_PropertyType", unit_suffix, ".png"))
  #smart_map_save("Map2CMS2N", paste0("Map_CMS2_Neighbourhood", unit_suffix, ".png"))

  cat("\n========================================\n")
  cat("EXPORT COMPLETE!\n")
  cat("========================================\n")
}
```

### Export CMS {.hidden}

```{r export_cms, include=FALSE}
# Export CMS sales to Excel file
openxlsx::write.xlsx(CMS1, "./CMS1_export.xlsx")
```
