---
title: "Winnipeg New Construction Permits (Multi-Residential)"
author: "Jason M. Schellenberg, P. App, AACI"
date: today
format:
  html:
    embed-resources: true
    toc: true
    toc-depth: 2
    toc-location: left
    theme: cosmo
    smooth-scroll: true
    page-layout: full
params:
  default_since_year: 2015
  subtype_preselect: null   # OPTIONAL - null or YAML list of sub_type values to pre-select
  show_parcels: true
  show_neighbourhoods: true # toggle the neighbourhood boundary overlay layer (off by default in Layers control)
  min_units: 3              # included in the pre-selected slider range; full dataset is still fetched
knitr:
  opts_chunk:
    message: false
    warning: false
    echo: false
---

```{r setup}
suppressPackageStartupMessages({
  library(httr2)
  library(jsonlite)
  library(dplyr)
  library(tidyr)
  library(stringr)
  library(lubridate)
  library(leaflet)
  library(leaflet.extras)
  library(DT)
  library(crosstalk)
  library(htmltools)
  library(downloadthis)
  library(rlang)
  library(sf)
})

# ---- Params ----
subtypes_param <- params$subtype_preselect
if (!is.null(subtypes_param)) {
  subtypes_param <- subtypes_param[nzchar(trimws(as.character(subtypes_param)))]
}
if (length(subtypes_param) == 0) subtypes_param <- NULL
default_since_year <- as.integer(params$default_since_year)
min_units_param    <- as.integer(params$min_units)

# ---- Query ----
# Multi-residential = Residential + Construct New + (dwelling_units_created > 2 OR NULL).
# The `> '2'` string-comparison form matches the user-supplied SoQL. Because SoQL
# coerces the RHS for numeric columns this works at the API level for integer units.
render_date_iso <- format(Sys.Date(), "%Y-%m-%d")
soql_parts <- c(
  "issue_date >= '2010-01-01'",
  sprintf("issue_date < '%s'", render_date_iso),
  "(work_type = 'Construct New')",
  "(permit_group = 'Residential')",
  "((dwelling_units_created > '2') OR dwelling_units_created IS NULL)"
)
query_str <- paste(
  "SELECT *",
  "WHERE", paste(soql_parts, collapse = " AND "),
  "ORDER BY issue_date DESC",
  "LIMIT 50000"
)

# ---- Cache: 24h TTL, key off query contents ----
cache_dir <- ".cache"
if (!dir.exists(cache_dir)) dir.create(cache_dir, recursive = TRUE)
qhash <- substr(rlang::hash(query_str), 1, 10)
cache_file <- file.path(cache_dir, paste0("permits_multires_", qhash, ".rds"))
fresh <- file.exists(cache_file) &&
  difftime(Sys.time(), file.info(cache_file)$mtime, units = "hours") < 24

endpoint <- "https://data.winnipeg.ca/resource/it4w-cpf4.json"
if (fresh) {
  permits_raw <- readRDS(cache_file)
  data_source <- sprintf("Cached (fetched %s)",
                         format(file.info(cache_file)$mtime, "%Y-%m-%d %H:%M %Z"))
} else {
  resp <- request(endpoint) |>
    req_url_query(`$query` = query_str) |>
    req_retry(max_tries = 3) |>
    req_perform()
  permits_raw <- resp |> resp_body_string() |> fromJSON(flatten = TRUE)
  saveRDS(permits_raw, cache_file)
  data_source <- sprintf("Live (fetched %s)", format(Sys.time(), "%Y-%m-%d %H:%M %Z"))
}

# ---- Tidy ----
permits <- permits_raw |>
  as_tibble() |>
  mutate(
    issue_date              = as_date(ymd_hms(issue_date, quiet = TRUE)),
    latitude                = suppressWarnings(as.numeric(location.latitude)),
    longitude               = suppressWarnings(as.numeric(location.longitude)),
    issue_year              = year(issue_date),
    street_number_num       = suppressWarnings(as.integer(str_extract(street_number, "^\\d+"))),
    dwelling_units_created  = suppressWarnings(as.integer(dwelling_units_created))
  ) |>
  # filter_slider (ionRangeSlider) bails on non-numeric values in its JSON
  # payload. Any permit without a parseable street number must get a numeric
  # stand-in or the slider silently fails to initialise.
  mutate(
    street_number_num = ifelse(
      is.na(street_number_num),
      suppressWarnings(min(street_number_num, na.rm = TRUE)),
      street_number_num
    ),
    street_number_num = ifelse(
      is.finite(street_number_num), as.integer(street_number_num), 0L
    )
  ) |>
  arrange(desc(issue_date)) |>
  mutate(.rowkey = as.character(row_number())) |>
  select(
    .rowkey, sub_type, issue_date, issue_year, permit_number, address,
    street_number, street_number_num, street_name,
    applicant_business_name, neighbourhood_name, ward, status,
    major_project, dwelling_units_created, latitude, longitude
  )

total_n <- nrow(permits)
years_available <- sort(unique(permits$issue_year))
units_max <- suppressWarnings(max(permits$dwelling_units_created, na.rm = TRUE))
if (!is.finite(units_max)) units_max <- 100L

# ---- Cluster boundary layer (local file: WpgNeighbourhoodClusters.geojson) ----
# 23 pre-dissolved WRHA neighbourhood-cluster polygons with a `cluster` property.
# We spatial-join permits to this file so every record gets a `cluster` tag.
clusters_sf   <- NULL
clusters_file <- "WpgNeighbourhoodClusters.geojson"
if (isTRUE(params$show_neighbourhoods) && file.exists(clusters_file)) {
  prev_s2 <- sf_use_s2(FALSE)
  on.exit(sf_use_s2(prev_s2), add = TRUE)
  clusters_sf <- tryCatch(
    sf::read_sf(clusters_file, quiet = TRUE) |>
      sf::st_zm(drop = TRUE) |>
      sf::st_make_valid() |>
      dplyr::select(cluster),
    error = function(e) NULL
  )
}

# ---- Spatial join: assign cluster to every permit ----
permits$cluster <- NA_character_
if (!is.null(clusters_sf) && nrow(clusters_sf) > 0 &&
    sum(!is.na(permits$latitude) & !is.na(permits$longitude)) > 0) {
  prev_s2 <- sf_use_s2(FALSE)
  on.exit(sf_use_s2(prev_s2), add = TRUE)
  permits_pts <- permits |>
    filter(!is.na(latitude), !is.na(longitude)) |>
    select(-cluster) |>  # avoid column name collision in st_join
    st_as_sf(coords = c("longitude", "latitude"), crs = 4326, remove = FALSE)
  suppressWarnings(st_agr(clusters_sf) <- "constant")
  hood_join <- suppressMessages(
    st_join(permits_pts, clusters_sf, join = st_within, left = TRUE)
  ) |>
    sf::st_drop_geometry() |>
    as_tibble() |>
    select(.rowkey, .cluster = cluster) |>
    (\(df) df[!duplicated(df$.rowkey), ])()

  missing_spatial <- hood_join |>
    filter(is.na(.cluster)) |>
    pull(.rowkey)
  if (length(missing_spatial) > 0) {
    nearest_pts <- permits_pts |>
      filter(.rowkey %in% missing_spatial)
    nearest_idx <- sf::st_nearest_feature(nearest_pts, clusters_sf)
    nearest_join <- tibble(
      .rowkey  = nearest_pts$.rowkey,
      .cluster = clusters_sf$cluster[nearest_idx]
    )
    hood_join <- hood_join |>
      filter(!(.rowkey %in% missing_spatial)) |>
      bind_rows(nearest_join) |>
      (\(df) df[!duplicated(df$.rowkey), ])()
  }

  permits <- permits |>
    select(-cluster) |>
    left_join(hood_join, by = ".rowkey") |>
    mutate(cluster = .cluster) |>
    select(-.cluster)
}

# ---- Parcel geometry (spatial join) ----
parcels_on_map <- NULL
parcel_match_count <- 0L
parcel_total_eligible <- sum(!is.na(permits$latitude) & !is.na(permits$longitude))

if (isTRUE(params$show_parcels) && parcel_total_eligible > 0) {
  parcel_endpoint <- "https://data.winnipeg.ca/resource/d4mq-wa44.geojson"
  parcels_cache <- file.path(cache_dir, paste0("parcels_multires_", qhash, ".rds"))
  parcels_fresh <- file.exists(parcels_cache) &&
    difftime(Sys.time(), file.info(parcels_cache)$mtime, units = "hours") < 168

  if (parcels_fresh) {
    parcels_sf <- readRDS(parcels_cache)
  } else {
    loc_unique <- permits |>
      filter(!is.na(latitude), !is.na(longitude)) |>
      distinct(latitude, longitude)
    d <- 0.0015  # ~150 m buffer around each permit on centroid bbox
    bbox_clauses <- sprintf(
      "(centroid_lat BETWEEN %.6f AND %.6f AND centroid_lon BETWEEN %.6f AND %.6f)",
      loc_unique$latitude - d, loc_unique$latitude + d,
      loc_unique$longitude - d, loc_unique$longitude + d
    )
    batch_size <- 60
    batches <- split(bbox_clauses, ceiling(seq_along(bbox_clauses) / batch_size))
    parcel_list <- lapply(batches, function(cls) {
      q <- sprintf(
        "SELECT roll_number, full_address, geometry WHERE %s LIMIT 50000",
        paste(cls, collapse = " OR ")
      )
      url <- paste0(parcel_endpoint, "?$query=",
                    utils::URLencode(q, reserved = TRUE))
      tryCatch(sf::read_sf(url, quiet = TRUE), error = function(e) NULL)
    })
    parcel_list <- parcel_list[!vapply(parcel_list, is.null, logical(1))]
    if (length(parcel_list) > 0) {
      parcels_sf <- do.call(rbind, parcel_list)
      parcels_sf <- parcels_sf[!duplicated(parcels_sf$roll_number), ]
      saveRDS(parcels_sf, parcels_cache)
    } else {
      parcels_sf <- NULL
    }
  }

  if (!is.null(parcels_sf) && nrow(parcels_sf) > 0) {
    prev_s2 <- sf_use_s2(FALSE)
    on.exit(sf_use_s2(prev_s2), add = TRUE)
    permits_pts <- permits |>
      filter(!is.na(latitude), !is.na(longitude)) |>
      st_as_sf(coords = c("longitude", "latitude"), crs = 4326, remove = FALSE)
    suppressWarnings(st_agr(parcels_sf) <- "constant")
    joined <- suppressMessages(
      st_join(permits_pts, parcels_sf, join = st_within, left = FALSE)
    )
    joined <- joined[!duplicated(joined$.rowkey), ]
    if (nrow(joined) > 0) {
      idx <- match(joined$roll_number, parcels_sf$roll_number)
      st_geometry(joined) <- st_geometry(parcels_sf)[idx]
      joined$.popup_parcel <- paste0(
        "<div style='font-family:sans-serif;font-size:12px;line-height:1.4;'>",
        "<strong>", htmlEscape(joined$sub_type), "</strong><br/>",
        "<b>Address:</b> ", htmlEscape(joined$address), "<br/>",
        "<b>Issued:</b> ", format(joined$issue_date, "%Y-%m-%d"), "<br/>",
        "<b>Permit #:</b> ", htmlEscape(joined$permit_number), "<br/>",
        "<b>Roll #:</b> ", htmlEscape(joined$roll_number), "<br/>",
        "<b>Dwelling units:</b> ", htmlEscape(ifelse(is.na(joined$dwelling_units_created), "—", as.character(joined$dwelling_units_created))), "<br/>",
        "<b>Applicant:</b> ", htmlEscape(ifelse(is.na(joined$applicant_business_name), "—", joined$applicant_business_name)), "<br/>",
        "<b>Neighbourhood:</b> ", htmlEscape(ifelse(is.na(joined$neighbourhood_name), "—", joined$neighbourhood_name)), "<br/>",
        "<b>Cluster:</b> ", htmlEscape(ifelse(is.na(joined$cluster), "—", joined$cluster)), "<br/>",
        "<b>Status:</b> ", htmlEscape(ifelse(is.na(joined$status), "—", joined$status)),
        "</div>"
      )
      parcels_on_map <- joined
      parcel_match_count <- nrow(parcels_on_map)
    }
  }
}

```

::: {.callout-note appearance="simple"}
**Data scope:** Building permits issued since **January 1, 2010** for **permit group = Residential**, **work type = Construct New**, and **dwelling units created > 2** (or null — to preserve legacy records where the field was not populated). Source: City of Winnipeg Open Data — [Building Permits (it4w-cpf4)](https://data.winnipeg.ca/Permits-Licenses/Building-Permits/it4w-cpf4). **`r data_source`**. Cache refreshes automatically after 24 hours.`r if (isTRUE(params$show_parcels)) sprintf(" Parcel polygons joined from [Assessment Parcels (d4mq-wa44)](https://data.winnipeg.ca/Assessment-Taxation-Corporate/Assessment-Parcels/d4mq-wa44) — **%s of %s** permits matched (%.0f%%).", format(parcel_match_count, big.mark = ","), format(parcel_total_eligible, big.mark = ","), 100 * parcel_match_count / max(parcel_total_eligible, 1))`
:::

```{r prefilter-notice, results='asis'}
if (!is.null(subtypes_param)) {
  cat(sprintf(
    '::: {.callout-warning appearance="simple"}\n**Pre-selected sub-types:** the Sub-type filter is pre-set to **%s**. Clear or change the selection in the filter bar to see other sub-types.\n:::\n',
    paste(subtypes_param, collapse = ", ")
  ))
}
```

```{r shared-data}
sd <- SharedData$new(permits, key = ~.rowkey, group = "permits")
```

```{r filter-bar-styles}
tags$style(HTML("
.filter-bar {
  position: sticky; top: 0; z-index: 500;
  background: #ffffff; padding: 12px 16px;
  border-bottom: 1px solid #ddd;
  box-shadow: 0 2px 6px rgba(0,0,0,0.08);
  margin-bottom: 16px;
}
.filter-grid {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(220px, 1fr));
  gap: 12px 16px; align-items: start;
}
.filter-item label { font-weight: 600; font-size: 13px; display: block; margin-bottom: 4px; }
.filter-item select.year-select {
  width: 100%; padding: 6px 8px; border: 1px solid #ccc; border-radius: 4px;
  font-size: 14px; background: white;
}
.filter-item .form-group { margin-bottom: 0 !important; }
.filter-item .control-label { font-weight: 600 !important; font-size: 13px !important; }
.count-display {
  font-size: 15px; font-weight: 500; color: #333;
  margin: 8px 0 12px 0;
}
.count-display strong { color: #c0392b; }
.filter-reset-row {
  display: flex; justify-content: flex-end; margin-top: 10px;
}
.btn-reset {
  padding: 6px 14px; border: 1px solid #c0392b; background: #ffffff;
  color: #c0392b; border-radius: 4px; font-size: 13px; font-weight: 600;
  cursor: pointer;
}
.btn-reset:hover { background: #c0392b; color: #ffffff; }
.streetnum-range { display: flex; gap: 6px; align-items: center; }
.streetnum-input {
  flex: 1 1 0; min-width: 0; padding: 6px 8px;
  border: 1px solid #ccc; border-radius: 4px;
  font-size: 14px; background: white;
}
.streetnum-sep { color: #7a7f87; font-weight: 600; }
"))
```

```{r filter-bar}
year_options <- tagList(lapply(2010:year(Sys.Date()), function(y) {
  tags$option(value = y, selected = if (y == default_since_year) NA else NULL, as.character(y))
}))

tags$div(
  class = "filter-bar",
  tags$div(
    class = "filter-grid",
    tags$div(
      class = "filter-item",
      tags$label("Issued since year", `for` = "year-filter"),
      tags$select(
        id = "year-filter",
        class = "year-select",
        onchange = "window.__applyYearFilter(this.value)",
        year_options
      )
    ),
    tags$div(
      class = "filter-item",
      filter_select("f-subtype", "Sub-type", sd, ~sub_type, multiple = TRUE)
    ),
    tags$div(
      class = "filter-item",
      filter_select("f-streetname", "Street name", sd, ~street_name, multiple = TRUE)
    ),
    tags$div(
      class = "filter-item",
      tags$label(class = "control-label", `for` = "f-streetnum-from", "Street number"),
      tags$div(
        class = "streetnum-range",
        tags$input(
          id = "f-streetnum-from", type = "number",
          inputmode = "numeric", min = 0, step = 1,
          class = "streetnum-input", placeholder = "From"
        ),
        tags$span(class = "streetnum-sep", "\u2013"),
        tags$input(
          id = "f-streetnum-to", type = "number",
          inputmode = "numeric", min = 0, step = 1,
          class = "streetnum-input", placeholder = "To"
        )
      )
    ),
    tags$div(
      class = "filter-item",
      filter_slider(
        "f-units", "Dwelling units created", sd, ~dwelling_units_created,
        step = 1, round = TRUE, ticks = FALSE, sep = ""
      )
    ),
    tags$div(
      class = "filter-item",
      filter_select("f-cluster", "Cluster", sd, ~cluster, multiple = TRUE)
    )
  ),
  tags$div(
    class = "filter-reset-row",
    tags$button(
      id = "btn-reset-filters",
      class = "btn-reset",
      type = "button",
      onclick = "window.__resetFilters && window.__resetFilters()",
      "Reset filters"
    )
  )
)
```

```{r count-display}
tags$div(
  class = "count-display",
  id = "count-display",
  HTML(sprintf("Showing <strong id='count-shown'>%s</strong> of %s permits",
               format(total_n, big.mark = ","),
               format(total_n, big.mark = ",")))
)
```

```{r year-filter-js}
year_data_json <- jsonlite::toJSON(permits$issue_year)
tags$script(HTML(sprintf("
(function() {
  var years = %s;
  var keys  = years.map(function(_, i) { return String(i + 1); });

  function onReady(cb) {
    if (document.readyState !== 'loading') cb();
    else document.addEventListener('DOMContentLoaded', cb);
  }

  onReady(function() {
    if (typeof crosstalk === 'undefined') return;
    var fh = new crosstalk.FilterHandle('permits');

    window.__applyYearFilter = function(yearStr) {
      var y = parseInt(yearStr, 10);
      if (isNaN(y)) { fh.clear(); return; }
      var matched = [];
      for (var i = 0; i < years.length; i++) {
        if (years[i] >= y) matched.push(keys[i]);
      }
      fh.set(matched);
    };

    var sel = document.getElementById('year-filter');
    if (sel) window.__applyYearFilter(sel.value);
  });
})();
", year_data_json)))
```

```{r reset-filters-js}
preselect_json_for_reset <- if (!is.null(subtypes_param)) {
  jsonlite::toJSON(subtypes_param)
} else {
  "null"
}
tags$script(HTML(sprintf("
(function() {
  var defaultYear = %d;
  var preselect   = %s;

  function getSelectize(containerId) {
    var c = document.getElementById(containerId);
    if (!c) return null;
    var sel = (c.tagName === 'SELECT') ? c : c.querySelector('select');
    return (sel && sel.selectize) ? sel.selectize : null;
  }
  function resetSlider(containerId) {
    var c = document.getElementById(containerId);
    if (!c) return;
    var input = c.querySelector('input.js-range-slider');
    if (!input) return;
    if (typeof $ !== 'undefined') {
      var inst = $(input).data('ionRangeSlider');
      if (inst && typeof inst.reset === 'function') inst.reset();
    }
  }

  window.__resetFilters = function() {
    // Year dropdown
    var yearSel = document.getElementById('year-filter');
    if (yearSel) {
      yearSel.value = String(defaultYear);
      if (typeof window.__applyYearFilter === 'function') {
        window.__applyYearFilter(yearSel.value);
      }
    }

    // clearAllExceptYear wipes every filter_select, the streetnum From/To
    // boxes, AND the dwelling-units slider under a suppression flag so
    // narrowAll doesn't cascade mid-clear.
    if (typeof window.__clearAllExceptYear === 'function') {
      window.__clearAllExceptYear();
    } else {
      ['f-subtype', 'f-streetname', 'f-cluster'].forEach(function(id) {
        var sz = getSelectize(id);
        if (sz) sz.clear(false);
      });
      if (typeof window.__resetStreetnum === 'function') window.__resetStreetnum();
      resetSlider('f-units');
    }

    // Re-narrow dropdown options based on the (now reset) filter state —
    // keeps options consistent with what the user sees before any preselect.
    if (typeof window.__narrowAll === 'function') {
      window.__narrowAll();
    }

    // Re-apply sub-type pre-selection if configured
    if (preselect && preselect.length) {
      var sub = getSelectize('f-subtype');
      if (sub) sub.setValue(preselect, false);
    }

    // Clear DT global + column search boxes and redraw
    if (typeof $ !== 'undefined' && $.fn && $.fn.DataTable) {
      $('table.dataTable').each(function() {
        try {
          var api = $(this).DataTable();
          api.search('');
          api.columns().search('');
          api.draw();
        } catch (e) {}
      });
    }

    // Reset leaflet map view to the initial bounds captured on load
    if (typeof window.__resetLeafletView === 'function') {
      window.__resetLeafletView();
    }
  };
})();
", default_since_year, preselect_json_for_reset)))
```

```{r map-reset-init-js}
tags$script(HTML("
(function() {
  function onReady(cb) {
    if (document.readyState !== 'loading') cb();
    else document.addEventListener('DOMContentLoaded', cb);
  }

  function findLeafletWidget() {
    if (typeof HTMLWidgets === 'undefined') return null;
    var widgets = HTMLWidgets.findAll ? HTMLWidgets.findAll('.leaflet') : [];
    for (var i = 0; i < widgets.length; i++) {
      if (widgets[i] && widgets[i].getMap) {
        var m = widgets[i].getMap();
        if (m) return m;
      }
      if (widgets[i] && widgets[i].map) return widgets[i].map;
    }
    return null;
  }

  onReady(function() {
    var initialCenter = null;
    var initialZoom   = null;
    var tries = 0;
    var iv = setInterval(function() {
      var map = findLeafletWidget();
      if (map && typeof map.getCenter === 'function') {
        try {
          initialCenter = map.getCenter();
          initialZoom   = map.getZoom();
          window.__resetLeafletView = function() {
            var m = findLeafletWidget();
            if (m && initialCenter != null && initialZoom != null) {
              m.setView(initialCenter, initialZoom, { animate: false });
            }
          };
          clearInterval(iv);
        } catch (e) {}
      } else if (++tries > 120) {
        clearInterval(iv);
      }
    }, 150);
  });
})();
"))
```

```{r subtype-prefill-js}
if (!is.null(subtypes_param)) {
  tags$script(HTML(sprintf("
(function() {
  var preselect = %s;
  function onReady(cb) {
    if (document.readyState !== 'loading') cb();
    else document.addEventListener('DOMContentLoaded', cb);
  }
  onReady(function() {
    var tries = 0;
    var iv = setInterval(function() {
      var container = document.getElementById('f-subtype');
      var sel = container ? container.querySelector('select') : null;
      if (sel && sel.selectize) {
        sel.selectize.setValue(preselect, false);
        clearInterval(iv);
      } else if (++tries > 80) {
        clearInterval(iv);
      }
    }, 100);
  });
})();
", jsonlite::toJSON(subtypes_param))))
}
```

```{r streetnum-filter-js}
streetnum_by_key_json <- jsonlite::toJSON(
  setNames(as.list(permits$street_number_num), permits$.rowkey),
  auto_unbox = TRUE, na = "null"
)
tags$script(HTML(sprintf("
(function() {
  var streetnumByKey = %s;

  function onReady(cb) {
    if (document.readyState !== 'loading') cb();
    else document.addEventListener('DOMContentLoaded', cb);
  }

  onReady(function() {
    if (typeof crosstalk === 'undefined') return;
    var fh = new crosstalk.FilterHandle('permits');
    var fromEl = document.getElementById('f-streetnum-from');
    var toEl   = document.getElementById('f-streetnum-to');
    if (!fromEl || !toEl) return;

    function apply() {
      var fromRaw = (fromEl.value || '').trim();
      var toRaw   = (toEl.value   || '').trim();
      if (fromRaw === '' && toRaw === '') { fh.clear(); return; }
      var lo = fromRaw === '' ? -Infinity : parseFloat(fromRaw);
      var hi = toRaw   === '' ?  Infinity : parseFloat(toRaw);
      if (isNaN(lo)) lo = -Infinity;
      if (isNaN(hi)) hi =  Infinity;
      var matched = [];
      for (var k in streetnumByKey) {
        var v = streetnumByKey[k];
        if (v == null) continue;
        if (v >= lo && v <= hi) matched.push(k);
      }
      fh.set(matched);
    }
    fromEl.addEventListener('input',  apply);
    fromEl.addEventListener('change', apply);
    toEl.addEventListener('input',    apply);
    toEl.addEventListener('change',   apply);

    window.__resetStreetnum = function() {
      fromEl.value = '';
      toEl.value   = '';
      fh.clear();
    };
  });
})();
", streetnum_by_key_json)))
```

```{r interactive-narrow-js}
# Per-rowkey payloads for MUTUAL narrowing. Every dropdown narrows its visible
# options to values that still exist in the intersection of (year floor) + all
# OTHER active filter selections + streetnum range + dwelling-units range.
# Year is primary — a year change wipes every other filter before re-narrowing.
key_subtype_n    <- jsonlite::toJSON(
  setNames(as.list(permits$sub_type),           permits$.rowkey),
  auto_unbox = TRUE, na = "null"
)
key_streetname_n <- jsonlite::toJSON(
  setNames(as.list(permits$street_name),        permits$.rowkey),
  auto_unbox = TRUE, na = "null"
)
key_cluster_n    <- jsonlite::toJSON(
  setNames(as.list(permits$cluster),            permits$.rowkey),
  auto_unbox = TRUE, na = "null"
)
key_hood_n       <- jsonlite::toJSON(
  setNames(as.list(permits$neighbourhood_name), permits$.rowkey),
  auto_unbox = TRUE, na = "null"
)
key_year_n       <- jsonlite::toJSON(
  setNames(as.integer(permits$issue_year),      permits$.rowkey),
  auto_unbox = TRUE, na = "null"
)
key_streetnum_n  <- jsonlite::toJSON(
  setNames(as.list(permits$street_number_num),  permits$.rowkey),
  auto_unbox = TRUE, na = "null"
)
key_units_n      <- jsonlite::toJSON(
  setNames(as.list(permits$dwelling_units_created), permits$.rowkey),
  auto_unbox = TRUE, na = "null"
)

tags$script(HTML(sprintf("
(function() {
  var KEY = {
    subtype:    %s,
    streetname: %s,
    cluster:    %s,
    hood:       %s,
    year:       %s,
    streetnum:  %s,
    units:      %s
  };

  var WIDGETS = [
    { id: 'f-subtype',       key: 'subtype'    },
    { id: 'f-streetname',    key: 'streetname' },
    { id: 'f-cluster',       key: 'cluster'    }
  ];

  var suppressNarrow = false;

  function onReady(cb) {
    if (document.readyState !== 'loading') cb();
    else document.addEventListener('DOMContentLoaded', cb);
  }

  function getSelectizeFor(containerId) {
    var c = document.getElementById(containerId);
    if (!c) return null;
    var sel = (c.tagName === 'SELECT') ? c : c.querySelector('select');
    return (sel && sel.selectize) ? sel.selectize : null;
  }

  function currentYear() {
    var s = document.getElementById('year-filter');
    if (!s) return null;
    var v = parseInt(s.value, 10);
    return isNaN(v) ? null : v;
  }

  function currentSelectionSet(id) {
    var sz = getSelectizeFor(id);
    if (!sz) return null;
    var v = sz.getValue();
    if (v == null) return null;
    var arr = Array.isArray(v) ? v : (v === '' ? [] : [v]);
    if (!arr.length) return null;
    var set = Object.create(null);
    arr.forEach(function(x) { if (x != null && x !== '') set[x] = true; });
    return Object.keys(set).length ? set : null;
  }

  function currentStreetnumRange() {
    var f = document.getElementById('f-streetnum-from');
    var t = document.getElementById('f-streetnum-to');
    var fromRaw = ((f && f.value) || '').trim();
    var toRaw   = ((t && t.value) || '').trim();
    if (fromRaw === '' && toRaw === '') return null;
    var lo = fromRaw === '' ? -Infinity : parseFloat(fromRaw);
    var hi = toRaw   === '' ?  Infinity : parseFloat(toRaw);
    if (isNaN(lo)) lo = -Infinity;
    if (isNaN(hi)) hi =  Infinity;
    return { lo: lo, hi: hi };
  }

  function currentUnitsRange() {
    var c = document.getElementById('f-units');
    if (!c || typeof $ === 'undefined') return null;
    var input = c.querySelector('input.js-range-slider');
    if (!input) return null;
    var inst = $(input).data('ionRangeSlider');
    if (!inst || !inst.result) return null;
    var r = inst.result;
    // Slider at full extent = no active filter
    if (r.from === r.min && r.to === r.max) return null;
    return { lo: r.from, hi: r.to };
  }

  // Rowkeys matching year + every active filter EXCEPT excludeWidgetId.
  function rowkeysMatching(excludeWidgetId) {
    var minYear = currentYear();
    var filters = [];
    WIDGETS.forEach(function(w) {
      if (w.id === excludeWidgetId) return;
      var sel = currentSelectionSet(w.id);
      if (sel) filters.push({ key: w.key, set: sel });
    });
    var snRange = currentStreetnumRange();
    var unRange = currentUnitsRange();

    var out = [];
    var yearMap = KEY.year;
    for (var k in yearMap) {
      var y = yearMap[k];
      if (minYear != null && (y == null || y < minYear)) continue;
      var ok = true;
      for (var i = 0; i < filters.length; i++) {
        var val = KEY[filters[i].key][k];
        if (val == null || !filters[i].set[val]) { ok = false; break; }
      }
      if (!ok) continue;
      if (snRange) {
        var sv = KEY.streetnum[k];
        if (sv == null || sv < snRange.lo || sv > snRange.hi) continue;
      }
      if (unRange) {
        var uv = KEY.units[k];
        if (uv == null || uv < unRange.lo || uv > unRange.hi) continue;
      }
      out.push(k);
    }
    return out;
  }

  function narrowOne(widget) {
    var sz = getSelectizeFor(widget.id);
    if (!sz) return;
    var rowkeys = rowkeysMatching(widget.id);
    var keyToValue = KEY[widget.key];
    var keep = Object.create(null);
    for (var i = 0; i < rowkeys.length; i++) {
      var v = keyToValue[rowkeys[i]];
      if (v != null) keep[v] = true;
    }
    // Preserve current selection so selectize doesn't drop displayed items.
    var cur = sz.getValue();
    if (cur) {
      (Array.isArray(cur) ? cur : [cur]).forEach(function(v) {
        if (v) keep[v] = true;
      });
    }
    Object.keys(sz.options).forEach(function(v) {
      if (!keep[v]) sz.removeOption(v, true);
    });
    Object.keys(keep).forEach(function(v) {
      if (!sz.options[v]) sz.addOption({ value: v, text: v });
    });
    sz.refreshOptions(false);
  }

  function narrowAll() {
    if (suppressNarrow) return;
    WIDGETS.forEach(narrowOne);
  }
  window.__narrowAll = narrowAll;

  function clearOthers() {
    suppressNarrow = true;
    try {
      WIDGETS.forEach(function(w) {
        var sz = getSelectizeFor(w.id);
        if (sz) sz.clear(false);
      });
      if (typeof window.__resetStreetnum === 'function') {
        window.__resetStreetnum();
      }
      // Reset units slider
      var uc = document.getElementById('f-units');
      if (uc && typeof $ !== 'undefined') {
        var ui = uc.querySelector('input.js-range-slider');
        if (ui) {
          var inst = $(ui).data('ionRangeSlider');
          if (inst && typeof inst.reset === 'function') inst.reset();
        }
      }
    } finally {
      suppressNarrow = false;
    }
  }
  window.__clearAllExceptYear = clearOthers;

  onReady(function() {
    var yearSel = document.getElementById('year-filter');

    // Year is primary: changing it wipes every other filter, then re-narrows.
    if (yearSel) {
      yearSel.addEventListener('change', function() {
        clearOthers();
        narrowAll();
      });
    }

    // Streetnum From/To boxes trigger mutual narrowing.
    ['f-streetnum-from', 'f-streetnum-to'].forEach(function(id) {
      var el = document.getElementById(id);
      if (!el) return;
      el.addEventListener('input',  narrowAll);
      el.addEventListener('change', narrowAll);
    });

    // Units slider: listen for crosstalk's change event on the hidden input.
    var unitsContainer = document.getElementById('f-units');
    if (unitsContainer) {
      var unitsInput = unitsContainer.querySelector('input.js-range-slider');
      if (unitsInput && typeof $ !== 'undefined') {
        $(unitsInput).on('change', narrowAll);
      }
    }

    // Wait for all selectize widgets to initialise, attach change hooks, then
    // do the first narrow pass.
    var tries = 0;
    var iv = setInterval(function() {
      var ready = WIDGETS.every(function(w) { return getSelectizeFor(w.id); });
      if (ready) {
        WIDGETS.forEach(function(w) {
          var sz = getSelectizeFor(w.id);
          sz.on('change', narrowAll);
        });
        narrowAll();
        clearInterval(iv);
      } else if (++tries > 120) {
        clearInterval(iv);
      }
    }, 100);
  });
})();
", key_subtype_n, key_streetname_n, key_cluster_n, key_hood_n, key_year_n, key_streetnum_n, key_units_n)))
```

## Map

```{r map}
pal <- colorFactor(palette = "viridis", domain = sort(unique(permits$sub_type)))

subtype_with_units <- function(st, units) {
  ifelse(is.na(units), st, sprintf("%s (%d units)", st, units))
}

popup_html <- paste0(
  "<div style='font-family:sans-serif;font-size:12px;line-height:1.4;'>",
  "<strong>", htmlEscape(permits$sub_type), "</strong><br/>",
  "<b>Address:</b> ", htmlEscape(permits$address), "<br/>",
  "<b>Issued:</b> ", format(permits$issue_date, "%Y-%m-%d"), "<br/>",
  "<b>Permit #:</b> ", htmlEscape(permits$permit_number), "<br/>",
  "<b>Dwelling units:</b> ", htmlEscape(ifelse(is.na(permits$dwelling_units_created), "—", as.character(permits$dwelling_units_created))), "<br/>",
  "<b>Applicant:</b> ", htmlEscape(ifelse(is.na(permits$applicant_business_name), "—", permits$applicant_business_name)), "<br/>",
  "<b>Neighbourhood:</b> ", htmlEscape(ifelse(is.na(permits$neighbourhood_name), "—", permits$neighbourhood_name)), "<br/>",
  "<b>Cluster:</b> ", htmlEscape(ifelse(is.na(permits$cluster), "—", permits$cluster)), "<br/>",
  "<b>Status:</b> ", htmlEscape(ifelse(is.na(permits$status), "—", permits$status)),
  "</div>"
)
permits$.popup <- popup_html
sd <- SharedData$new(permits, key = ~.rowkey, group = "permits")

map_widget <- leaflet(sd, width = "100%", height = 560) |>
  addProviderTiles(providers$CartoDB.Positron, group = "Light") |>
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite") |>
  addProviderTiles(providers$OpenStreetMap, group = "OSM")

if (!is.null(clusters_sf) && nrow(clusters_sf) > 0) {
  map_widget <- map_widget |>
    addPolygons(
      data        = clusters_sf,
      group       = "Clusters",
      color       = "#2563eb", weight = 1.75, opacity = 0.85,
      fillColor   = "#3b82f6", fillOpacity = 0.07,
      smoothFactor = 0.5,
      highlightOptions = highlightOptions(
        weight = 2.75, color = "#1d4ed8",
        fillOpacity = 0.14, bringToFront = FALSE
      ),
      label = ~cluster,
      popup = ~paste0("<b>Cluster:</b> ", htmlEscape(cluster)),
      options = pathOptions(pane = "overlayPane", interactive = TRUE)
    )
}

if (!is.null(parcels_on_map) && nrow(parcels_on_map) > 0) {
  map_widget <- map_widget |>
    addPolygons(
      data = parcels_on_map,
      layerId = ~.rowkey,
      color = ~pal(sub_type), fillColor = ~pal(sub_type),
      fillOpacity = 0.25, weight = 1.5, opacity = 0.9,
      popup = ~.popup_parcel,
      label = ~paste0(subtype_with_units(sub_type, dwelling_units_created), " — ", address, " (", issue_year, ") — ", ifelse(is.na(neighbourhood_name), "—", neighbourhood_name), " / ", ifelse(is.na(cluster), "—", cluster))
    )
}

map_widget |>
  addCircleMarkers(
    lng = ~longitude, lat = ~latitude,
    color = ~pal(sub_type), fillColor = ~pal(sub_type),
    fillOpacity = 0.85, stroke = TRUE, weight = 1, opacity = 1,
    radius = 6,
    popup = ~.popup,
    label = ~paste0(subtype_with_units(sub_type, dwelling_units_created), " — ", address, " (", issue_year, ")")
  ) |>
  addLegend(
    position = "bottomright", pal = pal,
    values = sort(unique(permits$sub_type)),
    title = "Sub-type", opacity = 0.9
  ) |>
  addLayersControl(
    baseGroups    = c("Light", "Satellite", "OSM"),
    overlayGroups = c(
      if (!is.null(clusters_sf) && nrow(clusters_sf) > 0) "Clusters"
    ),
    options       = layersControlOptions(collapsed = TRUE)
  ) |>
  addFullscreenControl() |>
  addScaleBar(position = "bottomleft") |>
  (\(m) m)()
```

```{r legend-filter-js}
key_subtype_json <- jsonlite::toJSON(
  setNames(as.list(permits$sub_type), permits$.rowkey),
  auto_unbox = TRUE
)
tags$script(HTML(sprintf("
(function() {
  var keyToSubtype = %s;

  function onReady(cb) {
    if (document.readyState !== 'loading') cb();
    else document.addEventListener('DOMContentLoaded', cb);
  }

  function findLegend() {
    return document.querySelector('.leaflet-container .info.legend');
  }

  function wrapLegend(legend) {
    if (legend.getAttribute('data-reactive') === '1') return;
    var swatches = legend.querySelectorAll('i');
    swatches.forEach(function(iEl) {
      var parts = [iEl];
      var label = '';
      var n = iEl.nextSibling;
      while (n) {
        if (n.nodeType === 3) {
          label += n.nodeValue;
          parts.push(n);
          n = n.nextSibling;
        } else if (n.nodeType === 1 && n.tagName === 'BR') {
          parts.push(n);
          break;
        } else {
          break;
        }
      }
      var span = document.createElement('span');
      span.className = 'legend-entry';
      span.setAttribute('data-label', label.trim());
      iEl.parentNode.insertBefore(span, iEl);
      parts.forEach(function(p) { span.appendChild(p); });
    });
    legend.setAttribute('data-reactive', '1');
  }

  onReady(function() {
    if (typeof crosstalk === 'undefined') return;
    var fh = new crosstalk.FilterHandle('permits');
    var legendReady = false;

    function update() {
      var legend = findLegend();
      if (!legend) return;
      var keys = fh.filteredKeys;
      var visible = null;
      if (keys != null) {
        visible = Object.create(null);
        for (var i = 0; i < keys.length; i++) {
          var st = keyToSubtype[keys[i]];
          if (st) visible[st] = true;
        }
      }
      var entries = legend.querySelectorAll('.legend-entry');
      entries.forEach(function(e) {
        var label = e.getAttribute('data-label');
        e.style.display = (visible == null || visible[label]) ? '' : 'none';
      });
    }

    fh.on('change', function() { if (legendReady) update(); });

    var tries = 0;
    var iv = setInterval(function() {
      var legend = findLegend();
      if (legend) {
        wrapLegend(legend);
        legendReady = true;
        update();
        clearInterval(iv);
      } else if (++tries > 80) {
        clearInterval(iv);
      }
    }, 100);
  });
})();
", key_subtype_json)))
```

```{r parcel-filter-js}
if (isTRUE(params$show_parcels)) {
  tags$script(HTML("
(function() {
  function onReady(cb) {
    if (document.readyState !== 'loading') cb();
    else document.addEventListener('DOMContentLoaded', cb);
  }

  function findLeafletWidget() {
    if (typeof HTMLWidgets === 'undefined') return null;
    var widgets = HTMLWidgets.findAll ? HTMLWidgets.findAll('.leaflet') : [];
    for (var i = 0; i < widgets.length; i++) {
      if (widgets[i] && widgets[i].getMap) {
        var m = widgets[i].getMap();
        if (m) return m;
      }
      if (widgets[i] && widgets[i].map) return widgets[i].map;
    }
    var els = document.querySelectorAll('.leaflet');
    for (var j = 0; j < els.length; j++) {
      var obj = HTMLWidgets.find ? HTMLWidgets.find('#' + els[j].id) : null;
      if (obj) {
        if (obj.getMap) return obj.getMap();
        if (obj.map) return obj.map;
      }
    }
    return null;
  }

  onReady(function() {
    if (typeof crosstalk === 'undefined') return;
    var fh = new crosstalk.FilterHandle('permits');
    var ready = false;

    function resolveLayer(entry) {
      if (!entry) return null;
      if (typeof entry.addTo === 'function') return entry;
      if (entry.layer && typeof entry.layer.addTo === 'function') return entry.layer;
      return null;
    }

    function applyFilter() {
      var map = findLeafletWidget();
      if (!map || !map.layerManager) return;
      var byId = map.layerManager._byLayerId || {};
      var keys = fh.filteredKeys;
      var visible = null;
      if (keys != null) {
        visible = Object.create(null);
        for (var i = 0; i < keys.length; i++) visible[keys[i]] = true;
      }
      Object.keys(byId).forEach(function(k) {
        var sepIdx = k.indexOf('\\n');
        var cat, rk;
        if (sepIdx > -1) { cat = k.substring(0, sepIdx); rk = k.substring(sepIdx + 1); }
        else if (k.indexOf('shape-') === 0) { cat = 'shape'; rk = k.substring(6); }
        else return;
        if (cat !== 'shape') return;
        var layer = resolveLayer(byId[k]);
        if (!layer) return;
        var show = (visible == null || visible[rk]);
        if (show) {
          if (!map.hasLayer(layer)) layer.addTo(map);
        } else {
          if (map.hasLayer(layer)) map.removeLayer(layer);
        }
      });
    }

    fh.on('change', function() { if (ready) applyFilter(); });

    var tries = 0;
    var iv = setInterval(function() {
      var map = findLeafletWidget();
      if (map && map.layerManager) {
        ready = true;
        applyFilter();
        clearInterval(iv);
      } else if (++tries > 100) {
        clearInterval(iv);
      }
    }, 100);
  });
})();
  "))
}
```

## Permit table

```{r dt-table}
roll_lookup <- if (!is.null(parcels_on_map)) {
  parcels_on_map |>
    sf::st_drop_geometry() |>
    as_tibble() |>
    select(.rowkey, roll_number)
} else {
  tibble(.rowkey = character(), roll_number = character())
}

dt_data <- permits |>
  left_join(roll_lookup, by = ".rowkey") |>
  mutate(issue_date = format(issue_date, "%Y-%m-%d")) |>
  select(
    `Issue date`    = issue_date,
    `Sub-type`      = sub_type,
    `Address`       = address,
    `Units`         = dwelling_units_created,
    `Neighbourhood` = neighbourhood_name,
    `Cluster`       = cluster,
    `Status`        = status,
    `Permit #`      = permit_number,
    `Roll #`        = roll_number,
    `Latitude`      = latitude,
    `Longitude`     = longitude
  )
dt_sd <- SharedData$new(dt_data, key = permits$.rowkey, group = "permits")

datatable(
  dt_sd,
  rownames   = FALSE,
  filter     = "top",
  extensions = c("Buttons"),
  options = list(
    order       = list(list(0, "desc")),
    pageLength  = 25,
    lengthMenu  = c(10, 25, 50, 100, 250),
    dom         = "Bfrtip",
    columnDefs  = list(
      list(targets = 7:10, visible = FALSE)  # Permit #, Roll #, Lat, Lon hidden on screen
    ),
    buttons     = list(
      list(extend = "copy",  text = "Copy",
           exportOptions = list(columns = 0:10, modifier = list(search = "applied"))),
      list(extend = "csv",   text = "Download CSV (filtered)",
           filename = "wpg_multires_new_permits_filtered",
           exportOptions = list(columns = 0:10, modifier = list(search = "applied"))),
      list(extend = "print", text = "Print")
    ),
    scrollX    = TRUE,
    autoWidth  = TRUE,
    drawCallback = DT::JS(
      "function() {
         var info = this.api().page.info();
         var el = document.getElementById('count-shown');
         if (el) el.textContent = info.recordsDisplay.toLocaleString();
       }"
    )
  )
)
```

## Download full dataset

```{r download-button}
permits |>
  select(-.rowkey, -.popup, -street_number_num) |>
  mutate(issue_date = format(issue_date, "%Y-%m-%d")) |>
  download_this(
    output_name      = sprintf("wpg_multires_new_permits_%s", format(Sys.Date(), "%Y%m%d")),
    output_extension = ".csv",
    button_label     = "Download full dataset (CSV, unfiltered)",
    button_type      = "primary",
    has_icon         = TRUE,
    icon             = "fa fa-download",
    csv2             = FALSE
  )
```

---

::: {.small}
Generated with [Quarto](https://quarto.org) · Data © City of Winnipeg, [Open Government Licence – Winnipeg](https://data.winnipeg.ca/open-data-licence). Report prepared by Jason M. Schellenberg, P. App, AACI.
:::
